---
title: "CoDev in Families: Main Script"
author: "Evan A. Warfel"
format: html
editor: visual
format: 
  html:
    code-tools: true
    code-copy: true
    code-line-numbers: true
    code-link: true
    theme: united
    highlight-style: tango
    df-print: paged
    code-fold: show
    toc: true
    toc-float: true
    self-contained: true
---

# Paradoxical Patterns of Personality Co-development in Families

Welcome to this project. This is the main data script; it was easier to keep everything in one big file. Data has been pre-processed in a Jupyter notebook also available in this github directory. NB: I find this much easier to view in "source" mode in Rstudio, the outline with the section headings make navigating this file much easier.

The overall strategy is as follows: 1. Once the data is pre-processed, create univariate growth curve models. 2. Store the Univariate LGCMs in a table, and programmatically combine them into Bivariate LGCMs. 3. Fit all of the models in parallel, extract parameters and fit metrics programmatically, etc. 4. Repeat the same kind of procedure for moderators.

Overall, the main strategy here is programmatically morph tables of models into final tables of parameter estimates.

# ----- Section 0: Housekeeping ----- ----- -----

## Packages

First, we load some packages and set the defaults:

```{r}
set.seed(42)
options(max.print = 2000, width = 120, repr.matrix.max.rows = 600, repr.matrix.max.cols = 210)

library(semTools)
library(dplyr)
library(lavaan)
library(kableExtra)
library(knitr)
library(tidyverse)
library(future.apply)
library(ggridges)
library(patchwork)
library(ragg)
library(showtext)

availableCores()
plan(multisession, workers = availableCores() - 1)
nbrOfWorkers()
```

## Getting the data

```{r}
#This data has been preprocessed via the python script. After items were reversed, they were parceled. Then, each parcel was  
ZSCORED <- read.csv("./Data/ParceledData_ZScoredToBaselineWave_6_26_2024.csv")
head(ZSCORED)
```

# ----- Section 1: Univariate Models ----- ----- -----

This section contains all of the base univariate growth curve models. Constraints were systematically tuned by hand according the procedures laid out in the methods section of the accompanying paper.

## 1. Univariate Growth Curves

Checks and gotchas for these models: 1. The =\~ NA\*Variable+Varible syntax comes from a Nilam Ram demo. 2. I've used three decimal places for the latent slope loadings. 3.The intercepts of the trajectories are at the actual midpoint instead of putting a 0 before one of the waves. 4. I used differences in the mean child age at each wave as the guide to how much time has elasped between waves.

## -------- EXTRAVERSION --------

### Full Trajectory Models:

#### CHILD EXTRAVERSION UNIVARIATE

```{r}
Child_Univariate_Extraversion <- "
#-------------------- ChildPartialStrongExtraversion --------------------
#Latent Variables:
W5Extraversion_Child  =~ NA*c05_E1 + clambda0*c05_E1 + clambda1*c05_E2 + clambda2*c05_E3
W7Extraversion_Child  =~ NA*c07_E1 + clambda0*c07_E1 + clambda1*c07_E2 + clambda2*c07_E3
W10Extraversion_Child =~ NA*c10_E1 + clambda0*c10_E1 + clambda1*c10_E2 + clambda2*c10_E3
W11Extraversion_Child =~ NA*c11_E1 + clambda0*c11_E1 + clambda1*c11_E2 + clambda2*c11_E3
W12Extraversion_Child =~ NA*c12_E1 + clambda0*c12_E1 + clambda1*c12_E2 + clambda2*c12_E3
W13Extraversion_Child =~ NA*c13_E1 + clambda0*c13_E1 + clambda1*c13_E2 + clambda2*c13_E3

#Standardizing the latent variables to have a mean of 0 and a Var of 1:
#Latent Variable Means:
W5Extraversion_Child  ~ 0
W7Extraversion_Child  ~ 0
W10Extraversion_Child ~ 0
W11Extraversion_Child ~ 0
W12Extraversion_Child ~ 0
W13Extraversion_Child ~ 0

# Latent Variable Variances
W5Extraversion_Child  ~~ 1*W5Extraversion_Child
W7Extraversion_Child  ~~ 1*W7Extraversion_Child
W10Extraversion_Child ~~ 1*W10Extraversion_Child
W11Extraversion_Child ~~ 1*W11Extraversion_Child
W12Extraversion_Child ~~ 1*W12Extraversion_Child
W13Extraversion_Child ~~ 1*W13Extraversion_Child


#Parcel Intercepts
c05_E1 ~ 1 #third highest subsequent residual error when constrained
c05_E2 ~ 1 #Highest residual error variance when constrainedfreed in  Ringwald Et al.
c05_E3 ~ 1 #Sixth freed intercept. ALso freed in Ringwald Et al.

c07_E1 ~ 1 #fifth highest subsequent residual error. Also freed in  Ringwald Et al.
c07_E2 ~ 1 #second highest  subsequent  residual error after freeing c05_E2
c07_E3 ~ 1 #fourth highest subsequent residual error when constrained. freed in Ringwald Et al.

c10_E1 ~ cintercept1*1
c10_E2 ~ cintercept2*1
c10_E3 ~ cintercept3*1

c11_E1 ~ cintercept1*1
c11_E2 ~ cintercept2*1
c11_E3 ~ cintercept3*1

c12_E1 ~ cintercept1*1
c12_E2 ~ cintercept2*1
c12_E3 ~ cintercept3*1

c13_E1 ~ cintercept1*1
c13_E2 ~ cintercept2*1
c13_E3 ~ cintercept3*1

# Parcel variances
c05_E1 ~~ c05_E1
c05_E2 ~~ c05_E2
c05_E3 ~~ c05_E3

c07_E1 ~~ c07_E1
c07_E2 ~~ c07_E2
c07_E3 ~~ c07_E3

c10_E1 ~~ c10_E1
c10_E2 ~~ c10_E2
c10_E3 ~~ c10_E3

c11_E1 ~~ c11_E1
c11_E2 ~~ c11_E2
c11_E3 ~~ c11_E3

c12_E1 ~~ c12_E1
c12_E2 ~~ c12_E2
c12_E3 ~~ c12_E3

c13_E1 ~~ c13_E1
c13_E2 ~~ c13_E2
c13_E3 ~~ c13_E3

# Parcel residual covariances
c05_E1 ~~ c07_E1 + c10_E1 + c11_E1 + c12_E1 + c13_E1
c05_E2 ~~ c07_E2 + c10_E2 + c11_E2 + c12_E2 + c13_E2
c05_E3 ~~ c07_E3 + c10_E3 + c11_E3 + c12_E3 + c13_E3

c07_E1 ~~ c10_E1 + c11_E1 + c12_E1 + c13_E1
c07_E2 ~~ c10_E2 + c11_E2 + c12_E2 + c13_E2
c07_E3 ~~ c10_E3 + c11_E3 + c12_E3 + c13_E3

c10_E1 ~~ c11_E1 + c12_E1 + c13_E1
c10_E2 ~~ c11_E2 + c12_E2 + c13_E2
c10_E3 ~~ c11_E3 + c12_E3 + c13_E3

c11_E1 ~~ c12_E1 + c13_E1
c11_E2 ~~ c12_E2 + c13_E2
c11_E3 ~~ c12_E3 + c13_E3

c12_E1 ~~ c13_E1
c12_E2 ~~ c13_E2
c12_E3 ~~ c13_E3

##Univariate Growth Curve Stuff:
ChildExtraversionIntercept =~ 1*W5Extraversion_Child+1*W7Extraversion_Child+1*W10Extraversion_Child+1*W11Extraversion_Child+1*W12Extraversion_Child+1*W13Extraversion_Child

ChildExtraversionSlope =~ -0.569*W5Extraversion_Child+-0.364*W7Extraversion_Child+-0.059*W10Extraversion_Child+0.13*W11Extraversion_Child+0.274*W12Extraversion_Child+0.569*W13Extraversion_Child

ChildExtraversionIntercept ~ 1
ChildExtraversionSlope ~ 1

ChildExtraversionIntercept ~~ ChildExtraversionIntercept
ChildExtraversionSlope ~~ ChildExtraversionSlope
ChildExtraversionIntercept ~~ ChildExtraversionSlope
"

fit.ChildUnivariateExtra <- growth(
  model = Child_Univariate_Extraversion,
  data = ZSCORED,
  missing = "fiml",
  parallel = "multicore"
)
summary(fit.ChildUnivariateExtra, fit.measures = T, std = T)
standardizedSolution(fit.ChildUnivariateExtra)

 
```

#### MOM EXTRAVERSION UNIVARIATE FULL

```{r}
Mom_Univariate_Extraversion_Full <- " #----------------- MOM Univariate Full -----------
#Latent Variables:
W1Extraversion_Mom  =~ NA*m01_E1 + mlambda0*m01_E1 + mlambda1*m01_E2 + mlambda2*m01_E3
W3Extraversion_Mom  =~ NA*m03_E1 + mlambda1*m03_E2 + mlambda2*m03_E3
W5Extraversion_Mom  =~ NA*m05_E1 + mlambda1*m05_E2 + mlambda2*m05_E3
W7Extraversion_Mom  =~ NA*m07_E1 + mlambda1*m07_E2 + m07_E3
W10Extraversion_Mom =~ NA*m10_E1 + mlambda0*m10_E1 + mlambda1*m10_E2 + mlambda2*m10_E3
W11Extraversion_Mom =~ NA*m11_E1 + mlambda0*m11_E1 + mlambda1*m11_E2 + mlambda2*m11_E3
W12Extraversion_Mom =~ NA*m12_E1 + mlambda0*m12_E1 + mlambda1*m12_E2 + mlambda2*m12_E3
W13Extraversion_Mom =~ NA*m13_E1 + mlambda0*m13_E1 + mlambda1*m13_E2 + mlambda2*m13_E3

#Standardizing the latent variables to have a mean of 0 and a Var of 1:
#Latent Variable Means:
W1Extraversion_Mom  ~ 0
W3Extraversion_Mom  ~ 0
W5Extraversion_Mom  ~ 0
W7Extraversion_Mom  ~ 0
W10Extraversion_Mom ~ 0
W11Extraversion_Mom ~ 0
W12Extraversion_Mom ~ 0
W13Extraversion_Mom ~ 0

# Latent Variable Variances
W1Extraversion_Mom  ~~ 1*W1Extraversion_Mom
W3Extraversion_Mom  ~~ 1*W3Extraversion_Mom
W5Extraversion_Mom  ~~ 1*W5Extraversion_Mom
W7Extraversion_Mom  ~~ 1*W7Extraversion_Mom
W10Extraversion_Mom ~~ 1*W10Extraversion_Mom
W11Extraversion_Mom ~~ 1*W11Extraversion_Mom
W12Extraversion_Mom ~~ 1*W12Extraversion_Mom
W13Extraversion_Mom ~~ 1*W13Extraversion_Mom

#Parcel Intercepts ## Note the change in the Strong MI model:
m01_E1 ~ 1
m01_E2 ~ 1
m01_E3 ~ 1

m03_E1 ~ 1
m03_E2 ~ 1
m03_E3 ~ 1

m05_E1 ~ mintercept1*1
m05_E2 ~ 1
m05_E3 ~ 1

m07_E1 ~ mintercept1*1
m07_E2 ~ 1
m07_E3 ~ mintercept3*1

m10_E1 ~ mintercept1*1
m10_E2 ~ mintercept2*1
m10_E3 ~ mintercept3*1

m11_E1 ~ mintercept1*1
m11_E2 ~ mintercept2*1
m11_E3 ~ mintercept3*1

m12_E1 ~ mintercept1*1
m12_E2 ~ mintercept2*1
m12_E3 ~ mintercept3*1

m13_E1 ~ mintercept1*1
m13_E2 ~ mintercept2*1
m13_E3 ~ mintercept3*1

# Parcel variances
m01_E1 ~~ m01_E1
m01_E2 ~~ m01_E2
m01_E3 ~~ m01_E3

m03_E1 ~~ m03_E1
m03_E2 ~~ m03_E2
m03_E3 ~~ m03_E3

m05_E1 ~~ m05_E1
m05_E2 ~~ m05_E2
m05_E3 ~~ m05_E3

m07_E1 ~~ m07_E1
m07_E2 ~~ m07_E2
m07_E3 ~~ m07_E3

m10_E1 ~~ m10_E1
m10_E2 ~~ m10_E2
m10_E3 ~~ m10_E3

m11_E1 ~~ m11_E1
m11_E2 ~~ m11_E2
m11_E3 ~~ m11_E3

m12_E1 ~~ m12_E1
m12_E2 ~~ m12_E2
m12_E3 ~~ m12_E3

m13_E1 ~~ m13_E1
m13_E2 ~~ m13_E2
m13_E3 ~~ m13_E3

# Parcel residual covariances
m01_E1 ~~ m03_E1 + m05_E1 + m07_E1 + m10_E1 + m11_E1 + m12_E1 + m13_E1
m01_E2 ~~ m03_E2 + m05_E2 + m07_E2 + m10_E2 + m11_E2 + m12_E2 + m13_E2
m01_E3 ~~ m03_E3 + m05_E3 + m07_E3 + m10_E3 + m11_E3 + m12_E3 + m13_E3

m03_E1 ~~ m05_E1 + m07_E1 + m10_E1 + m11_E1 + m12_E1 + m13_E1
m03_E2 ~~ m05_E2 + m07_E2 + m10_E2 + m11_E2 + m12_E2 + m13_E2
m03_E3 ~~ m05_E3 + m07_E3 + m10_E3 + m11_E3 + m12_E3 + m13_E3

m05_E1 ~~ m07_E1 + m10_E1 + m11_E1 + m12_E1 + m13_E1
m05_E2 ~~ m07_E2 + m10_E2 + m11_E2 + m12_E2 + m13_E2
m05_E3 ~~ m07_E3 + m10_E3 + m11_E3 + m12_E3 + m13_E3

m07_E1 ~~ m10_E1 + m11_E1 + m12_E1 + m13_E1
m07_E2 ~~ m10_E2 + m11_E2 + m12_E2 + m13_E2
m07_E3 ~~ m10_E3 + m11_E3 + m12_E3 + m13_E3

m10_E1 ~~ m11_E1 + m12_E1 + m13_E1
m10_E2 ~~ m11_E2 + m12_E2 + m13_E2
m10_E3 ~~ m11_E3 + m12_E3 + m13_E3

m11_E1 ~~ m12_E1 + m13_E1
m11_E2 ~~ m12_E2 + m13_E2
m11_E3 ~~ m12_E3 + m13_E3

m12_E1 ~~ m13_E1
m12_E2 ~~ m13_E2
m12_E3 ~~ m13_E3

##Univariate Growth Curve Stuff:
MomExtraversionIntercept =~ 1*W1Extraversion_Mom+1*W3Extraversion_Mom+1*W5Extraversion_Mom+1*W7Extraversion_Mom+1*W10Extraversion_Mom+1*W11Extraversion_Mom+1*W12Extraversion_Mom+1*W13Extraversion_Mom

MomExtraversionSlope =~ -0.764*W1Extraversion_Mom+-0.569*W3Extraversion_Mom+-0.374*W5Extraversion_Mom+-0.17*W7Extraversion_Mom+0.136*W10Extraversion_Mom+0.324*W11Extraversion_Mom+0.468*W12Extraversion_Mom+0.764*W13Extraversion_Mom

MomExtraversionIntercept ~ 0*1
MomExtraversionSlope ~ 1

MomExtraversionIntercept ~~ MomExtraversionIntercept
MomExtraversionSlope ~~ MomExtraversionSlope
MomExtraversionIntercept ~~ MomExtraversionSlope
"
```

#### DAD EXTRAVERSION UNIVARIATE FULL

```{r}
Dad_Extraversion_Univariate_Full <- "## ----------------- DAD UNIVARIATE FULL ------------
#Latent Variables:
W1Extraversion_Dad  =~ NA*d01_E1 + dlambda0*d01_E1 + dlambda1*d01_E2 + dlambda2*d01_E3
W3Extraversion_Dad  =~ NA*d03_E1 + dlambda0*d03_E1 + dlambda1*d03_E2 + dlambda2*d03_E3
W5Extraversion_Dad  =~ NA*d05_E1 + dlambda0*d05_E1 + dlambda1*d05_E2 + dlambda2*d05_E3
W7Extraversion_Dad  =~ NA*d07_E1 + dlambda0*d07_E1 + dlambda1*d07_E2 + dlambda2*d07_E3
W11Extraversion_Dad =~ NA*d11_E1 + dlambda0*d11_E1 + dlambda1*d11_E2 + dlambda2*d11_E3
W12Extraversion_Dad =~ NA*d12_E1 + dlambda0*d12_E1 + dlambda1*d12_E2 + dlambda2*d12_E3
W13Extraversion_Dad =~ NA*d13_E1 + dlambda0*d13_E1 + dlambda1*d13_E2 + dlambda2*d13_E3

#Standardizing the latent variables to have a mean of 0 and a Var of 1:
#Latent Variable Means:
W1Extraversion_Dad  ~ 0
W3Extraversion_Dad  ~ 0
W5Extraversion_Dad  ~ 0
W7Extraversion_Dad  ~ 0
W11Extraversion_Dad ~ 0
W12Extraversion_Dad ~ 0
W13Extraversion_Dad ~ 0

# Latent Variable Variances
W1Extraversion_Dad  ~~ 1*W1Extraversion_Dad
W3Extraversion_Dad  ~~ 1*W3Extraversion_Dad
W5Extraversion_Dad  ~~ 1*W5Extraversion_Dad
W7Extraversion_Dad  ~~ 1*W7Extraversion_Dad
W11Extraversion_Dad ~~ 1*W11Extraversion_Dad
W12Extraversion_Dad ~~ 1*W12Extraversion_Dad
W13Extraversion_Dad ~~ 1*W13Extraversion_Dad

#Parcel Intercepts ## Note the change in the Strong MI model:
d01_E1 ~ 1
d01_E2 ~ 1
d01_E3 ~ 1

d03_E1 ~ 1
d03_E2 ~ 1
d03_E3 ~ 1

d05_E1 ~ dintercept1*1
d05_E2 ~ 1
d05_E3 ~ 1

d07_E1 ~ dintercept1*1
d07_E2 ~ 1
d07_E3 ~ 1

d11_E1 ~ dintercept1*1
d11_E2 ~ dintercept2*1
d11_E3 ~ dintercept3*1

d12_E1 ~ dintercept1*1
d12_E2 ~ dintercept2*1
d12_E3 ~ dintercept3*1

d13_E1 ~ dintercept1*1
d13_E2 ~ dintercept2*1
d13_E3 ~ dintercept3*1

# Parcel variances
d01_E1 ~~ d01_E1
d01_E2 ~~ d01_E2
d01_E3 ~~ d01_E3

d03_E1 ~~ d03_E1
d03_E2 ~~ d03_E2
d03_E3 ~~ d03_E3

d05_E1 ~~ d05_E1
d05_E2 ~~ d05_E2
d05_E3 ~~ d05_E3

d07_E1 ~~ d07_E1
d07_E2 ~~ d07_E2
d07_E3 ~~ d07_E3


d11_E1 ~~ d11_E1
d11_E2 ~~ d11_E2
d11_E3 ~~ d11_E3

d12_E1 ~~ d12_E1
d12_E2 ~~ d12_E2
d12_E3 ~~ d12_E3

d13_E1 ~~ d13_E1
d13_E2 ~~ d13_E2
d13_E3 ~~ d13_E3

# Parcel residual covariances
d01_E1 ~~ d03_E1 + d05_E1 + d07_E1 + d11_E1 + d12_E1 + d13_E1
d01_E2 ~~ d03_E2 + d05_E2 + d07_E2 + d11_E2 + d12_E2 + d13_E2
d01_E3 ~~ d03_E3 + d05_E3 + d07_E3 + d11_E3 + d12_E3 + d13_E3

d03_E1 ~~ d05_E1 + d07_E1 + d11_E1 + d12_E1 + d13_E1
d03_E2 ~~ d05_E2 + d07_E2 + d11_E2 + d12_E2 + d13_E2
d03_E3 ~~ d05_E3 + d07_E3 + d11_E3 + d12_E3 + d13_E3

d05_E1 ~~ d07_E1 + d11_E1 + d12_E1 + d13_E1
d05_E2 ~~ d07_E2 + d11_E2 + d12_E2 + d13_E2
d05_E3 ~~ d07_E3 + d11_E3 + d12_E3 + d13_E3

d07_E1 ~~ d11_E1 + d12_E1 + d13_E1
d07_E2 ~~ d11_E2 + d12_E2 + d13_E2
d07_E3 ~~ d11_E3 + d12_E3 + d13_E3


d11_E1 ~~ d12_E1 + d13_E1
d11_E2 ~~ d12_E2 + d13_E2
d11_E3 ~~ d12_E3 + d13_E3

d12_E1 ~~ d13_E1
d12_E2 ~~ d13_E2
d12_E3 ~~ d13_E3

##Univariate Growth Curve Stuff:
DadExtraversionIntercept =~ 1*W1Extraversion_Dad+1*W3Extraversion_Dad+1*W5Extraversion_Dad+1*W7Extraversion_Dad+1*W11Extraversion_Dad+1*W12Extraversion_Dad+1*W13Extraversion_Dad

DadExtraversionSlope =~ -0.764*W1Extraversion_Dad+-0.569*W3Extraversion_Dad+-0.374*W5Extraversion_Dad+-0.17*W7Extraversion_Dad+0.324*W11Extraversion_Dad+0.468*W12Extraversion_Dad+0.764*W13Extraversion_Dad


DadExtraversionIntercept ~ 0*1
DadExtraversionSlope ~ 1

DadExtraversionIntercept ~~ DadExtraversionIntercept
DadExtraversionSlope ~~ DadExtraversionSlope
DadExtraversionIntercept ~~ DadExtraversionSlope
"
```

### Strictly Overlapping Models:

##### MOM EXTRAVERSION UNIVARIATE Overlap

```{r}
Mom_Univariate_Extraversion_Overlap <- " #----------------- MOM Univariate OVERLAP -----------
#Latent Variables:
W5Extraversion_Mom  =~ NA*m05_E1 + mlambda1*m05_E2 + mlambda2*m05_E3
W7Extraversion_Mom  =~ NA*m07_E1 + mlambda1*m07_E2 + mlambda2*m07_E3
W10Extraversion_Mom =~ NA*m10_E1 + mlambda0*m10_E1 + mlambda1*m10_E2 + mlambda2*m10_E3
W11Extraversion_Mom =~ NA*m11_E1 + mlambda0*m11_E1 + mlambda1*m11_E2 + mlambda2*m11_E3
W12Extraversion_Mom =~ NA*m12_E1 + mlambda0*m12_E1 + mlambda1*m12_E2 + mlambda2*m12_E3
W13Extraversion_Mom =~ NA*m13_E1 + mlambda0*m13_E1 + mlambda1*m13_E2 + mlambda2*m13_E3

#Standardizing the latent variables to have a mean of 0 and a Var of 1:
#Latent Variable Means:
W5Extraversion_Mom  ~ 0
W7Extraversion_Mom  ~ 0
W10Extraversion_Mom ~ 0
W11Extraversion_Mom ~ 0
W12Extraversion_Mom ~ 0
W13Extraversion_Mom ~ 0

# Latent Variable Variances
W5Extraversion_Mom  ~~ 1*W5Extraversion_Mom
W7Extraversion_Mom  ~~ 1*W7Extraversion_Mom
W10Extraversion_Mom ~~ 1*W10Extraversion_Mom
W11Extraversion_Mom ~~ 1*W11Extraversion_Mom
W12Extraversion_Mom ~~ 1*W12Extraversion_Mom
W13Extraversion_Mom ~~ 1*W13Extraversion_Mom

#Parcel Intercepts

m05_E1 ~ mintercept1*1
m05_E2 ~ 1
m05_E3 ~ mintercept3*1

m07_E1 ~ mintercept1*1
m07_E2 ~ 1
m07_E3 ~ mintercept3*1

m10_E1 ~ mintercept1*1
m10_E2 ~ mintercept2*1
m10_E3 ~ mintercept3*1

m11_E1 ~ mintercept1*1
m11_E2 ~ mintercept2*1
m11_E3 ~ mintercept3*1

m12_E1 ~ mintercept1*1
m12_E2 ~ mintercept2*1
m12_E3 ~ mintercept3*1

m13_E1 ~ mintercept1*1
m13_E2 ~ mintercept2*1
m13_E3 ~ mintercept3*1

# Parcel variances

m05_E1 ~~ m05_E1
m05_E2 ~~ m05_E2
m05_E3 ~~ m05_E3

m07_E1 ~~ m07_E1
m07_E2 ~~ m07_E2
m07_E3 ~~ m07_E3

m10_E1 ~~ m10_E1
m10_E2 ~~ m10_E2
m10_E3 ~~ m10_E3

m11_E1 ~~ m11_E1
m11_E2 ~~ m11_E2
m11_E3 ~~ m11_E3

m12_E1 ~~ m12_E1
m12_E2 ~~ m12_E2
m12_E3 ~~ m12_E3

m13_E1 ~~ m13_E1
m13_E2 ~~ m13_E2
m13_E3 ~~ m13_E3

# Parcel residual covariances
m05_E1 ~~ m07_E1 + m10_E1 + m11_E1 + m12_E1 + m13_E1
m05_E2 ~~ m07_E2 + m10_E2 + m11_E2 + m12_E2 + m13_E2
m05_E3 ~~ m07_E3 + m10_E3 + m11_E3 + m12_E3 + m13_E3

m07_E1 ~~ m10_E1 + m11_E1 + m12_E1 + m13_E1
m07_E2 ~~ m10_E2 + m11_E2 + m12_E2 + m13_E2
m07_E3 ~~ m10_E3 + m11_E3 + m12_E3 + m13_E3

m10_E1 ~~ m11_E1 + m12_E1 + m13_E1
m10_E2 ~~ m11_E2 + m12_E2 + m13_E2
m10_E3 ~~ m11_E3 + m12_E3 + m13_E3

m11_E1 ~~ m12_E1 + m13_E1
m11_E2 ~~ m12_E2 + m13_E2
m11_E3 ~~ m12_E3 + m13_E3

m12_E1 ~~ m13_E1
m12_E2 ~~ m13_E2
m12_E3 ~~ m13_E3

##Univariate Growth Curve Stuff:
MomExtraversionIntercept =~ W5Extraversion_Mom+1*W7Extraversion_Mom+1*W10Extraversion_Mom+1*W11Extraversion_Mom+1*W12Extraversion_Mom+1*W13Extraversion_Mom

MomExtraversionSlope =~ -0.569*W5Extraversion_Mom+-0.364*W7Extraversion_Mom+-0.059*W10Extraversion_Mom+0.13*W11Extraversion_Mom+0.274*W12Extraversion_Mom+0.569*W13Extraversion_Mom

MomExtraversionIntercept ~ 0*1
MomExtraversionSlope ~ 1

MomExtraversionIntercept ~~ MomExtraversionIntercept
MomExtraversionSlope ~~ MomExtraversionSlope
MomExtraversionIntercept ~~ MomExtraversionSlope
"
# fit.MomUnivariateExtraversionOverlap = growth(model = Mom_Univariate_Extraversion_Overlap,
#                         data = ZSCORED,
#                         missing = "fiml",
#                         parallel="multicore")

# summary(fit.MomUnivariateExtraversionOverlap, fit.measures=T,std=T)
```

##### DAD EXTRAVERSION UNIVARIATE Overlap

```{r}
Dad_Univariate_Extraversion_Overlap <- " #---------- Dad Uni Extra Overlap -----------
#Latent Variables:
W5Extraversion_Dad  =~ NA*d05_E1 + dlambda0*d05_E1 + dlambda1*d05_E2 + dlambda2*d05_E3
W7Extraversion_Dad  =~ NA*d07_E1 + dlambda0*d07_E1 + dlambda1*d07_E2 + d07_E3
W11Extraversion_Dad =~ NA*d11_E1 + dlambda0*d11_E1 + dlambda1*d11_E2 + dlambda2*d11_E3
W12Extraversion_Dad =~ NA*d12_E1 + dlambda0*d12_E1 + dlambda1*d12_E2 + dlambda2*d12_E3
W13Extraversion_Dad =~ NA*d13_E1 + dlambda0*d13_E1 + dlambda1*d13_E2 + dlambda2*d13_E3

#Standardizing the latent variables to have a mean of 0 and a Var of 1:
#Latent Variable Means:
W5Extraversion_Dad  ~ 0
W7Extraversion_Dad  ~ 0
W11Extraversion_Dad ~ 0
W12Extraversion_Dad ~ 0
W13Extraversion_Dad ~ 0

# Latent Variable Variances
W5Extraversion_Dad  ~~ 1*W5Extraversion_Dad
W7Extraversion_Dad  ~~ 1*W7Extraversion_Dad
W11Extraversion_Dad ~~ 1*W11Extraversion_Dad
W12Extraversion_Dad ~~ 1*W12Extraversion_Dad
W13Extraversion_Dad ~~ 1*W13Extraversion_Dad

#Parcel Intercepts ## Note the change in the Strong MI model:

d05_E1 ~ 1
d05_E2 ~ 1
d05_E3 ~ 1

d07_E1 ~ 1
d07_E2 ~ 1
d07_E3 ~ 1

d11_E1 ~ dintercept1*1
d11_E2 ~ dintercept2*1
d11_E3 ~ 1

d12_E1 ~ dintercept1*1
d12_E2 ~ dintercept2*1
d12_E3 ~ dintercept3*1

d13_E1 ~ dintercept1*1
d13_E2 ~ 1
d13_E3 ~ dintercept3*1

# Parcel variances
d05_E1 ~~ d05_E1
d05_E2 ~~ d05_E2
d05_E3 ~~ d05_E3

d07_E1 ~~ d07_E1
d07_E2 ~~ d07_E2
d07_E3 ~~ d07_E3


d11_E1 ~~ d11_E1
d11_E2 ~~ d11_E2
d11_E3 ~~ d11_E3

d12_E1 ~~ d12_E1
d12_E2 ~~ d12_E2
d12_E3 ~~ d12_E3

d13_E1 ~~ d13_E1
d13_E2 ~~ d13_E2
d13_E3 ~~ d13_E3

# Parcel residual covariances
d05_E1 ~~ d07_E1 + d11_E1 + d12_E1 + d13_E1
d05_E2 ~~ d07_E2 + d11_E2 + d12_E2 + d13_E2
d05_E3 ~~ d07_E3 + d11_E3 + d12_E3 + d13_E3

d07_E1 ~~ d11_E1 + d12_E1 + d13_E1
d07_E2 ~~ d11_E2 + d12_E2 + d13_E2
d07_E3 ~~ d11_E3 + d12_E3 + d13_E3

d11_E1 ~~ d12_E1 + d13_E1
d11_E2 ~~ d12_E2 + d13_E2
d11_E3 ~~ d12_E3 + d13_E3

d12_E1 ~~ d13_E1
d12_E2 ~~ d13_E2
d12_E3 ~~ d13_E3

##Univariate Growth Curve Stuff:
DadExtraversionIntercept =~ 1*W5Extraversion_Dad+1*W7Extraversion_Dad+1*W11Extraversion_Dad+1*W12Extraversion_Dad+1*W13Extraversion_Dad

DadExtraversionSlope =~ -0.569*W5Extraversion_Dad+-0.364*W7Extraversion_Dad+0.13*W11Extraversion_Dad+0.274*W12Extraversion_Dad+0.569*W13Extraversion_Dad


DadExtraversionIntercept ~ 0*1
DadExtraversionSlope ~ 1

DadExtraversionIntercept ~~ DadExtraversionIntercept
DadExtraversionSlope ~~ DadExtraversionSlope
DadExtraversionIntercept ~~ DadExtraversionSlope
"
```

## -------- AGREEABLENESS --------

### Full Trajectory Models:

#### CHILD AGREEABLENESS UNIVARIATE

```{r}
Child_Univariate_Agreeableness <- "#-------------------- ChildPartialStrongAgreeableness --------------------

#Latent Variables:
W5Agreeableness_Child  =~ NA*c05_A1 + clambda0*c05_A1 + clambda1*c05_A2 + clambda2*c05_A3
W7Agreeableness_Child  =~ NA*c07_A1 + clambda0*c07_A1 + clambda1*c07_A2 + clambda2*c07_A3
W10Agreeableness_Child =~ NA*c10_A1 + clambda0*c10_A1 + clambda1*c10_A2 + clambda2*c10_A3
W11Agreeableness_Child =~ NA*c11_A1 + clambda0*c11_A1 + clambda1*c11_A2 + clambda2*c11_A3
W12Agreeableness_Child =~ NA*c12_A1 + clambda0*c12_A1 + clambda1*c12_A2 + clambda2*c12_A3
W13Agreeableness_Child =~ NA*c13_A1 + clambda0*c13_A1 + clambda1*c13_A2 + clambda2*c13_A3

#Standardizing the latent variables to have a mean of 0 and a Var of 1:
#Latent Variable Means:
W5Agreeableness_Child  ~ 0
W7Agreeableness_Child  ~ 0
W10Agreeableness_Child ~ 0
W11Agreeableness_Child ~ 0
W12Agreeableness_Child ~ 0
W13Agreeableness_Child ~ 0

# Latent Variable Variances
W5Agreeableness_Child  ~~ 1*W5Agreeableness_Child
W7Agreeableness_Child  ~~ 1*W7Agreeableness_Child
W10Agreeableness_Child ~~ 1*W10Agreeableness_Child
W11Agreeableness_Child ~~ 1*W11Agreeableness_Child
W12Agreeableness_Child ~~ 1*W12Agreeableness_Child
W13Agreeableness_Child ~~ 1*W13Agreeableness_Child


#Parcel Intercepts
c05_A1 ~ 1
c05_A2 ~ 1
c05_A3 ~ 1

c07_A1 ~ 1
c07_A2 ~ 1
c07_A3 ~ 1


c10_A1 ~ 1
c10_A2 ~ cintercept2*1
c10_A3 ~ 1

c11_A1 ~ cintercept1*1
c11_A2 ~ cintercept2*1
c11_A3 ~ 1

c12_A1 ~ cintercept1*1
c12_A2 ~ 1
c12_A3 ~ 1

c13_A1 ~ 1
c13_A2 ~ cintercept2*1
c13_A3 ~ 1

# Parcel variances
c05_A1 ~~ c05_A1
c05_A2 ~~ c05_A2
c05_A3 ~~ c05_A3

c07_A1 ~~ c07_A1
c07_A2 ~~ c07_A2
c07_A3 ~~ c07_A3

c10_A1 ~~ c10_A1
c10_A2 ~~ c10_A2
c10_A3 ~~ c10_A3

c11_A1 ~~ c11_A1
c11_A2 ~~ c11_A2
c11_A3 ~~ c11_A3

c12_A1 ~~ c12_A1
c12_A2 ~~ c12_A2
c12_A3 ~~ c12_A3

c13_A1 ~~ c13_A1
c13_A2 ~~ c13_A2
c13_A3 ~~ c13_A3


# Parcel residual covariances
c05_A1 ~~ c07_A1 + c10_A1 + c11_A1 + c12_A1 + c13_A1
c05_A2 ~~ c07_A2 + c10_A2 + c11_A2 + c12_A2 + c13_A2
c05_A3 ~~ c07_A3 + c10_A3 + c11_A3 + c12_A3 + c13_A3

c07_A1 ~~ c10_A1 + c11_A1 + c12_A1 + c13_A1
c07_A2 ~~ c10_A2 + c11_A2 + c12_A2 + c13_A2
c07_A3 ~~ c10_A3 + c11_A3 + c12_A3 + c13_A3

c10_A1 ~~ c11_A1 + c12_A1 + c13_A1
c10_A2 ~~ c11_A2 + c12_A2 + c13_A2
c10_A3 ~~ c11_A3 + c12_A3 + c13_A3

c11_A1 ~~ c12_A1 + c13_A1
c11_A2 ~~ c12_A2 + c13_A2
c11_A3 ~~ c12_A3 + c13_A3

c12_A1 ~~ c13_A1
c12_A2 ~~ c13_A2
c12_A3 ~~ c13_A3


##Univariate Growth Curve Stuff:
ChildAgreeablenessIntercept =~ 1*W5Agreeableness_Child+1*W7Agreeableness_Child+1*W10Agreeableness_Child+1*W11Agreeableness_Child+1*W12Agreeableness_Child+1*W13Agreeableness_Child

ChildAgreeablenessSlope =~ -0.569*W5Agreeableness_Child+-0.364*W7Agreeableness_Child+-0.059*W10Agreeableness_Child+0.13*W11Agreeableness_Child+0.274*W12Agreeableness_Child+0.569*W13Agreeableness_Child

ChildAgreeablenessIntercept ~ 0*1
ChildAgreeablenessSlope ~ 1

ChildAgreeablenessIntercept ~~ ChildAgreeablenessIntercept
ChildAgreeablenessSlope ~~ ChildAgreeablenessSlope
ChildAgreeablenessIntercept ~~ ChildAgreeablenessSlope
"
```

#### MOM AGREEABLENESS UNIVARIATE

```{r}
Mom_Univariate_Agreeableness_Full <- " #----------------- MOM Univariate Full AGREE -----------

#Latent Variables:
W1Agreeableness_Mom  =~ NA*m01_A1 + mlambda0*m01_A1 + mlambda1*m01_A2 + mlambda2*m01_A3
W3Agreeableness_Mom  =~ NA*m03_A1 + mlambda0*m03_A1 + mlambda1*m03_A2 + mlambda2*m03_A3
W5Agreeableness_Mom  =~ NA*m05_A1 + mlambda0*m05_A1 + mlambda1*m05_A2 + mlambda2*m05_A3
W7Agreeableness_Mom  =~ NA*m07_A1 + mlambda0*m07_A1 + mlambda1*m07_A2 + mlambda2*m07_A3
W10Agreeableness_Mom =~ NA*m10_A1 + mlambda0*m10_A1 + mlambda1*m10_A2 + mlambda2*m10_A3
W11Agreeableness_Mom =~ NA*m11_A1 + mlambda0*m11_A1 + mlambda1*m11_A2 + mlambda2*m11_A3
W12Agreeableness_Mom =~ NA*m12_A1 + mlambda0*m12_A1 + mlambda1*m12_A2 + mlambda2*m12_A3
W13Agreeableness_Mom =~ NA*m13_A1 + mlambda0*m13_A1 + mlambda1*m13_A2 + mlambda2*m13_A3

#Standardizing the latent variables to have a mean of 0 and a Var of 1:
#Latent Variable Means:
W1Agreeableness_Mom  ~ 0
W3Agreeableness_Mom  ~ 0
W5Agreeableness_Mom  ~ 0
W7Agreeableness_Mom  ~ 0
W10Agreeableness_Mom ~ 0
W11Agreeableness_Mom ~ 0
W12Agreeableness_Mom ~ 0
W13Agreeableness_Mom ~ 0

# Latent Variable Variances
W1Agreeableness_Mom  ~~ 1*W1Agreeableness_Mom
W3Agreeableness_Mom  ~~ 1*W3Agreeableness_Mom
W5Agreeableness_Mom  ~~ 1*W5Agreeableness_Mom
W7Agreeableness_Mom  ~~ 1*W7Agreeableness_Mom
W10Agreeableness_Mom ~~ 1*W10Agreeableness_Mom
W11Agreeableness_Mom ~~ 1*W11Agreeableness_Mom
W12Agreeableness_Mom ~~ 1*W12Agreeableness_Mom
W13Agreeableness_Mom ~~ 1*W13Agreeableness_Mom

#Parcel Intercepts
m01_A1 ~ 1
m01_A2 ~ 1
m01_A3 ~ 1

m03_A1 ~ 1
m03_A2 ~ 1
m03_A3 ~ 1

m05_A1 ~ 1
m05_A2 ~ 1
m05_A3 ~ 1

m07_A1 ~ 1
m07_A2 ~ 1
m07_A3 ~ mintercept3*1

m10_A1 ~ mintercept1*1
m10_A2 ~ mintercept2*1
m10_A3 ~ 1

m11_A1 ~ mintercept1*1
m11_A2 ~ mintercept2*1
m11_A3 ~ 1

m12_A1 ~ mintercept1*1
m12_A2 ~ mintercept2*1
m12_A3 ~ 1

m13_A1 ~ 1
m13_A2 ~ mintercept2*1
m13_A3 ~ 1

# Parcel variances
m01_A1 ~~ m01_A1
m01_A2 ~~ m01_A2
m01_A3 ~~ m01_A3

m03_A1 ~~ m03_A1
m03_A2 ~~ m03_A2
m03_A3 ~~ m03_A3

m05_A1 ~~ m05_A1
m05_A2 ~~ m05_A2
m05_A3 ~~ m05_A3

m07_A1 ~~ m07_A1
m07_A2 ~~ m07_A2
m07_A3 ~~ m07_A3

m10_A1 ~~ m10_A1
m10_A2 ~~ m10_A2
m10_A3 ~~ m10_A3

m11_A1 ~~ m11_A1
m11_A2 ~~ m11_A2
m11_A3 ~~ m11_A3

m12_A1 ~~ m12_A1
m12_A2 ~~ m12_A2
m12_A3 ~~ m12_A3

m13_A1 ~~ m13_A1
m13_A2 ~~ m13_A2
m13_A3 ~~ m13_A3

# Parcel residual covariances
m01_A1 ~~ m03_A1 + m05_A1 + m07_A1 + m10_A1 + m11_A1 + m12_A1 + m13_A1
m01_A2 ~~ m03_A2 + m05_A2 + m07_A2 + m10_A2 + m11_A2 + m12_A2 + m13_A2
m01_A3 ~~ m03_A3 + m05_A3 + m07_A3 + m10_A3 + m11_A3 + m12_A3 + m13_A3

m03_A1 ~~ m05_A1 + m07_A1 + m10_A1 + m11_A1 + m12_A1 + m13_A1
m03_A2 ~~ m05_A2 + m07_A2 + m10_A2 + m11_A2 + m12_A2 + m13_A2
m03_A3 ~~ m05_A3 + m07_A3 + m10_A3 + m11_A3 + m12_A3 + m13_A3

m05_A1 ~~ m07_A1 + m10_A1 + m11_A1 + m12_A1 + m13_A1
m05_A2 ~~ m07_A2 + m10_A2 + m11_A2 + m12_A2 + m13_A2
m05_A3 ~~ m07_A3 + m10_A3 + m11_A3 + m12_A3 + m13_A3

m07_A1 ~~ m10_A1 + m11_A1 + m12_A1 + m13_A1
m07_A2 ~~ m10_A2 + m11_A2 + m12_A2 + m13_A2
m07_A3 ~~ m10_A3 + m11_A3 + m12_A3 + m13_A3

m10_A1 ~~ m11_A1 + m12_A1 + m13_A1
m10_A2 ~~ m11_A2 + m12_A2 + m13_A2
m10_A3 ~~ m11_A3 + m12_A3 + m13_A3

m11_A1 ~~ m12_A1 + m13_A1
m11_A2 ~~ m12_A2 + m13_A2
m11_A3 ~~ m12_A3 + m13_A3

m12_A1 ~~ m13_A1
m12_A2 ~~ m13_A2
m12_A3 ~~ m13_A3

##Univariate Growth Curve Stuff:
MomAgreeablenessIntercept =~ 1*W1Agreeableness_Mom+1*W3Agreeableness_Mom+1*W5Agreeableness_Mom+1*W7Agreeableness_Mom+1*W10Agreeableness_Mom+1*W11Agreeableness_Mom+1*W12Agreeableness_Mom+1*W13Agreeableness_Mom

MomAgreeablenessSlope =~ -0.764*W1Agreeableness_Mom+-0.569*W3Agreeableness_Mom+-0.374*W5Agreeableness_Mom+-0.17*W7Agreeableness_Mom+0.136*W10Agreeableness_Mom+0.324*W11Agreeableness_Mom+0.468*W12Agreeableness_Mom+0.764*W13Agreeableness_Mom

MomAgreeablenessIntercept ~ 0*1
MomAgreeablenessSlope ~ 1

MomAgreeablenessIntercept ~~ MomAgreeablenessIntercept
MomAgreeablenessSlope ~~ MomAgreeablenessSlope
MomAgreeablenessIntercept ~~ MomAgreeablenessSlope
"
```

#### DAD AGREEABLENESS UNIVARIATE

```{r}
Dad_Agreeableness_Univariate_Full <- "## ----------------- DAD UNIVARIATE FULL ------------
#Latent Variables:
W1Agreeableness_Dad  =~ NA*d01_A1 + dlambda0*d01_A1 + dlambda1*d01_A2 + dlambda2*d01_A3
W3Agreeableness_Dad  =~ NA*d03_A1 + dlambda0*d03_A1 + dlambda1*d03_A2 + dlambda2*d03_A3
W5Agreeableness_Dad  =~ NA*d05_A1 + dlambda0*d05_A1 + dlambda1*d05_A2 + dlambda2*d05_A3
W7Agreeableness_Dad  =~ NA*d07_A1 + dlambda1*d07_A2 + dlambda2*d07_A3
W11Agreeableness_Dad =~ NA*d11_A1 + dlambda0*d11_A1 + dlambda1*d11_A2 + dlambda2*d11_A3
W12Agreeableness_Dad =~ NA*d12_A1 + dlambda0*d12_A1 + dlambda1*d12_A2 + dlambda2*d12_A3
W13Agreeableness_Dad =~ NA*d13_A1 + dlambda0*d13_A1 + dlambda1*d13_A2 + dlambda2*d13_A3

#Standardizing the latent variables to have a mean of 0 and a Var of 1:
#Latent Variable Means:
W1Agreeableness_Dad  ~ 0
W3Agreeableness_Dad  ~ 0
W5Agreeableness_Dad  ~ 0
W7Agreeableness_Dad  ~ 0
W11Agreeableness_Dad ~ 0
W12Agreeableness_Dad ~ 0
W13Agreeableness_Dad ~ 0

# Latent Variable Variances
W1Agreeableness_Dad  ~~ 1*W1Agreeableness_Dad
W3Agreeableness_Dad  ~~ 1*W3Agreeableness_Dad
W5Agreeableness_Dad  ~~ 1*W5Agreeableness_Dad
W7Agreeableness_Dad  ~~ 1*W7Agreeableness_Dad
W11Agreeableness_Dad ~~ 1*W11Agreeableness_Dad
W12Agreeableness_Dad ~~ 1*W12Agreeableness_Dad
W13Agreeableness_Dad ~~ 1*W13Agreeableness_Dad

#Parcel Intercepts ## Note the change in the Strong MI model:
d01_A1 ~ 1
d01_A2 ~ 1
d01_A3 ~ dintercept3*1

d03_A1 ~ 1
d03_A2 ~ 1
d03_A3 ~ 1

d05_A1 ~ dintercept1*1
d05_A2 ~ 1
d05_A3 ~ 1

d07_A1 ~ 1
d07_A2 ~ 1
d07_A3 ~ 1

d11_A1 ~ 1
d11_A2 ~ dintercept2*1
d11_A3 ~ 1

d12_A1 ~ 1
d12_A2 ~ dintercept2*1
d12_A3 ~ 1

d13_A1 ~ 1
d13_A2 ~ dintercept2*1
d13_A3 ~ 1

# Parcel variances
d01_A1 ~~ d01_A1
d01_A2 ~~ d01_A2
d01_A3 ~~ d01_A3

d03_A1 ~~ d03_A1
d03_A2 ~~ d03_A2
d03_A3 ~~ d03_A3

d05_A1 ~~ d05_A1
d05_A2 ~~ d05_A2
d05_A3 ~~ d05_A3

d07_A1 ~~ d07_A1
d07_A2 ~~ d07_A2
d07_A3 ~~ d07_A3

d11_A1 ~~ d11_A1
d11_A2 ~~ d11_A2
d11_A3 ~~ d11_A3

d12_A1 ~~ d12_A1
d12_A2 ~~ d12_A2
d12_A3 ~~ d12_A3

d13_A1 ~~ d13_A1
d13_A2 ~~ d13_A2
d13_A3 ~~ d13_A3

# Parcel residual covariances
d01_A1 ~~ d03_A1 + d05_A1 + d07_A1 + d11_A1 + d12_A1 + d13_A1
d01_A2 ~~ d03_A2 + d05_A2 + d07_A2 + d11_A2 + d12_A2 + d13_A2
d01_A3 ~~ d03_A3 + d05_A3 + d07_A3 + d11_A3 + d12_A3 + d13_A3

d03_A1 ~~ d05_A1 + d07_A1 + d11_A1 + d12_A1 + d13_A1
d03_A2 ~~ d05_A2 + d07_A2 + d11_A2 + d12_A2 + d13_A2
d03_A3 ~~ d05_A3 + d07_A3 + d11_A3 + d12_A3 + d13_A3

d05_A1 ~~ d07_A1 + d11_A1 + d12_A1 + d13_A1
d05_A2 ~~ d07_A2 + d11_A2 + d12_A2 + d13_A2
d05_A3 ~~ d07_A3 + d11_A3 + d12_A3 + d13_A3

d07_A1 ~~ d11_A1 + d12_A1 + d13_A1
d07_A2 ~~ d11_A2 + d12_A2 + d13_A2
d07_A3 ~~ d11_A3 + d12_A3 + d13_A3


d11_A1 ~~ d12_A1 + d13_A1
d11_A2 ~~ d12_A2 + d13_A2
d11_A3 ~~ d12_A3 + d13_A3

d12_A1 ~~ d13_A1
d12_A2 ~~ d13_A2
d12_A3 ~~ d13_A3


##Univariate Growth Curve Stuff:
DadAgreeablenessIntercept =~ 1*W1Agreeableness_Dad+1*W3Agreeableness_Dad+1*W5Agreeableness_Dad+1*W7Agreeableness_Dad+1*W11Agreeableness_Dad +1*W12Agreeableness_Dad+1*W13Agreeableness_Dad

DadAgreeablenessSlope =~ -0.764*W1Agreeableness_Dad+-0.569*W3Agreeableness_Dad+-0.374*W5Agreeableness_Dad+-0.17*W7Agreeableness_Dad+0.324*W11Agreeableness_Dad+0.468*W12Agreeableness_Dad+0.764*W13Agreeableness_Dad


DadAgreeablenessIntercept ~ 0*1
DadAgreeablenessSlope ~ 1

DadAgreeablenessIntercept ~~ DadAgreeablenessIntercept
DadAgreeablenessSlope ~~ DadAgreeablenessSlope
DadAgreeablenessIntercept ~~ DadAgreeablenessSlope
"
```

### Strictly Overlapping Models

##### MOM Agreeableness UNIVARIATE Overlap

```{r}
Mom_Univariate_Agreeableness_Overlap <- " #----------------- MOM Univariate OVERLAP -----------
#Latent Variables:
W5Agreeableness_Mom  =~ NA*m05_A1 + mlambda0*m05_A1 + mlambda1*m05_A2 + mlambda2*m05_A3
W7Agreeableness_Mom  =~ NA*m07_A1 + mlambda0*m07_A1 + mlambda1*m07_A2 + mlambda2*m07_A3
W10Agreeableness_Mom =~ NA*m10_A1 + mlambda0*m10_A1 + mlambda1*m10_A2 + mlambda2*m10_A3
W11Agreeableness_Mom =~ NA*m11_A1 + mlambda0*m11_A1 + mlambda1*m11_A2 + mlambda2*m11_A3
W12Agreeableness_Mom =~ NA*m12_A1 + mlambda0*m12_A1 + mlambda1*m12_A2 + mlambda2*m12_A3
W13Agreeableness_Mom =~ NA*m13_A1 + mlambda0*m13_A1 + mlambda1*m13_A2 + mlambda2*m13_A3

#Standardizing the latent variables to have a mean of 0 and a Var of 1:
#Latent Variable Means:
W5Agreeableness_Mom  ~ 0
W7Agreeableness_Mom  ~ 0
W10Agreeableness_Mom ~ 0
W11Agreeableness_Mom ~ 0
W12Agreeableness_Mom ~ 0
W13Agreeableness_Mom ~ 0

# Latent Variable Variances
W5Agreeableness_Mom  ~~ 1*W5Agreeableness_Mom
W7Agreeableness_Mom  ~~ 1*W7Agreeableness_Mom
W10Agreeableness_Mom ~~ 1*W10Agreeableness_Mom
W11Agreeableness_Mom ~~ 1*W11Agreeableness_Mom
W12Agreeableness_Mom ~~ 1*W12Agreeableness_Mom
W13Agreeableness_Mom ~~ 1*W13Agreeableness_Mom

#Parcel Intercepts ## Note the change in the Strong MI model:
m05_A1 ~ 1
m05_A2 ~ 1
m05_A3 ~ 1

m07_A1 ~ 1
m07_A2 ~ 1
m07_A3 ~ mintercept3*1

m10_A1 ~ mintercept1*1
m10_A2 ~ mintercept2*1
m10_A3 ~ 1

m11_A1 ~ mintercept1*1
m11_A2 ~ mintercept2*1
m11_A3 ~ 1

m12_A1 ~ mintercept1*1
m12_A2 ~ mintercept2*1
m12_A3 ~ 1

m13_A1 ~ 1
m13_A2 ~ mintercept2*1
m13_A3 ~ 1

# Parcel variances
m05_A1 ~~ m05_A1
m05_A2 ~~ m05_A2
m05_A3 ~~ m05_A3

m07_A1 ~~ m07_A1
m07_A2 ~~ m07_A2
m07_A3 ~~ m07_A3

m10_A1 ~~ m10_A1
m10_A2 ~~ m10_A2
m10_A3 ~~ m10_A3

m11_A1 ~~ m11_A1
m11_A2 ~~ m11_A2
m11_A3 ~~ m11_A3

m12_A1 ~~ m12_A1
m12_A2 ~~ m12_A2
m12_A3 ~~ m12_A3

m13_A1 ~~ m13_A1
m13_A2 ~~ m13_A2
m13_A3 ~~ m13_A3

# Parcel residual covariances
m05_A1 ~~ m07_A1 + m10_A1 + m11_A1 + m12_A1 + m13_A1
m05_A2 ~~ m07_A2 + m10_A2 + m11_A2 + m12_A2 + m13_A2
m05_A3 ~~ m07_A3 + m10_A3 + m11_A3 + m12_A3 + m13_A3

m07_A1 ~~ m10_A1 + m11_A1 + m12_A1 + m13_A1
m07_A2 ~~ m10_A2 + m11_A2 + m12_A2 + m13_A2
m07_A3 ~~ m10_A3 + m11_A3 + m12_A3 + m13_A3

m10_A1 ~~ m11_A1 + m12_A1 + m13_A1
m10_A2 ~~ m11_A2 + m12_A2 + m13_A2
m10_A3 ~~ m11_A3 + m12_A3 + m13_A3

m11_A1 ~~ m12_A1 + m13_A1
m11_A2 ~~ m12_A2 + m13_A2
m11_A3 ~~ m12_A3 + m13_A3

m12_A1 ~~ m13_A1
m12_A2 ~~ m13_A2
m12_A3 ~~ m13_A3

##Univariate Growth Curve Stuff:
MomAgreeablenessIntercept =~ W5Agreeableness_Mom+1*W7Agreeableness_Mom+1*W10Agreeableness_Mom+1*W11Agreeableness_Mom+1*W12Agreeableness_Mom +1*W13Agreeableness_Mom

MomAgreeablenessSlope =~ -0.569*W5Agreeableness_Mom+-0.364*W7Agreeableness_Mom+-0.059*W10Agreeableness_Mom+0.13*W11Agreeableness_Mom+0.274*W12Agreeableness_Mom+0.569*W13Agreeableness_Mom

MomAgreeablenessIntercept ~ 0*1
MomAgreeablenessSlope ~ 1

MomAgreeablenessIntercept ~~ MomAgreeablenessIntercept
MomAgreeablenessSlope ~~ MomAgreeablenessSlope
MomAgreeablenessIntercept ~~ MomAgreeablenessSlope
"
```

##### DAD Agreeableness UNIVARIATE Overlap

```{r}
Dad_Univariate_Agreeableness_Overlap <- " #---------- Dad Uni Extra Overlap -----------
#Latent Variables:
W5Agreeableness_Dad  =~ NA*d05_A1 + dlambda0*d05_A1 + dlambda1*d05_A2 + dlambda2*d05_A3
W7Agreeableness_Dad  =~ NA*d07_A1 + dlambda1*d07_A2 + dlambda2*d07_A3
W11Agreeableness_Dad =~ NA*d11_A1 + dlambda0*d11_A1 + dlambda1*d11_A2 + dlambda2*d11_A3
W12Agreeableness_Dad =~ NA*d12_A1 + dlambda0*d12_A1 + dlambda1*d12_A2 + dlambda2*d12_A3
W13Agreeableness_Dad =~ NA*d13_A1 + dlambda0*d13_A1 + dlambda1*d13_A2 + dlambda2*d13_A3

#Standardizing the latent variables to have a mean of 0 and a Var of 1:
#Latent Variable Means:
W5Agreeableness_Dad  ~ 0
W7Agreeableness_Dad  ~ 0
W11Agreeableness_Dad ~ 0
W12Agreeableness_Dad ~ 0
W13Agreeableness_Dad ~ 0

# Latent Variable Variances
W5Agreeableness_Dad  ~~ 1*W5Agreeableness_Dad
W7Agreeableness_Dad  ~~ 1*W7Agreeableness_Dad
W11Agreeableness_Dad ~~ 1*W11Agreeableness_Dad
W12Agreeableness_Dad ~~ 1*W12Agreeableness_Dad
W13Agreeableness_Dad ~~ 1*W13Agreeableness_Dad

#Parcel Intercepts
d05_A1 ~ 1
d05_A2 ~ 1
d05_A3 ~ 1

d07_A1 ~ 1
d07_A2 ~ 1
d07_A3 ~ 1

d11_A1 ~ 1
d11_A2 ~ dintercept2*1
d11_A3 ~ 1

d12_A1 ~ dintercept1*1
d12_A2 ~ dintercept2*1
d12_A3 ~ 1

d13_A1 ~ 1
d13_A2 ~ dintercept2*1
d13_A3 ~ 1

# Parcel variances
d05_A1 ~~ d05_A1
d05_A2 ~~ d05_A2
d05_A3 ~~ d05_A3

d07_A1 ~~ d07_A1
d07_A2 ~~ d07_A2
d07_A3 ~~ d07_A3

d11_A1 ~~ d11_A1
d11_A2 ~~ d11_A2
d11_A3 ~~ d11_A3

d12_A1 ~~ d12_A1
d12_A2 ~~ d12_A2
d12_A3 ~~ d12_A3

d13_A1 ~~ d13_A1
d13_A2 ~~ d13_A2
d13_A3 ~~ d13_A3

# Parcel residual covariances
d05_A1 ~~ d07_A1 + d11_A1 + d12_A1 + d13_A1
d05_A2 ~~ d07_A2 + d11_A2 + d12_A2 + d13_A2
d05_A3 ~~ d07_A3 + d11_A3 + d12_A3 + d13_A3

d07_A1 ~~ d11_A1 + d12_A1 + d13_A1
d07_A2 ~~ d11_A2 + d12_A2 + d13_A2
d07_A3 ~~ d11_A3 + d12_A3 + d13_A3

d11_A1 ~~ d12_A1 + d13_A1
d11_A2 ~~ d12_A2 + d13_A2
d11_A3 ~~ d12_A3 + d13_A3

d12_A1 ~~ d13_A1
d12_A2 ~~ d13_A2
d12_A3 ~~ d13_A3


##Univariate Growth Curve Stuff:
DadAgreeablenessIntercept =~ 1*W5Agreeableness_Dad+1*W7Agreeableness_Dad+1*W11Agreeableness_Dad+1*W12Agreeableness_Dad+1*W13Agreeableness_Dad

DadAgreeablenessSlope =~ -0.569*W5Agreeableness_Dad+-0.364*W7Agreeableness_Dad+0.13*W11Agreeableness_Dad+0.274*W12Agreeableness_Dad+0.569*W13Agreeableness_Dad


DadAgreeablenessIntercept ~ 0*1
DadAgreeablenessSlope ~ 1

DadAgreeablenessIntercept ~~ DadAgreeablenessIntercept
DadAgreeablenessSlope ~~ DadAgreeablenessSlope
DadAgreeablenessIntercept ~~ DadAgreeablenessSlope
"
```

## -------- CONSCIENTIOUSNESS --------

### Full Trajectory Models:

##### CHILD CONSCIENTIOUSNESS UNIVARIATE

```{r}
Child_Univariate_Conscientiousness <- "
#-------------------- ChildPartialStrong_1 --------------------
W5Conscientiousness_Child  =~ NA*c05_C1 + clambda0*c05_C1 + clambda1*c05_C2 + clambda2*c05_C3
W7Conscientiousness_Child  =~ NA*c07_C1 + clambda0*c07_C1 + clambda1*c07_C2 + clambda2*c07_C3
W10Conscientiousness_Child =~ NA*c10_C1 + clambda0*c10_C1 + clambda1*c10_C2 + clambda2*c10_C3
W11Conscientiousness_Child =~ NA*c11_C1 + clambda0*c11_C1 + clambda1*c11_C2 + clambda2*c11_C3
W12Conscientiousness_Child =~ NA*c12_C1 + clambda0*c12_C1 + clambda1*c12_C2 + clambda2*c12_C3
W13Conscientiousness_Child =~ NA*c13_C1 + clambda0*c13_C1 + clambda1*c13_C2 + clambda2*c13_C3

#Standardizing the latent variables to have a mean of 0 and a Var of 1:
#Latent Variable Means:
W5Conscientiousness_Child  ~ 0
W7Conscientiousness_Child  ~ 0
W10Conscientiousness_Child ~ 0
W11Conscientiousness_Child ~ 0
W12Conscientiousness_Child ~ 0
W13Conscientiousness_Child ~ 0

# Latent Variable Variances
W5Conscientiousness_Child  ~~ 1*W5Conscientiousness_Child
W7Conscientiousness_Child  ~~ 1*W7Conscientiousness_Child
W10Conscientiousness_Child ~~ 1*W10Conscientiousness_Child
W11Conscientiousness_Child ~~ 1*W11Conscientiousness_Child
W12Conscientiousness_Child ~~ 1*W12Conscientiousness_Child
W13Conscientiousness_Child ~~ 1*W13Conscientiousness_Child

#Parcel Intercepts ## Note the change in the Strong MI model:
c05_C1 ~ cintercept1*1
c05_C2 ~ 1
c05_C3 ~ 1

c07_C1 ~ cintercept1*1
c07_C2 ~ 1
c07_C3 ~ 1

c10_C1 ~ cintercept1*1
c10_C2 ~ 1
c10_C3 ~ 1

c11_C1 ~ cintercept1*1
c11_C2 ~ cintercept2*1
c11_C3 ~ cintercept3*1

c12_C1 ~ cintercept1*1
c12_C2 ~ cintercept2*1
c12_C3 ~ cintercept3*1

c13_C1 ~ cintercept1*1
c13_C2 ~ 1
c13_C3 ~ cintercept3*1

# Parcel variances
c05_C1 ~~ c05_C1
c05_C2 ~~ c05_C2
c05_C3 ~~ c05_C3

c07_C1 ~~ c07_C1
c07_C2 ~~ c07_C2
c07_C3 ~~ c07_C3

c10_C1 ~~ c10_C1
c10_C2 ~~ c10_C2
c10_C3 ~~ c10_C3

c11_C1 ~~ c11_C1
c11_C2 ~~ c11_C2
c11_C3 ~~ c11_C3

c12_C1 ~~ c12_C1
c12_C2 ~~ c12_C2
c12_C3 ~~ c12_C3

c13_C1 ~~ c13_C1
c13_C2 ~~ c13_C2
c13_C3 ~~ c13_C3

# Parcel residual covariances
c05_C1 ~~ c07_C1 + c10_C1 + c11_C1 + c12_C1 + c13_C1
c05_C2 ~~ c07_C2 + c10_C2 + c11_C2 + c12_C2 + c13_C2
c05_C3 ~~ c07_C3 + c10_C3 + c11_C3 + c12_C3 + c13_C3

c07_C1 ~~ c10_C1 + c11_C1 + c12_C1 + c13_C1
c07_C2 ~~ c10_C2 + c11_C2 + c12_C2 + c13_C2
c07_C3 ~~ c10_C3 + c11_C3 + c12_C3 + c13_C3

c10_C1 ~~ c11_C1 + c12_C1 + c13_C1
c10_C2 ~~ c11_C2 + c12_C2 + c13_C2
c10_C3 ~~ c11_C3 + c12_C3 + c13_C3

c11_C1 ~~ c12_C1 + c13_C1
c11_C2 ~~ c12_C2 + c13_C2
c11_C3 ~~ c12_C3 + c13_C3

c12_C1 ~~ c13_C1
c12_C2 ~~ c13_C2
c12_C3 ~~ c13_C3

##Univariate Growth Curve Stuff:
ChildConscientiousnessIntercept =~ 1*W5Conscientiousness_Child+1*W7Conscientiousness_Child+1*W10Conscientiousness_Child+1*W11Conscientiousness_Child+1*W12Conscientiousness_Child+1*W13Conscientiousness_Child

ChildConscientiousnessSlope =~ -0.569*W5Conscientiousness_Child+-0.364*W7Conscientiousness_Child+-0.059*W10Conscientiousness_Child+0.13*W11Conscientiousness_Child+0.274*W12Conscientiousness_Child+0.569*W13Conscientiousness_Child

ChildConscientiousnessIntercept ~ 0*1
ChildConscientiousnessSlope ~ 1

ChildConscientiousnessIntercept ~~ ChildConscientiousnessIntercept
ChildConscientiousnessSlope ~~ ChildConscientiousnessSlope
ChildConscientiousnessIntercept ~~ ChildConscientiousnessSlope
"
```

##### MOM Conscientiousness UNIVARIATE FULL

```{r}
Mom_Univariate_Conscientiousness_Full <- " #----------------- MOM Univariate Full -----------

#Latent Variables:
W1Conscientiousness_Mom  =~ NA*m01_C1 + mlambda0*m01_C1 + mlambda1*m01_C2 + mlambda2*m01_C3
W3Conscientiousness_Mom  =~ NA*m03_C1 + mlambda0*m03_C1 + mlambda1*m03_C2 + mlambda2*m03_C3
W5Conscientiousness_Mom  =~ NA*m05_C1 + mlambda0*m05_C1 + mlambda1*m05_C2 + mlambda2*m05_C3
W7Conscientiousness_Mom  =~ NA*m07_C1 + mlambda0*m07_C1 + mlambda1*m07_C2 + mlambda2*m07_C3
W10Conscientiousness_Mom =~ NA*m10_C1 + mlambda0*m10_C1 + mlambda1*m10_C2 + mlambda2*m10_C3
W11Conscientiousness_Mom =~ NA*m11_C1 + mlambda0*m11_C1 + mlambda1*m11_C2 + mlambda2*m11_C3
W12Conscientiousness_Mom =~ NA*m12_C1 + mlambda0*m12_C1 + mlambda1*m12_C2 + mlambda2*m12_C3
W13Conscientiousness_Mom =~ NA*m13_C1 + mlambda0*m13_C1 + mlambda1*m13_C2 + mlambda2*m13_C3

#Standardizing the latent variables to have a mean of 0 and a Var of 1:
#Latent Variable Means:
W1Conscientiousness_Mom  ~ 0
W3Conscientiousness_Mom  ~ 0
W5Conscientiousness_Mom  ~ 0
W7Conscientiousness_Mom  ~ 0
W10Conscientiousness_Mom ~ 0
W11Conscientiousness_Mom ~ 0
W12Conscientiousness_Mom ~ 0
W13Conscientiousness_Mom ~ 0

# Latent Variable Variances
W1Conscientiousness_Mom  ~~ 1*W1Conscientiousness_Mom
W3Conscientiousness_Mom  ~~ 1*W3Conscientiousness_Mom
W5Conscientiousness_Mom  ~~ 1*W5Conscientiousness_Mom
W7Conscientiousness_Mom  ~~ 1*W7Conscientiousness_Mom
W10Conscientiousness_Mom ~~ 1*W10Conscientiousness_Mom
W11Conscientiousness_Mom ~~ 1*W11Conscientiousness_Mom
W12Conscientiousness_Mom ~~ 1*W12Conscientiousness_Mom
W13Conscientiousness_Mom ~~ 1*W13Conscientiousness_Mom

#Parcel Intercepts ## Note the change in the Strong MI model:
m01_C1 ~ 1
m01_C2 ~ mintercept2*1
m01_C3 ~ 1

m03_C1 ~ 1
m03_C2 ~ 1
m03_C3 ~ 1

m05_C1 ~ mintercept1*1
m05_C2 ~ 1
m05_C3 ~ 1

m07_C1 ~ mintercept1*1
m07_C2 ~ 1
m07_C3 ~ 1

m10_C1 ~ mintercept1*1
m10_C2 ~ mintercept2*1
m10_C3 ~ mintercept3*1

m11_C1 ~ mintercept1*1
m11_C2 ~ 1
m11_C3 ~ mintercept3*1

m12_C1 ~ mintercept1*1
m12_C2 ~ 1
m12_C3 ~ mintercept3*1

m13_C1 ~ mintercept1*1
m13_C2 ~ mintercept2*1
m13_C3 ~ 1

# Parcel variances
m01_C1 ~~ m01_C1
m01_C2 ~~ m01_C2
m01_C3 ~~ m01_C3

m03_C1 ~~ m03_C1
m03_C2 ~~ m03_C2
m03_C3 ~~ m03_C3

m05_C1 ~~ m05_C1
m05_C2 ~~ m05_C2
m05_C3 ~~ m05_C3

m07_C1 ~~ m07_C1
m07_C2 ~~ m07_C2
m07_C3 ~~ m07_C3

m10_C1 ~~ m10_C1
m10_C2 ~~ m10_C2
m10_C3 ~~ m10_C3

m11_C1 ~~ m11_C1
m11_C2 ~~ m11_C2
m11_C3 ~~ m11_C3

m12_C1 ~~ m12_C1
m12_C2 ~~ m12_C2
m12_C3 ~~ m12_C3

m13_C1 ~~ m13_C1
m13_C2 ~~ m13_C2
m13_C3 ~~ m13_C3

# Parcel residual covariances
m01_C1 ~~ m03_C1 + m05_C1 + m07_C1 + m10_C1 + m11_C1 + m12_C1 + m13_C1
m01_C2 ~~ m03_C2 + m05_C2 + m07_C2 + m10_C2 + m11_C2 + m12_C2 + m13_C2
m01_C3 ~~ m03_C3 + m05_C3 + m07_C3 + m10_C3 + m11_C3 + m12_C3 + m13_C3

m03_C1 ~~ m05_C1 + m07_C1 + m10_C1 + m11_C1 + m12_C1 + m13_C1
m03_C2 ~~ m05_C2 + m07_C2 + m10_C2 + m11_C2 + m12_C2 + m13_C2
m03_C3 ~~ m05_C3 + m07_C3 + m10_C3 + m11_C3 + m12_C3 + m13_C3

m05_C1 ~~ m07_C1 + m10_C1 + m11_C1 + m12_C1 + m13_C1
m05_C2 ~~ m07_C2 + m10_C2 + m11_C2 + m12_C2 + m13_C2
m05_C3 ~~ m07_C3 + m10_C3 + m11_C3 + m12_C3 + m13_C3

m07_C1 ~~ m10_C1 + m11_C1 + m12_C1 + m13_C1
m07_C2 ~~ m10_C2 + m11_C2 + m12_C2 + m13_C2
m07_C3 ~~ m10_C3 + m11_C3 + m12_C3 + m13_C3

m10_C1 ~~ m11_C1 + m12_C1 + m13_C1
m10_C2 ~~ m11_C2 + m12_C2 + m13_C2
m10_C3 ~~ m11_C3 + m12_C3 + m13_C3

m11_C1 ~~ m12_C1 + m13_C1
m11_C2 ~~ m12_C2 + m13_C2
m11_C3 ~~ m12_C3 + m13_C3

m12_C1 ~~ m13_C1
m12_C2 ~~ m13_C2
m12_C3 ~~ m13_C3

##Univariate Growth Curve Stuff:
MomConscientiousnessIntercept =~ 1*W1Conscientiousness_Mom+1*W3Conscientiousness_Mom+1*W5Conscientiousness_Mom+1*W7Conscientiousness_Mom+1*W10Conscientiousness_Mom+1*W11Conscientiousness_Mom+1*W12Conscientiousness_Mom+1*W13Conscientiousness_Mom

MomConscientiousnessSlope =~ -0.764*W1Conscientiousness_Mom+-0.569*W3Conscientiousness_Mom+-0.374*W5Conscientiousness_Mom+-0.17*W7Conscientiousness_Mom+0.136*W10Conscientiousness_Mom+0.324*W11Conscientiousness_Mom+0.468*W12Conscientiousness_Mom+0.764*W13Conscientiousness_Mom

MomConscientiousnessIntercept ~ 0*1
MomConscientiousnessSlope ~ 1

MomConscientiousnessIntercept ~~ MomConscientiousnessIntercept
MomConscientiousnessSlope ~~ MomConscientiousnessSlope
MomConscientiousnessIntercept ~~ MomConscientiousnessSlope
"
```

##### DAD Conscientiousness UNIVARIATE FULL

```{r}
Dad_Conscientiousness_Univariate_Full <- "## ----------------- DAD UNIVARIATE FULL ------------
W1Conscientiousness_Dad  =~ NA*d01_C1 + dlambda0*d01_C1 + dlambda1*d01_C2 + dlambda2*d01_C3
W3Conscientiousness_Dad  =~ NA*d03_C1 + dlambda0*d03_C1 + dlambda1*d03_C2 + dlambda2*d03_C3
W5Conscientiousness_Dad  =~ NA*d05_C1 + dlambda0*d05_C1 + dlambda1*d05_C2 + dlambda2*d05_C3
W7Conscientiousness_Dad  =~ NA*d07_C1 + dlambda0*d07_C1 + dlambda1*d07_C2 + dlambda2*d07_C3
W11Conscientiousness_Dad =~ NA*d11_C1 + dlambda0*d11_C1 + dlambda1*d11_C2 + dlambda2*d11_C3
W12Conscientiousness_Dad =~ NA*d12_C1 + dlambda0*d12_C1 + dlambda1*d12_C2 + dlambda2*d12_C3
W13Conscientiousness_Dad =~ NA*d13_C1 + dlambda1*d13_C2 + dlambda2*d13_C3

#Standardizing the latent variables to have a mean of 0 and a Var of 1:
#Latent Variable Means:
W1Conscientiousness_Dad  ~ 0
W3Conscientiousness_Dad  ~ 0
W5Conscientiousness_Dad  ~ 0
W7Conscientiousness_Dad  ~ 0
W11Conscientiousness_Dad ~ 0
W12Conscientiousness_Dad ~ 0
W13Conscientiousness_Dad ~ 0

# Latent Variable Variances
W1Conscientiousness_Dad  ~~ 1*W1Conscientiousness_Dad
W3Conscientiousness_Dad  ~~ 1*W3Conscientiousness_Dad
W5Conscientiousness_Dad  ~~ 1*W5Conscientiousness_Dad
W7Conscientiousness_Dad  ~~ 1*W7Conscientiousness_Dad
W11Conscientiousness_Dad ~~ 1*W11Conscientiousness_Dad
W12Conscientiousness_Dad ~~ 1*W12Conscientiousness_Dad
W13Conscientiousness_Dad ~~ 1*W13Conscientiousness_Dad

#Parcel Intercepts ## Note the change in the Strong MI model:
d01_C1 ~ dintercept1*1
d01_C2 ~ 1
d01_C3 ~ 1

d03_C1 ~ dintercept1*1
d03_C2 ~ 1
d03_C3 ~ dintercept3*1

d05_C1 ~ dintercept1*1
d05_C2 ~ dintercept2*1
d05_C3 ~ dintercept3*1

d07_C1 ~ dintercept1*1
d07_C2 ~ 1
d07_C3 ~ dintercept3*1

d11_C1 ~ dintercept1*1
d11_C2 ~ dintercept2*1
d11_C3 ~ dintercept3*1

d12_C1 ~ dintercept1*1
d12_C2 ~ dintercept2*1
d12_C3 ~ dintercept3*1

d13_C1 ~ dintercept1*1
d13_C2 ~ dintercept2*1
d13_C3 ~ dintercept3*1

# Parcel variances
d01_C1 ~~ d01_C1
d01_C2 ~~ d01_C2
d01_C3 ~~ d01_C3

d03_C1 ~~ d03_C1
d03_C2 ~~ d03_C2
d03_C3 ~~ d03_C3

d05_C1 ~~ d05_C1
d05_C2 ~~ d05_C2
d05_C3 ~~ d05_C3

d07_C1 ~~ d07_C1
d07_C2 ~~ d07_C2
d07_C3 ~~ d07_C3

d11_C1 ~~ d11_C1
d11_C2 ~~ d11_C2
d11_C3 ~~ d11_C3

d12_C1 ~~ d12_C1
d12_C2 ~~ d12_C2
d12_C3 ~~ d12_C3

d13_C1 ~~ d13_C1
d13_C2 ~~ d13_C2
d13_C3 ~~ d13_C3

# Parcel residual covariances
d01_C1 ~~ d03_C1 + d05_C1 + d07_C1 + d11_C1 + d12_C1 + d13_C1
d01_C2 ~~ d03_C2 + d05_C2 + d07_C2 + d11_C2 + d12_C2 + d13_C2
d01_C3 ~~ d03_C3 + d05_C3 + d07_C3 + d11_C3 + d12_C3 + d13_C3

d03_C1 ~~ d05_C1 + d07_C1 + d11_C1 + d12_C1 + d13_C1
d03_C2 ~~ d05_C2 + d07_C2 + d11_C2 + d12_C2 + d13_C2
d03_C3 ~~ d05_C3 + d07_C3 + d11_C3 + d12_C3 + d13_C3

d05_C1 ~~ d07_C1 + d11_C1 + d12_C1 + d13_C1
d05_C2 ~~ d07_C2 + d11_C2 + d12_C2 + d13_C2
d05_C3 ~~ d07_C3 + d11_C3 + d12_C3 + d13_C3

d07_C1 ~~ d11_C1 + d12_C1 + d13_C1
d07_C2 ~~ d11_C2 + d12_C2 + d13_C2
d07_C3 ~~ d11_C3 + d12_C3 + d13_C3


d11_C1 ~~ d12_C1 + d13_C1
d11_C2 ~~ d12_C2 + d13_C2
d11_C3 ~~ d12_C3 + d13_C3

d12_C1 ~~ d13_C1
d12_C2 ~~ d13_C2
d12_C3 ~~ d13_C3

##Univariate Growth Curve Stuff:
DadConscientiousnessIntercept =~ 1*W1Conscientiousness_Dad+1*W3Conscientiousness_Dad+1*W5Conscientiousness_Dad+1*W7Conscientiousness_Dad+1*W11Conscientiousness_Dad+1*W12Conscientiousness_Dad+1*W13Conscientiousness_Dad

DadConscientiousnessSlope =~ -0.764*W1Conscientiousness_Dad+-0.569*W3Conscientiousness_Dad+-0.374*W5Conscientiousness_Dad+-0.17*W7Conscientiousness_Dad+0.324*W11Conscientiousness_Dad+0.468*W12Conscientiousness_Dad+0.764*W13Conscientiousness_Dad

DadConscientiousnessIntercept ~ 0*1
DadConscientiousnessSlope ~ 1

DadConscientiousnessIntercept ~~ DadConscientiousnessIntercept
DadConscientiousnessSlope ~~ DadConscientiousnessSlope
DadConscientiousnessIntercept ~~ DadConscientiousnessSlope
"
```

### Strictly Overlapping Models:

##### MOM Conscientiousness UNIVARIATE FULL

##### MOM Conscientiousness UNIVARIATE Overlap

```{r}
Mom_Univariate_Conscientiousness_Overlap <- " #----------------- MOM Univariate OVERLAP -----------
#Latent Variables:
W5Conscientiousness_Mom  =~ NA*m05_C1 + mlambda0*m05_C1 + mlambda1*m05_C2 + mlambda2*m05_C3
W7Conscientiousness_Mom  =~ NA*m07_C1 + mlambda0*m07_C1 + mlambda1*m07_C2 + mlambda2*m07_C3
W10Conscientiousness_Mom =~ NA*m10_C1 + mlambda0*m10_C1 + mlambda1*m10_C2 + mlambda2*m10_C3
W11Conscientiousness_Mom =~ NA*m11_C1 + mlambda0*m11_C1 + mlambda1*m11_C2 + mlambda2*m11_C3
W12Conscientiousness_Mom =~ NA*m12_C1 + mlambda0*m12_C1 + mlambda1*m12_C2 + mlambda2*m12_C3
W13Conscientiousness_Mom =~ NA*m13_C1 + mlambda0*m13_C1 + mlambda1*m13_C2 + mlambda2*m13_C3

#Standardizing the latent variables to have a mean of 0 and a Var of 1:
#Latent Variable Means:
W5Conscientiousness_Mom  ~ 0
W7Conscientiousness_Mom  ~ 0
W10Conscientiousness_Mom ~ 0
W11Conscientiousness_Mom ~ 0
W12Conscientiousness_Mom ~ 0
W13Conscientiousness_Mom ~ 0

# Latent Variable Variances
W5Conscientiousness_Mom  ~~ 1*W5Conscientiousness_Mom
W7Conscientiousness_Mom  ~~ 1*W7Conscientiousness_Mom
W10Conscientiousness_Mom ~~ 1*W10Conscientiousness_Mom
W11Conscientiousness_Mom ~~ 1*W11Conscientiousness_Mom
W12Conscientiousness_Mom ~~ 1*W12Conscientiousness_Mom
W13Conscientiousness_Mom ~~ 1*W13Conscientiousness_Mom

#Parcel Intercepts ## Note the change in the Strong MI model:
m05_C1 ~ mintercept1*1
m05_C2 ~ mintercept2*1
m05_C3 ~ mintercept3*1

m07_C1 ~ mintercept1*1
m07_C2 ~ mintercept2*1
m07_C3 ~ mintercept3*1

m10_C1 ~ mintercept1*1
m10_C2 ~ mintercept2*1
m10_C3 ~ mintercept3*1

m11_C1 ~ mintercept1*1
m11_C2 ~ mintercept2*1
m11_C3 ~ mintercept3*1

m12_C1 ~ mintercept1*1
m12_C2 ~ mintercept2*1
m12_C3 ~ mintercept3*1

m13_C1 ~ mintercept1*1
m13_C2 ~ mintercept2*1
m13_C3 ~ mintercept3*1

# Parcel variances
m05_C1 ~~ m05_C1
m05_C2 ~~ m05_C2
m05_C3 ~~ m05_C3

m07_C1 ~~ m07_C1
m07_C2 ~~ m07_C2
m07_C3 ~~ m07_C3

m10_C1 ~~ m10_C1
m10_C2 ~~ m10_C2
m10_C3 ~~ m10_C3

m11_C1 ~~ m11_C1
m11_C2 ~~ m11_C2
m11_C3 ~~ m11_C3

m12_C1 ~~ m12_C1
m12_C2 ~~ m12_C2
m12_C3 ~~ m12_C3

m13_C1 ~~ m13_C1
m13_C2 ~~ m13_C2
m13_C3 ~~ m13_C3

# Parcel residual covariances
m05_C1 ~~ m07_C1 + m10_C1 + m11_C1 + m12_C1 + m13_C1
m05_C2 ~~ m07_C2 + m10_C2 + m11_C2 + m12_C2 + m13_C2
m05_C3 ~~ m07_C3 + m10_C3 + m11_C3 + m12_C3 + m13_C3

m07_C1 ~~ m10_C1 + m11_C1 + m12_C1 + m13_C1
m07_C2 ~~ m10_C2 + m11_C2 + m12_C2 + m13_C2
m07_C3 ~~ m10_C3 + m11_C3 + m12_C3 + m13_C3

m10_C1 ~~ m11_C1 + m12_C1 + m13_C1
m10_C2 ~~ m11_C2 + m12_C2 + m13_C2
m10_C3 ~~ m11_C3 + m12_C3 + m13_C3

m11_C1 ~~ m12_C1 + m13_C1
m11_C2 ~~ m12_C2 + m13_C2
m11_C3 ~~ m12_C3 + m13_C3

m12_C1 ~~ m13_C1
m12_C2 ~~ m13_C2
m12_C3 ~~ m13_C3

##Univariate Growth Curve Stuff:
MomConscientiousnessIntercept =~ W5Conscientiousness_Mom+1*W7Conscientiousness_Mom+1*W10Conscientiousness_Mom+1*W11Conscientiousness_Mom+1*W12Conscientiousness_Mom+1*W13Conscientiousness_Mom

MomConscientiousnessSlope =~ -0.569*W5Conscientiousness_Mom+-0.364*W7Conscientiousness_Mom+-0.059*W10Conscientiousness_Mom+0.13*W11Conscientiousness_Mom+0.274*W12Conscientiousness_Mom+0.569*W13Conscientiousness_Mom

MomConscientiousnessIntercept ~ 0*1
MomConscientiousnessSlope ~ 1

MomConscientiousnessIntercept ~~ MomConscientiousnessIntercept
MomConscientiousnessSlope ~~ MomConscientiousnessSlope
MomConscientiousnessIntercept ~~ MomConscientiousnessSlope
"
```

##### DAD Conscientiousness UNIVARIATE Overlap

```{r}
Dad_Univariate_Conscientiousness_Overlap <- " #---------- Dad Uni Consci Overlap -----------
#Latent Variables:
W5Conscientiousness_Dad  =~ NA*d05_C1 + dlambda0*d05_C1 + dlambda1*d05_C2 + dlambda2*d05_C3
W7Conscientiousness_Dad  =~ NA*d07_C1 + dlambda0*d07_C1 + dlambda1*d07_C2 + dlambda2*d07_C3
W11Conscientiousness_Dad =~ NA*d11_C1 + dlambda0*d11_C1 + dlambda1*d11_C2 + dlambda2*d11_C3
W12Conscientiousness_Dad =~ NA*d12_C1 + dlambda0*d12_C1 + dlambda1*d12_C2 + dlambda2*d12_C3
W13Conscientiousness_Dad =~ NA*d13_C1 + dlambda0*d13_C1 + dlambda1*d13_C2 + dlambda2*d13_C3

#Standardizing the latent variables to have a mean of 0 and a Var of 1:
#Latent Variable Means:
W5Conscientiousness_Dad  ~ 0
W7Conscientiousness_Dad  ~ 0
W11Conscientiousness_Dad ~ 0
W12Conscientiousness_Dad ~ 0
W13Conscientiousness_Dad ~ 0

# Latent Variable Variances
W5Conscientiousness_Dad  ~~ 1*W5Conscientiousness_Dad
W7Conscientiousness_Dad  ~~ 1*W7Conscientiousness_Dad
W11Conscientiousness_Dad ~~ 1*W11Conscientiousness_Dad
W12Conscientiousness_Dad ~~ 1*W12Conscientiousness_Dad
W13Conscientiousness_Dad ~~ 1*W13Conscientiousness_Dad

#Parcel Intercepts ## Note the change in the Strong MI model:

d05_C1 ~ dintercept1*1
d05_C2 ~ dintercept2*1
d05_C3 ~ 1

d07_C1 ~ 1
d07_C2 ~ dintercept2*1
d07_C3 ~ 1

d11_C1 ~ 1
d11_C2 ~ dintercept2*1
d11_C3 ~ 1

d12_C1 ~ 1
d12_C2 ~ dintercept2*1
d12_C3 ~ 1

d13_C1 ~ 1
d13_C2 ~ 1
d13_C3 ~ dintercept3*1

# Parcel variances
d05_C1 ~~ d05_C1
d05_C2 ~~ d05_C2
d05_C3 ~~ d05_C3

d07_C1 ~~ d07_C1
d07_C2 ~~ d07_C2
d07_C3 ~~ d07_C3


d11_C1 ~~ d11_C1
d11_C2 ~~ d11_C2
d11_C3 ~~ d11_C3

d12_C1 ~~ d12_C1
d12_C2 ~~ d12_C2
d12_C3 ~~ d12_C3

d13_C1 ~~ d13_C1
d13_C2 ~~ d13_C2
d13_C3 ~~ d13_C3

# Parcel residual covariances
d05_C1 ~~ d07_C1 + d11_C1 + d12_C1 + d13_C1
d05_C2 ~~ d07_C2 + d11_C2 + d12_C2 + d13_C2
d05_C3 ~~ d07_C3 + d11_C3 + d12_C3 + d13_C3

d07_C1 ~~ d11_C1 + d12_C1 + d13_C1
d07_C2 ~~ d11_C2 + d12_C2 + d13_C2
d07_C3 ~~ d11_C3 + d12_C3 + d13_C3

d11_C1 ~~ d12_C1 + d13_C1
d11_C2 ~~ d12_C2 + d13_C2
d11_C3 ~~ d12_C3 + d13_C3

d12_C1 ~~ d13_C1
d12_C2 ~~ d13_C2
d12_C3 ~~ d13_C3

##Univariate Growth Curve Stuff:
DadConscientiousnessIntercept =~ 1*W5Conscientiousness_Dad+1*W7Conscientiousness_Dad+1*W11Conscientiousness_Dad+1*W12Conscientiousness_Dad+1*W13Conscientiousness_Dad

DadConscientiousnessSlope =~ -0.569*W5Conscientiousness_Dad+-0.364*W7Conscientiousness_Dad+0.13*W11Conscientiousness_Dad+0.274*W12Conscientiousness_Dad+0.569*W13Conscientiousness_Dad


DadConscientiousnessIntercept ~ 0
DadConscientiousnessSlope ~ 1

DadConscientiousnessIntercept ~~ DadConscientiousnessIntercept
DadConscientiousnessSlope ~~ DadConscientiousnessSlope
DadConscientiousnessIntercept ~~ DadConscientiousnessSlope
"
```

### -------- NEUROTICISM --------

### Full Trajectory Models:

##### CHILD Neuroticism UNIVARIATE

```{r}
Child_Univariate_Neuroticism <- "
#Latent Variables:
W5Neuroticism_Child  =~ NA*c05_N1 + clambda0*c05_N1 + clambda1*c05_N2 + clambda2*c05_N3
W7Neuroticism_Child  =~ NA*c07_N1 + clambda0*c07_N1 + clambda1*c07_N2 + c07_N3
W10Neuroticism_Child =~ NA*c10_N1 + clambda0*c10_N1 + clambda1*c10_N2 + clambda2*c10_N3
W11Neuroticism_Child =~ NA*c11_N1 + clambda0*c11_N1 + clambda1*c11_N2 + clambda2*c11_N3
W12Neuroticism_Child =~ NA*c12_N1 + clambda0*c12_N1 + clambda1*c12_N2 + clambda2*c12_N3
W13Neuroticism_Child =~ NA*c13_N1 + clambda0*c13_N1 + clambda1*c13_N2 + clambda2*c13_N3

#Standardizing the latent variables to have a mean of 0 and a Var of 1:
#Latent Variable Means:
W5Neuroticism_Child  ~ 0
W7Neuroticism_Child  ~ 0
W10Neuroticism_Child ~ 0
W11Neuroticism_Child ~ 0
W12Neuroticism_Child ~ 0
W13Neuroticism_Child ~ 0

# Latent Variable Variances
W5Neuroticism_Child  ~~ 1*W5Neuroticism_Child
W7Neuroticism_Child  ~~ 1*W7Neuroticism_Child
W10Neuroticism_Child ~~ 1*W10Neuroticism_Child
W11Neuroticism_Child ~~ 1*W11Neuroticism_Child
W12Neuroticism_Child ~~ 1*W12Neuroticism_Child
W13Neuroticism_Child ~~ 1*W13Neuroticism_Child

#Parcel Intercepts
c05_N1 ~ 1
c05_N2 ~ 1
c05_N3 ~ 1

c07_N1 ~ 1
c07_N2 ~ 1
c07_N3 ~ 1

c10_N1 ~ cintercept1*1
c10_N2 ~ cintercept2*1
c10_N3 ~ cintercept3*1

c11_N1 ~ cintercept1*1
c11_N2 ~ 1
c11_N3 ~ cintercept3*1

c12_N1 ~ cintercept1*1
c12_N2 ~ cintercept2*1
c12_N3 ~ cintercept3*1

c13_N1 ~ cintercept1*1
c13_N2 ~ cintercept2*1
c13_N3 ~ cintercept3*1

# Parcel variances
c05_N1 ~~ c05_N1
c05_N2 ~~ c05_N2
c05_N3 ~~ c05_N3

c07_N1 ~~ c07_N1
c07_N2 ~~ c07_N2
c07_N3 ~~ c07_N3

c10_N1 ~~ c10_N1
c10_N2 ~~ c10_N2
c10_N3 ~~ c10_N3

c11_N1 ~~ c11_N1
c11_N2 ~~ c11_N2
c11_N3 ~~ c11_N3

c12_N1 ~~ c12_N1
c12_N2 ~~ c12_N2
c12_N3 ~~ c12_N3

c13_N1 ~~ c13_N1
c13_N2 ~~ c13_N2
c13_N3 ~~ c13_N3

# Parcel residual covariances
c05_N1 ~~ c07_N1 + c10_N1 + c11_N1 + c12_N1 + c13_N1
c05_N2 ~~ c07_N2 + c10_N2 + c11_N2 + c12_N2 + c13_N2
c05_N3 ~~ c07_N3 + c10_N3 + c11_N3 + c12_N3 + c13_N3

c07_N1 ~~ c10_N1 + c11_N1 + c12_N1 + c13_N1
c07_N2 ~~ c10_N2 + c11_N2 + c12_N2 + c13_N2
c07_N3 ~~ c10_N3 + c11_N3 + c12_N3 + c13_N3

c10_N1 ~~ c11_N1 + c12_N1 + c13_N1
c10_N2 ~~ c11_N2 + c12_N2 + c13_N2
c10_N3 ~~ c11_N3 + c12_N3 + c13_N3

c11_N1 ~~ c12_N1 + c13_N1
c11_N2 ~~ c12_N2 + c13_N2
c11_N3 ~~ c12_N3 + c13_N3

c12_N1 ~~ c13_N1
c12_N2 ~~ c13_N2
c12_N3 ~~ c13_N3

##Univariate Growth Curve Stuff:
ChildNeuroticismIntercept =~ 1*W5Neuroticism_Child+1*W7Neuroticism_Child+1*W10Neuroticism_Child+1*W11Neuroticism_Child+1*W12Neuroticism_Child+1*W13Neuroticism_Child

ChildNeuroticismSlope =~ -0.569*W5Neuroticism_Child+-0.364*W7Neuroticism_Child+-0.059*W10Neuroticism_Child+0.13*W11Neuroticism_Child+0.274*W12Neuroticism_Child+0.569*W13Neuroticism_Child

ChildNeuroticismIntercept ~ 1
ChildNeuroticismSlope ~ 1

ChildNeuroticismIntercept ~~ ChildNeuroticismIntercept
ChildNeuroticismSlope ~~ ChildNeuroticismSlope
ChildNeuroticismIntercept ~~ ChildNeuroticismSlope
"
```

##### MOM Neuroticism UNIVARIATE FULL

```{r}
Mom_Univariate_Neuroticism_Full <- " #----------------- MOM Univariate Full -----------
#Latent Variables:
W1Neuroticism_Mom  =~ NA*m01_N1 + mlambda0*m01_N1 + mlambda1*m01_N2 + mlambda2*m01_N3
W3Neuroticism_Mom  =~ NA*m03_N1 + mlambda1*m03_N2 + mlambda2*m03_N3
W5Neuroticism_Mom  =~ NA*m05_N1 + m05_N2 + mlambda2*m05_N3
W7Neuroticism_Mom  =~ NA*m07_N1 + mlambda1*m07_N2 + mlambda2*m07_N3
W10Neuroticism_Mom =~ NA*m10_N1 + mlambda0*m10_N1 + mlambda1*m10_N2 + mlambda2*m10_N3
W11Neuroticism_Mom =~ NA*m11_N1 + mlambda0*m11_N1 + m11_N2 + lambda2*m11_N3
W12Neuroticism_Mom =~ NA*m12_N1 + mlambda0*m12_N1 + mlambda1*m12_N2 + mlambda2*m12_N3
W13Neuroticism_Mom =~ NA*m13_N1 + mlambda0*m13_N1 + mlambda1*m13_N2 + mlambda2*m13_N3


#Standardizing the latent variables to have a mean of 0 and a Var of 1:
#Latent Variable Means:
W1Neuroticism_Mom  ~ 0
W3Neuroticism_Mom  ~ 0
W5Neuroticism_Mom  ~ 0
W7Neuroticism_Mom  ~ 0
W10Neuroticism_Mom ~ 0
W11Neuroticism_Mom ~ 0
W12Neuroticism_Mom ~ 0
W13Neuroticism_Mom ~ 0

# Latent Variable Variances
W1Neuroticism_Mom  ~~ 1*W1Neuroticism_Mom
W3Neuroticism_Mom  ~~ 1*W3Neuroticism_Mom
W5Neuroticism_Mom  ~~ 1*W5Neuroticism_Mom
W7Neuroticism_Mom  ~~ 1*W7Neuroticism_Mom
W10Neuroticism_Mom ~~ 1*W10Neuroticism_Mom
W11Neuroticism_Mom ~~ 1*W11Neuroticism_Mom
W12Neuroticism_Mom ~~ 1*W12Neuroticism_Mom
W13Neuroticism_Mom ~~ 1*W13Neuroticism_Mom

#Parcel Intercepts ## Note the change in the Strong MI model:
m01_N1 ~ 1
m01_N2 ~ 1
m01_N3 ~ 1

m03_N1 ~ 1
m03_N2 ~ 1
m03_N3 ~ 1

m05_N1 ~ 1
m05_N2 ~ 1
m05_N3 ~ 1

m07_N1 ~ 1
m07_N2 ~ 1
m07_N3 ~ 1

m10_N1 ~ mintercept1*1
m10_N2 ~ mintercept2*1
m10_N3 ~ mintercept3*1

m11_N1 ~ mintercept1*1
m11_N2 ~ mintercept2*1
m11_N3 ~ mintercept3*1

m12_N1 ~ 1
m12_N2 ~ 1
m12_N3 ~ 1

m13_N1 ~ 1
m13_N2 ~ 1
m13_N3 ~ 1

# Parcel variances
m01_N1 ~~ m01_N1
m01_N2 ~~ m01_N2
m01_N3 ~~ m01_N3

m03_N1 ~~ m03_N1
m03_N2 ~~ m03_N2
m03_N3 ~~ m03_N3

m05_N1 ~~ m05_N1
m05_N2 ~~ m05_N2
m05_N3 ~~ m05_N3

m07_N1 ~~ m07_N1
m07_N2 ~~ m07_N2
m07_N3 ~~ m07_N3

m10_N1 ~~ m10_N1
m10_N2 ~~ m10_N2
m10_N3 ~~ m10_N3

m11_N1 ~~ m11_N1
m11_N2 ~~ m11_N2
m11_N3 ~~ m11_N3

m12_N1 ~~ m12_N1
m12_N2 ~~ m12_N2
m12_N3 ~~ m12_N3

m13_N1 ~~ m13_N1
m13_N2 ~~ m13_N2
m13_N3 ~~ m13_N3

# Parcel residual covariances
m01_N1 ~~ m03_N1 + m05_N1 + m07_N1 + m10_N1 + m11_N1 + m12_N1 + m13_N1
m01_N2 ~~ m03_N2 + m05_N2 + m07_N2 + m10_N2 + m11_N2 + m12_N2 + m13_N2
m01_N3 ~~ m03_N3 + m05_N3 + m07_N3 + m10_N3 + m11_N3 + m12_N3 + m13_N3

m03_N1 ~~ m05_N1 + m07_N1 + m10_N1 + m11_N1 + m12_N1 + m13_N1
m03_N2 ~~ m05_N2 + m07_N2 + m10_N2 + m11_N2 + m12_N2 + m13_N2
m03_N3 ~~ m05_N3 + m07_N3 + m10_N3 + m11_N3 + m12_N3 + m13_N3

m05_N1 ~~ m07_N1 + m10_N1 + m11_N1 + m12_N1 + m13_N1
m05_N2 ~~ m07_N2 + m10_N2 + m11_N2 + m12_N2 + m13_N2
m05_N3 ~~ m07_N3 + m10_N3 + m11_N3 + m12_N3 + m13_N3

m07_N1 ~~ m10_N1 + m11_N1 + m12_N1 + m13_N1
m07_N2 ~~ m10_N2 + m11_N2 + m12_N2 + m13_N2
m07_N3 ~~ m10_N3 + m11_N3 + m12_N3 + m13_N3

m10_N1 ~~ m11_N1 + m12_N1 + m13_N1
m10_N2 ~~ m11_N2 + m12_N2 + m13_N2
m10_N3 ~~ m11_N3 + m12_N3 + m13_N3

m11_N1 ~~ m12_N1 + m13_N1
m11_N2 ~~ m12_N2 + m13_N2
m11_N3 ~~ m12_N3 + m13_N3

m12_N1 ~~ m13_N1
m12_N2 ~~ m13_N2
m12_N3 ~~ m13_N3

##Univariate Growth Curve Stuff:
MomNeuroticismIntercept =~ 1*W1Neuroticism_Mom+1*W3Neuroticism_Mom+1*W5Neuroticism_Mom+1*W7Neuroticism_Mom+1*W10Neuroticism_Mom+1*W11Neuroticism_Mom+1*W12Neuroticism_Mom+1*W13Neuroticism_Mom

MomNeuroticismSlope =~ -0.764*W1Neuroticism_Mom+-0.569*W3Neuroticism_Mom+-0.374*W5Neuroticism_Mom+-0.17*W7Neuroticism_Mom+0.136*W10Neuroticism_Mom+0.324*W11Neuroticism_Mom+0.468*W12Neuroticism_Mom+0.764*W13Neuroticism_Mom

MomNeuroticismIntercept ~ 1
MomNeuroticismSlope ~ 1

MomNeuroticismIntercept ~~ MomNeuroticismIntercept
MomNeuroticismSlope ~~ MomNeuroticismSlope
MomNeuroticismIntercept ~~ MomNeuroticismSlope
"
```

##### DAD Neuroticism UNIVARIATE FULL

```{r}
Dad_Neuroticism_Univariate_Full <- "## ----------------- DAD UNIVARIATE FULL ------------
#Latent Variables:
W1Neuroticism_Dad  =~ NA*d01_N1 + dlambda0*d01_N1 + dlambda1*d01_N2 + dlambda2*d01_N3
W3Neuroticism_Dad  =~ NA*d03_N1 + dlambda1*d03_N2 + dlambda2*d03_N3
W5Neuroticism_Dad  =~ NA*d05_N1 + dlambda1*d05_N2 + dlambda2*d05_N3
W7Neuroticism_Dad  =~ NA*d07_N1 + dlambda1*d07_N2 + dlambda2*d07_N3
W11Neuroticism_Dad =~ NA*d11_N1 + dlambda0*d11_N1 + d11_N2 + dlambda2*d11_N3
W12Neuroticism_Dad =~ NA*d12_N1 + dlambda0*d12_N1 + d12_N2 + dlambda2*d12_N3
W13Neuroticism_Dad =~ NA*d13_N1 + dlambda0*d13_N1 + d13_N2 + dlambda2*d13_N3


#Standardizing the latent variables to have a mean of 0 and a Var of 1:
#Latent Variable Means:
W1Neuroticism_Dad  ~ 0
W3Neuroticism_Dad  ~ 0
W5Neuroticism_Dad  ~ 0
W7Neuroticism_Dad  ~ 0
W11Neuroticism_Dad ~ 0
W12Neuroticism_Dad ~ 0
W13Neuroticism_Dad ~ 0

# Latent Variable Variances
W1Neuroticism_Dad  ~~ 1*W1Neuroticism_Dad
W3Neuroticism_Dad  ~~ 1*W3Neuroticism_Dad
W5Neuroticism_Dad  ~~ 1*W5Neuroticism_Dad
W7Neuroticism_Dad  ~~ 1*W7Neuroticism_Dad
W11Neuroticism_Dad ~~ 1*W11Neuroticism_Dad
W12Neuroticism_Dad ~~ 1*W12Neuroticism_Dad
W13Neuroticism_Dad ~~ 1*W13Neuroticism_Dad

#Parcel Intercepts
d01_N1 ~ 1
d01_N2 ~ 1
d01_N3 ~ 1

d03_N1 ~ 1
d03_N2 ~ 1
d03_N3 ~ 1

d05_N1 ~ 1
d05_N2 ~ 1
d05_N3 ~ 1

d07_N1 ~ 1
d07_N2 ~ 1
d07_N3 ~ 1

d11_N1 ~ 1
d11_N2 ~ 1
d11_N3 ~ 1

d12_N1 ~ dintercept1*1
d12_N2 ~ 1
d12_N3 ~ 1

d13_N1 ~ dintercept1*1
d13_N2 ~ 1
d13_N3 ~ 1

# Parcel variances
d01_N1 ~~ d01_N1
d01_N2 ~~ d01_N2
d01_N3 ~~ d01_N3

d03_N1 ~~ d03_N1
d03_N2 ~~ d03_N2
d03_N3 ~~ d03_N3

d05_N1 ~~ d05_N1
d05_N2 ~~ d05_N2
d05_N3 ~~ d05_N3

d07_N1 ~~ d07_N1
d07_N2 ~~ d07_N2
d07_N3 ~~ d07_N3

d11_N1 ~~ d11_N1
d11_N2 ~~ d11_N2
d11_N3 ~~ d11_N3

d12_N1 ~~ d12_N1
d12_N2 ~~ d12_N2
d12_N3 ~~ d12_N3

d13_N1 ~~ d13_N1
d13_N2 ~~ d13_N2
d13_N3 ~~ d13_N3

# Parcel residual covariances
d01_N1 ~~ d03_N1 + d05_N1 + d07_N1 + d11_N1 + d12_N1 + d13_N1
d01_N2 ~~ d03_N2 + d05_N2 + d07_N2 + d11_N2 + d12_N2 + d13_N2
d01_N3 ~~ d03_N3 + d05_N3 + d07_N3 + d11_N3 + d12_N3 + d13_N3

d03_N1 ~~ d05_N1 + d07_N1 + d11_N1 + d12_N1 + d13_N1
d03_N2 ~~ d05_N2 + d07_N2 + d11_N2 + d12_N2 + d13_N2
d03_N3 ~~ d05_N3 + d07_N3 + d11_N3 + d12_N3 + d13_N3

d05_N1 ~~ d07_N1 + d11_N1 + d12_N1 + d13_N1
d05_N2 ~~ d07_N2 + d11_N2 + d12_N2 + d13_N2
d05_N3 ~~ d07_N3 + d11_N3 + d12_N3 + d13_N3

d07_N1 ~~ d11_N1 + d12_N1 + d13_N1
d07_N2 ~~ d11_N2 + d12_N2 + d13_N2
d07_N3 ~~ d11_N3 + d12_N3 + d13_N3


d11_N1 ~~ d12_N1 + d13_N1
d11_N2 ~~ d12_N2 + d13_N2
d11_N3 ~~ d12_N3 + d13_N3

d12_N1 ~~ d13_N1
d12_N2 ~~ d13_N2
d12_N3 ~~ d13_N3

##Univariate Growth Curve Stuff:
DadNeuroticismIntercept =~ 1*W1Neuroticism_Dad+1*W3Neuroticism_Dad+1*W5Neuroticism_Dad+1*W7Neuroticism_Dad+1*W11Neuroticism_Dad+1*W12Neuroticism_Dad+1*W13Neuroticism_Dad

DadNeuroticismSlope =~ -0.764*W1Neuroticism_Dad+-0.569*W3Neuroticism_Dad+-0.374*W5Neuroticism_Dad+-0.17*W7Neuroticism_Dad+0.324*W11Neuroticism_Dad+0.468*W12Neuroticism_Dad+0.764*W13Neuroticism_Dad

DadNeuroticismIntercept ~ 1
DadNeuroticismSlope ~ 1

DadNeuroticismIntercept ~~ DadNeuroticismIntercept
DadNeuroticismSlope ~~ DadNeuroticismSlope
DadNeuroticismIntercept ~~ DadNeuroticismSlope
"
```

### Strictly Overlapping Models:

##### MOM Neuroticism UNIVARIATE Overlap

```{r}
Mom_Univariate_Neuroticism_Overlap <- " #----------------- MOM Univariate OVERLAP -----------
#Latent Variables:
W5Neuroticism_Mom  =~ NA*m05_N1 + mlambda1*m05_N2 + mlambda2*m05_N3
W7Neuroticism_Mom  =~ NA*m07_N1 + mlambda1*m07_N2 + mlambda2*m07_N3
W10Neuroticism_Mom =~ NA*m10_N1 + mlambda0*m10_N1 + m10_N2 + mlambda2*m10_N3
W11Neuroticism_Mom =~ NA*m11_N1 + mlambda0*m11_N1 + m11_N2 + mlambda2*m11_N3
W12Neuroticism_Mom =~ NA*m12_N1 + mlambda0*m12_N1 + mlambda1*m12_N2 + mlambda2*m12_N3
W13Neuroticism_Mom =~ NA*m13_N1 + mlambda0*m13_N1 + mlambda1*m13_N2 + mlambda2*m13_N3

#Standardizing the latent variables to have a mean of 0 and a Var of 1:
#Latent Variable Means:
W5Neuroticism_Mom  ~ 0
W7Neuroticism_Mom  ~ 0
W10Neuroticism_Mom ~ 0
W11Neuroticism_Mom ~ 0
W12Neuroticism_Mom ~ 0
W13Neuroticism_Mom ~ 0

# Latent Variable Variances
W5Neuroticism_Mom  ~~ 1*W5Neuroticism_Mom
W7Neuroticism_Mom  ~~ 1*W7Neuroticism_Mom
W10Neuroticism_Mom ~~ 1*W10Neuroticism_Mom
W11Neuroticism_Mom ~~ 1*W11Neuroticism_Mom
W12Neuroticism_Mom ~~ 1*W12Neuroticism_Mom
W13Neuroticism_Mom ~~ 1*W13Neuroticism_Mom

#Parcel Intercepts
m05_N1 ~ 1
m05_N2 ~ 1
m05_N3 ~ 1

m07_N1 ~ 1
m07_N2 ~ 1
m07_N3 ~ 1

m10_N1 ~ mintercept1*1
m10_N2 ~ mintercept2*1
m10_N3 ~ mintercept3*1

m11_N1 ~ mintercept1*1
m11_N2 ~ 1
m11_N3 ~ mintercept3*1

m12_N1 ~ 1
m12_N2 ~ 1
m12_N3 ~ 1

m13_N1 ~ 1
m13_N2 ~ mintercept2*1
m13_N3 ~ 1


# Parcel variances

m05_N1 ~~ m05_N1
m05_N2 ~~ m05_N2
m05_N3 ~~ m05_N3

m07_N1 ~~ m07_N1
m07_N2 ~~ m07_N2
m07_N3 ~~ m07_N3

m10_N1 ~~ m10_N1
m10_N2 ~~ m10_N2
m10_N3 ~~ m10_N3

m11_N1 ~~ m11_N1
m11_N2 ~~ m11_N2
m11_N3 ~~ m11_N3

m12_N1 ~~ m12_N1
m12_N2 ~~ m12_N2
m12_N3 ~~ m12_N3

m13_N1 ~~ m13_N1
m13_N2 ~~ m13_N2
m13_N3 ~~ m13_N3

# Parcel residual covariances
m05_N1 ~~ m07_N1 + m10_N1 + m11_N1 + m12_N1 + m13_N1
m05_N2 ~~ m07_N2 + m10_N2 + m11_N2 + m12_N2 + m13_N2
m05_N3 ~~ m07_N3 + m10_N3 + m11_N3 + m12_N3 + m13_N3

m07_N1 ~~ m10_N1 + m11_N1 + m12_N1 + m13_N1
m07_N2 ~~ m10_N2 + m11_N2 + m12_N2 + m13_N2
m07_N3 ~~ m10_N3 + m11_N3 + m12_N3 + m13_N3

m10_N1 ~~ m11_N1 + m12_N1 + m13_N1
m10_N2 ~~ m11_N2 + m12_N2 + m13_N2
m10_N3 ~~ m11_N3 + m12_N3 + m13_N3

m11_N1 ~~ m12_N1 + m13_N1
m11_N2 ~~ m12_N2 + m13_N2
m11_N3 ~~ m12_N3 + m13_N3

m12_N1 ~~ m13_N1
m12_N2 ~~ m13_N2
m12_N3 ~~ m13_N3

##Univariate Growth Curve Stuff:
MomNeuroticismIntercept =~ W5Neuroticism_Mom+1*W7Neuroticism_Mom+1*W10Neuroticism_Mom+1*W11Neuroticism_Mom+1*W12Neuroticism_Mom+1*W13Neuroticism_Mom

MomNeuroticismSlope =~ -0.569*W5Neuroticism_Mom+-0.364*W7Neuroticism_Mom+-0.059*W10Neuroticism_Mom+0.13*W11Neuroticism_Mom+0.274*W12Neuroticism_Mom+0.569*W13Neuroticism_Mom

MomNeuroticismIntercept ~ 0*1
MomNeuroticismSlope ~ 1

MomNeuroticismIntercept ~~ MomNeuroticismIntercept
MomNeuroticismSlope ~~ MomNeuroticismSlope
MomNeuroticismIntercept ~~ MomNeuroticismSlope
"
```

##### DAD Neuroticism UNIVARIATE Overlap

```{r}
Dad_Univariate_Neuroticism_Overlap <- " #---------- Dad Uni Consci Overlap -----------
#Latent Variables:
W5Neuroticism_Dad  =~ NA*d05_N1 + dlambda1*d05_N2 + dlambda2*d05_N3
W7Neuroticism_Dad  =~ NA*d07_N1 + dlambda1*d07_N2 + dlambda2*d07_N3
W11Neuroticism_Dad =~ NA*d11_N1 + dlambda0*d11_N1 + d11_N2 + dlambda2*d11_N3
W12Neuroticism_Dad =~ NA*d12_N1 + dlambda0*d12_N1 + d12_N2 + dlambda2*d12_N3
W13Neuroticism_Dad =~ NA*d13_N1 + dlambda0*d13_N1 + d13_N2 + dlambda2*d13_N3


#Standardizing the latent variables to have a mean of 0 and a Var of 1:
#Latent Variable Means:
W5Neuroticism_Dad  ~ 0
W7Neuroticism_Dad  ~ 0
W11Neuroticism_Dad ~ 0
W12Neuroticism_Dad ~ 0
W13Neuroticism_Dad ~ 0

# Latent Variable Variances
W5Neuroticism_Dad  ~~ 1*W5Neuroticism_Dad
W7Neuroticism_Dad  ~~ 1*W7Neuroticism_Dad
W11Neuroticism_Dad ~~ 1*W11Neuroticism_Dad
W12Neuroticism_Dad ~~ 1*W12Neuroticism_Dad
W13Neuroticism_Dad ~~ 1*W13Neuroticism_Dad

#Parcel Intercepts

d05_N1 ~ 1
d05_N2 ~ dintercept2*1
d05_N3 ~ 1

d07_N1 ~ 1
d07_N2 ~ 1
d07_N3 ~ 1

d11_N1 ~ 1
d11_N2 ~ 1
d11_N3 ~ 1

d12_N1 ~ dintercept1*1
d12_N2 ~ 1
d12_N3 ~ 1

d13_N1 ~ dintercept1*1
d13_N2 ~ 1
d13_N3 ~ 1

# Parcel variances
d05_N1 ~~ d05_N1
d05_N2 ~~ d05_N2
d05_N3 ~~ d05_N3

d07_N1 ~~ d07_N1
d07_N2 ~~ d07_N2
d07_N3 ~~ d07_N3

d11_N1 ~~ d11_N1
d11_N2 ~~ d11_N2
d11_N3 ~~ d11_N3

d12_N1 ~~ d12_N1
d12_N2 ~~ d12_N2
d12_N3 ~~ d12_N3

d13_N1 ~~ d13_N1
d13_N2 ~~ d13_N2
d13_N3 ~~ d13_N3

# Parcel residual covariances
d05_N1 ~~ d07_N1 + d11_N1 + d12_N1 + d13_N1
d05_N2 ~~ d07_N2 + d11_N2 + d12_N2 + d13_N2
d05_N3 ~~ d07_N3 + d11_N3 + d12_N3 + d13_N3

d07_N1 ~~ d11_N1 + d12_N1 + d13_N1
d07_N2 ~~ d11_N2 + d12_N2 + d13_N2
d07_N3 ~~ d11_N3 + d12_N3 + d13_N3

d11_N1 ~~ d12_N1 + d13_N1
d11_N2 ~~ d12_N2 + d13_N2
d11_N3 ~~ d12_N3 + d13_N3

d12_N1 ~~ d13_N1
d12_N2 ~~ d13_N2
d12_N3 ~~ d13_N3

##Univariate Growth Curve Stuff:
DadNeuroticismIntercept =~ 1*W5Neuroticism_Dad+1*W7Neuroticism_Dad+1*W11Neuroticism_Dad+1*W12Neuroticism_Dad+1*W13Neuroticism_Dad

DadNeuroticismSlope =~ -0.569*W5Neuroticism_Dad+-0.364*W7Neuroticism_Dad+0.13*W11Neuroticism_Dad+0.274*W12Neuroticism_Dad+0.569*W13Neuroticism_Dad

DadNeuroticismIntercept ~ 0
DadNeuroticismSlope ~ 1

DadNeuroticismIntercept ~~ DadNeuroticismIntercept
DadNeuroticismSlope ~~ DadNeuroticismSlope
DadNeuroticismIntercept ~~ DadNeuroticismSlope
"
```

## -------- OPENNESS --------

### Full Trajectory Models:

##### CHILD Opennesss UNIVARIATE

```{r}
Child_Univariate_Opennesss <- "
#Latent Variables:
W5Opennesss_Child  =~ NA*c05_O1 + clambda0*c05_O1 + clambda1*c05_O2 + clambda2*c05_O3
W7Opennesss_Child  =~ NA*c07_O1 + clambda0*c07_O1 + clambda1*c07_O2 + clambda2*c07_O3
W10Opennesss_Child =~ NA*c10_O1 + clambda0*c10_O1 + clambda1*c10_O2 + clambda2*c10_O3
W11Opennesss_Child =~ NA*c11_O1 + clambda0*c11_O1 + clambda1*c11_O2 + clambda2*c11_O3
W12Opennesss_Child =~ NA*c12_O1 + clambda0*c12_O1 + clambda1*c12_O2 + clambda2*c12_O3
W13Opennesss_Child =~ NA*c13_O1 + clambda0*c13_O1 + c13_O2 + clambda2*c13_O3


#Standardizing the latent variables to have a mean of 0 and a Var of 1:
#Latent Variable Means:
W5Opennesss_Child  ~ 0
W7Opennesss_Child  ~ 0
W10Opennesss_Child ~ 0
W11Opennesss_Child ~ 0
W12Opennesss_Child ~ 0
W13Opennesss_Child ~ 0

# Latent Variable Variances
W5Opennesss_Child  ~~ 1*W5Opennesss_Child
W7Opennesss_Child  ~~ 1*W7Opennesss_Child
W10Opennesss_Child ~~ 1*W10Opennesss_Child
W11Opennesss_Child ~~ 1*W11Opennesss_Child
W12Opennesss_Child ~~ 1*W12Opennesss_Child
W13Opennesss_Child ~~ 1*W13Opennesss_Child

#Parcel Intercepts
c05_O1 ~ 1
c05_O2 ~ 1
c05_O3 ~ cintercept3*1

c07_O1 ~ 1
c07_O2 ~ 1
c07_O3 ~ cintercept3*1

c10_O1 ~ 1
c10_O2 ~ 1
c10_O3 ~ cintercept3*1

c11_O1 ~ cintercept1*1
c11_O2 ~ 1
c11_O3 ~ 1

c12_O1 ~ cintercept1*1
c12_O2 ~ 1
c12_O3 ~ cintercept3*1

c13_O1 ~ 1
c13_O2 ~ 1
c13_O3 ~ 1

# Parcel variances
c05_O1 ~~ c05_O1
c05_O2 ~~ c05_O2
c05_O3 ~~ c05_O3

c07_O1 ~~ c07_O1
c07_O2 ~~ c07_O2
c07_O3 ~~ c07_O3

c10_O1 ~~ c10_O1
c10_O2 ~~ c10_O2
c10_O3 ~~ c10_O3

c11_O1 ~~ c11_O1
c11_O2 ~~ c11_O2
c11_O3 ~~ c11_O3

c12_O1 ~~ c12_O1
c12_O2 ~~ c12_O2
c12_O3 ~~ c12_O3

c13_O1 ~~ c13_O1
c13_O2 ~~ c13_O2
c13_O3 ~~ c13_O3

# Parcel residual covariances
c05_O1 ~~ c07_O1 + c10_O1 + c11_O1 + c12_O1 + c13_O1
c05_O2 ~~ c07_O2 + c10_O2 + c11_O2 + c12_O2 + c13_O2
c05_O3 ~~ c07_O3 + c10_O3 + c11_O3 + c12_O3 + c13_O3

c07_O1 ~~ c10_O1 + c11_O1 + c12_O1 + c13_O1
c07_O2 ~~ c10_O2 + c11_O2 + c12_O2 + c13_O2
c07_O3 ~~ c10_O3 + c11_O3 + c12_O3 + c13_O3

c10_O1 ~~ c11_O1 + c12_O1 + c13_O1
c10_O2 ~~ c11_O2 + c12_O2 + c13_O2
c10_O3 ~~ c11_O3 + c12_O3 + c13_O3

c11_O1 ~~ c12_O1 + c13_O1
c11_O2 ~~ c12_O2 + c13_O2
c11_O3 ~~ c12_O3 + c13_O3

c12_O1 ~~ c13_O1
c12_O2 ~~ c13_O2
c12_O3 ~~ c13_O3

##Univariate Growth Curve Stuff:
ChildOpennesssIntercept =~ 1*W5Opennesss_Child+1*W7Opennesss_Child+1*W10Opennesss_Child+1*W11Opennesss_Child+1*W12Opennesss_Child+1*W13Opennesss_Child

ChildOpennesssSlope =~ -0.569*W5Opennesss_Child+-0.364*W7Opennesss_Child+-0.059*W10Opennesss_Child+0.13*W11Opennesss_Child+0.274*W12Opennesss_Child+0.569*W13Opennesss_Child

ChildOpennesssIntercept ~ 1
ChildOpennesssSlope ~ 1

ChildOpennesssIntercept ~~ ChildOpennesssIntercept
ChildOpennesssSlope ~~ ChildOpennesssSlope
ChildOpennesssIntercept ~~ ChildOpennesssSlope
"
```

##### MOM Opennesss UNIVARIATE FULL

```{r}
Mom_Univariate_Opennesss_Full <- " #----------------- MOM Univariate Full -----------
#Latent Variables:
W1Opennesss_Mom  =~ NA*m01_O1 + mlambda1*m01_O2 + mlambda2*m01_O3
W3Opennesss_Mom  =~ NA*m03_O1 + mlambda1*m03_O2 + mlambda2*m03_O3
W5Opennesss_Mom  =~ NA*m05_O1 + mlambda1*m05_O2 + mlambda2*m05_O3
W7Opennesss_Mom  =~ NA*m07_O1 + mlambda1*m07_O2 + mlambda2*m07_O3
W10Opennesss_Mom =~ NA*m10_O1 + mlambda0*m10_O1 + mlambda1*m10_O2 + mlambda2*m10_O3
W11Opennesss_Mom =~ NA*m11_O1 + mlambda0*m11_O1 + mlambda1*m11_O2 + m11_O3
W12Opennesss_Mom =~ NA*m12_O1 + mlambda0*m12_O1 + mlambda1*m12_O2 + m12_O3
W13Opennesss_Mom =~ NA*m13_O1 + mlambda0*m13_O1 + mlambda1*m13_O2 + mlambda2*m13_O3

#Standardizing the latent variables to have a mean of 0 and a Var of 1:
#Latent Variable Means:
W1Opennesss_Mom  ~ 0
W3Opennesss_Mom  ~ 0
W5Opennesss_Mom  ~ 0
W7Opennesss_Mom  ~ 0
W10Opennesss_Mom ~ 0
W11Opennesss_Mom ~ 0
W12Opennesss_Mom ~ 0
W13Opennesss_Mom ~ 0

# Latent Variable Variances
W1Opennesss_Mom  ~~ 1*W1Opennesss_Mom
W3Opennesss_Mom  ~~ 1*W3Opennesss_Mom
W5Opennesss_Mom  ~~ 1*W5Opennesss_Mom
W7Opennesss_Mom  ~~ 1*W7Opennesss_Mom
W10Opennesss_Mom ~~ 1*W10Opennesss_Mom
W11Opennesss_Mom ~~ 1*W11Opennesss_Mom
W12Opennesss_Mom ~~ 1*W12Opennesss_Mom
W13Opennesss_Mom ~~ 1*W13Opennesss_Mom

#Parcel Intercepts
m01_O1 ~ 1
m01_O2 ~ 1
m01_O3 ~ 1

m03_O1 ~ 1
m03_O2 ~ 1
m03_O3 ~ 1

m05_O1 ~ 1
m05_O2 ~ 1
m05_O3 ~ mintercept3*1

m07_O1 ~ 1
m07_O2 ~ 1
m07_O3 ~ mintercept3*1

m10_O1 ~ mintercept1*1
m10_O2 ~ 1
m10_O3 ~ 1

m11_O1 ~ 1
m11_O2 ~ mintercept2*1
m11_O3 ~ 1

m12_O1 ~ 1
m12_O2 ~ 1
m12_O3 ~ 1

m13_O1 ~ 1
m13_O2 ~ 1
m13_O3 ~ 1

# Parcel variances
m01_O1 ~~ m01_O1
m01_O2 ~~ m01_O2
m01_O3 ~~ m01_O3

m03_O1 ~~ m03_O1
m03_O2 ~~ m03_O2
m03_O3 ~~ m03_O3

m05_O1 ~~ m05_O1
m05_O2 ~~ m05_O2
m05_O3 ~~ m05_O3

m07_O1 ~~ m07_O1
m07_O2 ~~ m07_O2
m07_O3 ~~ m07_O3

m10_O1 ~~ m10_O1
m10_O2 ~~ m10_O2
m10_O3 ~~ m10_O3

m11_O1 ~~ m11_O1
m11_O2 ~~ m11_O2
m11_O3 ~~ m11_O3

m12_O1 ~~ m12_O1
m12_O2 ~~ m12_O2
m12_O3 ~~ m12_O3

m13_O1 ~~ m13_O1
m13_O2 ~~ m13_O2
m13_O3 ~~ m13_O3

# Parcel residual covariances
m01_O1 ~~ m03_O1 + m05_O1 + m07_O1 + m10_O1 + m11_O1 + m12_O1 + m13_O1
m01_O2 ~~ m03_O2 + m05_O2 + m07_O2 + m10_O2 + m11_O2 + m12_O2 + m13_O2
m01_O3 ~~ m03_O3 + m05_O3 + m07_O3 + m10_O3 + m11_O3 + m12_O3 + m13_O3

m03_O1 ~~ m05_O1 + m07_O1 + m10_O1 + m11_O1 + m12_O1 + m13_O1
m03_O2 ~~ m05_O2 + m07_O2 + m10_O2 + m11_O2 + m12_O2 + m13_O2
m03_O3 ~~ m05_O3 + m07_O3 + m10_O3 + m11_O3 + m12_O3 + m13_O3

m05_O1 ~~ m07_O1 + m10_O1 + m11_O1 + m12_O1 + m13_O1
m05_O2 ~~ m07_O2 + m10_O2 + m11_O2 + m12_O2 + m13_O2
m05_O3 ~~ m07_O3 + m10_O3 + m11_O3 + m12_O3 + m13_O3

m07_O1 ~~ m10_O1 + m11_O1 + m12_O1 + m13_O1
m07_O2 ~~ m10_O2 + m11_O2 + m12_O2 + m13_O2
m07_O3 ~~ m10_O3 + m11_O3 + m12_O3 + m13_O3

m10_O1 ~~ m11_O1 + m12_O1 + m13_O1
m10_O2 ~~ m11_O2 + m12_O2 + m13_O2
m10_O3 ~~ m11_O3 + m12_O3 + m13_O3

m11_O1 ~~ m12_O1 + m13_O1
m11_O2 ~~ m12_O2 + m13_O2
m11_O3 ~~ m12_O3 + m13_O3

m12_O1 ~~ m13_O1
m12_O2 ~~ m13_O2
m12_O3 ~~ m13_O3

##Univariate Growth Curve Stuff:
MomOpennesssIntercept =~ 1*W1Opennesss_Mom+1*W3Opennesss_Mom+1*W5Opennesss_Mom+1*W7Opennesss_Mom+1*W10Opennesss_Mom+1*W11Opennesss_Mom+ 1*W12Opennesss_Mom+1*W13Opennesss_Mom

MomOpennesssSlope =~ -0.764*W1Opennesss_Mom+-0.569*W3Opennesss_Mom+-0.374*W5Opennesss_Mom+-0.17*W7Opennesss_Mom+0.136*W10Opennesss_Mom+0.324*W11Opennesss_Mom+0.468*W12Opennesss_Mom+0.764*W13Opennesss_Mom

MomOpennesssIntercept ~ 1
MomOpennesssSlope ~ 1

MomOpennesssIntercept ~~ MomOpennesssIntercept
MomOpennesssSlope ~~ MomOpennesssSlope
MomOpennesssIntercept ~~ MomOpennesssSlope
"
```

##### DAD Opennesss UNIVARIATE FULL

```{r}
Dad_Opennesss_Univariate_Full <- "## ----------------- DAD UNIVARIATE FULL ------------
W1Opennesss_Dad  =~ NA*d01_O1 + dlambda0*d01_O1 + dlambda1*d01_O2 + dlambda2*d01_O3
W3Opennesss_Dad  =~ NA*d03_O1 + dlambda0*d03_O1 + dlambda1*d03_O2 + dlambda2*d03_O3
W5Opennesss_Dad  =~ NA*d05_O1 + dlambda0*d05_O1 + dlambda1*d05_O2 + dlambda2*d05_O3
W7Opennesss_Dad  =~ NA*d07_O1 + dlambda0*d07_O1 + dlambda1*d07_O2 + dlambda2*d07_O3
W11Opennesss_Dad =~ NA*d11_O1 + dlambda1*d11_O2 + dlambda2*d11_O3
W12Opennesss_Dad =~ NA*d12_O1 + dlambda1*d12_O2 + dlambda2*d12_O3
W13Opennesss_Dad =~ NA*d13_O1 + dlambda1*d13_O2 + dlambda2*d13_O3


#Standardizing the latent variables to have a mean of 0 and a Var of 1:
#Latent Variable Means:
W1Opennesss_Dad  ~ 0
W3Opennesss_Dad  ~ 0
W5Opennesss_Dad  ~ 0
W7Opennesss_Dad  ~ 0
W11Opennesss_Dad ~ 0
W12Opennesss_Dad ~ 0
W13Opennesss_Dad ~ 0

# Latent Variable Variances
W1Opennesss_Dad  ~~ 1*W1Opennesss_Dad
W3Opennesss_Dad  ~~ 1*W3Opennesss_Dad
W5Opennesss_Dad  ~~ 1*W5Opennesss_Dad
W7Opennesss_Dad  ~~ 1*W7Opennesss_Dad
W11Opennesss_Dad ~~ 1*W11Opennesss_Dad
W12Opennesss_Dad ~~ 1*W12Opennesss_Dad
W13Opennesss_Dad ~~ 1*W13Opennesss_Dad

#Parcel Intercepts
d01_O1 ~ 1
d01_O2 ~ 1
d01_O3 ~ dintercept3*1

d03_O1 ~ 1
d03_O2 ~ 1
d03_O3 ~ dintercept3*1

d05_O1 ~ 1
d05_O2 ~ 1
d05_O3 ~ dintercept3*1

d07_O1 ~ 1
d07_O2 ~ 1
d07_O3 ~ dintercept3*1

d11_O1 ~ 1
d11_O2 ~ 1
d11_O3 ~ 1

d12_O1 ~ 1
d12_O2 ~ 1
d12_O3 ~ 1

d13_O1 ~ 1
d13_O2 ~ 1
d13_O3 ~ 1

# Parcel variances
d01_O1 ~~ d01_O1
d01_O2 ~~ d01_O2
d01_O3 ~~ d01_O3

d03_O1 ~~ d03_O1
d03_O2 ~~ d03_O2
d03_O3 ~~ d03_O3

d05_O1 ~~ d05_O1
d05_O2 ~~ d05_O2
d05_O3 ~~ d05_O3

d07_O1 ~~ d07_O1
d07_O2 ~~ d07_O2
d07_O3 ~~ d07_O3

d11_O1 ~~ d11_O1
d11_O2 ~~ d11_O2
d11_O3 ~~ d11_O3

d12_O1 ~~ d12_O1
d12_O2 ~~ d12_O2
d12_O3 ~~ d12_O3

d13_O1 ~~ d13_O1
d13_O2 ~~ d13_O2
d13_O3 ~~ d13_O3

# Parcel residual covariances
d01_O1 ~~ d03_O1 + d05_O1 + d07_O1 + d11_O1 + d12_O1 + d13_O1
d01_O2 ~~ d03_O2 + d05_O2 + d07_O2 + d11_O2 + d12_O2 + d13_O2
d01_O3 ~~ d03_O3 + d05_O3 + d07_O3 + d11_O3 + d12_O3 + d13_O3

d03_O1 ~~ d05_O1 + d07_O1 + d11_O1 + d12_O1 + d13_O1
d03_O2 ~~ d05_O2 + d07_O2 + d11_O2 + d12_O2 + d13_O2
d03_O3 ~~ d05_O3 + d07_O3 + d11_O3 + d12_O3 + d13_O3

d05_O1 ~~ d07_O1 + d11_O1 + d12_O1 + d13_O1
d05_O2 ~~ d07_O2 + d11_O2 + d12_O2 + d13_O2
d05_O3 ~~ d07_O3 + d11_O3 + d12_O3 + d13_O3

d07_O1 ~~ d11_O1 + d12_O1 + d13_O1
d07_O2 ~~ d11_O2 + d12_O2 + d13_O2
d07_O3 ~~ d11_O3 + d12_O3 + d13_O3


d11_O1 ~~ d12_O1 + d13_O1
d11_O2 ~~ d12_O2 + d13_O2
d11_O3 ~~ d12_O3 + d13_O3

d12_O1 ~~ d13_O1
d12_O2 ~~ d13_O2
d12_O3 ~~ d13_O3

##Univariate Growth Curve Stuff:
DadOpennesssIntercept =~ 1*W1Opennesss_Dad+1*W3Opennesss_Dad+1*W5Opennesss_Dad+1*W7Opennesss_Dad+1*W11Opennesss_Dad+1*W12Opennesss_Dad+1*W13Opennesss_Dad

DadOpennesssSlope =~ -0.764*W1Opennesss_Dad+-0.569*W3Opennesss_Dad+-0.374*W5Opennesss_Dad+-0.17*W7Opennesss_Dad+0.324*W11Opennesss_Dad+0.468*W12Opennesss_Dad+0.764*W13Opennesss_Dad

DadOpennesssIntercept ~ 1
DadOpennesssSlope ~ 1

DadOpennesssIntercept ~~ DadOpennesssIntercept
DadOpennesssSlope ~~ DadOpennesssSlope
DadOpennesssIntercept ~~ DadOpennesssSlope
"
```

### Strictly Overlapping Models:

##### MOM Opennesss UNIVARIATE Overlap

```{r}
Mom_Univariate_Opennesss_Overlap <- " #----------------- MOM Univariate OVERLAP -----------
#Latent Variables:
W5Opennesss_Mom  =~ NA*m05_O1 + mlambda1*m05_O2 + m05_O3
W7Opennesss_Mom  =~ NA*m07_O1 + mlambda1*m07_O2 + m07_O3
W10Opennesss_Mom =~ NA*m10_O1 + mlambda1*m10_O2 + mlambda2*m10_O3
W11Opennesss_Mom =~ NA*m11_O1 + mlambda1*m11_O2 + mlambda2*m11_O3
W12Opennesss_Mom =~ NA*m12_O1 + mlambda0*m12_O1 + mlambda1*m12_O2 + mlambda2*m12_O3
W13Opennesss_Mom =~ NA*m13_O1 + mlambda0*m13_O1 + mlambda1*m13_O2 + mlambda2*m13_O3


#Standardizing the latent variables to have a mean of 0 and a Var of 1:
#Latent Variable Means:
W5Opennesss_Mom  ~ 0
W7Opennesss_Mom  ~ 0
W10Opennesss_Mom ~ 0
W11Opennesss_Mom ~ 0
W12Opennesss_Mom ~ 0
W13Opennesss_Mom ~ 0

# Latent Variable Variances
W5Opennesss_Mom  ~~ 1*W5Opennesss_Mom
W7Opennesss_Mom  ~~ 1*W7Opennesss_Mom
W10Opennesss_Mom ~~ 1*W10Opennesss_Mom
W11Opennesss_Mom ~~ 1*W11Opennesss_Mom
W12Opennesss_Mom ~~ 1*W12Opennesss_Mom
W13Opennesss_Mom ~~ 1*W13Opennesss_Mom

#Parcel Intercepts
m05_O1 ~ 1
m05_O2 ~ 1
m05_O3 ~ mintercept3*1

m07_O1 ~ 1
m07_O2 ~ 1
m07_O3 ~ mintercept3*1

m10_O1 ~ 1
m10_O2 ~ mintercept2*1
m10_O3 ~ 1

m11_O1 ~ 1
m11_O2 ~ mintercept2*1
m11_O3 ~ 1

m12_O1 ~ 1
m12_O2 ~ 1
m12_O3 ~ 1

m13_O1 ~ 1
m13_O2 ~ 1
m13_O3 ~ 1

# Parcel variances

m05_O1 ~~ m05_O1
m05_O2 ~~ m05_O2
m05_O3 ~~ m05_O3

m07_O1 ~~ m07_O1
m07_O2 ~~ m07_O2
m07_O3 ~~ m07_O3

m10_O1 ~~ m10_O1
m10_O2 ~~ m10_O2
m10_O3 ~~ m10_O3

m11_O1 ~~ m11_O1
m11_O2 ~~ m11_O2
m11_O3 ~~ m11_O3

m12_O1 ~~ m12_O1
m12_O2 ~~ m12_O2
m12_O3 ~~ m12_O3

m13_O1 ~~ m13_O1
m13_O2 ~~ m13_O2
m13_O3 ~~ m13_O3

# Parcel residual covariances
m05_O1 ~~ m07_O1 + m10_O1 + m11_O1 + m12_O1 + m13_O1
m05_O2 ~~ m07_O2 + m10_O2 + m11_O2 + m12_O2 + m13_O2
m05_O3 ~~ m07_O3 + m10_O3 + m11_O3 + m12_O3 + m13_O3

m07_O1 ~~ m10_O1 + m11_O1 + m12_O1 + m13_O1
m07_O2 ~~ m10_O2 + m11_O2 + m12_O2 + m13_O2
m07_O3 ~~ m10_O3 + m11_O3 + m12_O3 + m13_O3

m10_O1 ~~ m11_O1 + m12_O1 + m13_O1
m10_O2 ~~ m11_O2 + m12_O2 + m13_O2
m10_O3 ~~ m11_O3 + m12_O3 + m13_O3

m11_O1 ~~ m12_O1 + m13_O1
m11_O2 ~~ m12_O2 + m13_O2
m11_O3 ~~ m12_O3 + m13_O3

m12_O1 ~~ m13_O1
m12_O2 ~~ m13_O2
m12_O3 ~~ m13_O3

##Univariate Growth Curve Stuff:
MomOpennesssIntercept =~ W5Opennesss_Mom+1*W7Opennesss_Mom+1*W10Opennesss_Mom+1*W11Opennesss_Mom+1*W12Opennesss_Mom+1*W13Opennesss_Mom

MomOpennesssSlope =~ -0.569*W5Opennesss_Mom+-0.364*W7Opennesss_Mom+-0.059*W10Opennesss_Mom+0.13*W11Opennesss_Mom+0.274*W12Opennesss_Mom+0.569*W13Opennesss_Mom

MomOpennesssIntercept ~ 0*1
MomOpennesssSlope ~ 1

MomOpennesssIntercept ~~ MomOpennesssIntercept
MomOpennesssSlope ~~ MomOpennesssSlope
MomOpennesssIntercept ~~ MomOpennesssSlope
"
```

##### DAD Opennesss UNIVARIATE Overlap

```{r}
Dad_Univariate_Opennesss_Overlap <- "
#Latent Variables:
W5Opennesss_Dad  =~ NA*d05_O1 + dlambda1*d05_O2 + d05_O3
W7Opennesss_Dad  =~ NA*d07_O1 + dlambda1*d07_O2 + d07_O3
W11Opennesss_Dad =~ NA*d11_O1 + dlambda0*d11_O1 + dlambda1*d11_O2 + dlambda2*d11_O3
W12Opennesss_Dad =~ NA*d12_O1 + dlambda0*d12_O1 + dlambda1*d12_O2 + dlambda2*d12_O3
W13Opennesss_Dad =~ NA*d13_O1 + dlambda0*d13_O1 + dlambda1*d13_O2 + dlambda2*d13_O3

#Standardizing the latent variables to have a mean of 0 and a Var of 1:
#Latent Variable Means:
W5Opennesss_Dad  ~ 0
W7Opennesss_Dad  ~ 0
W11Opennesss_Dad ~ 0
W12Opennesss_Dad ~ 0
W13Opennesss_Dad ~ 0

# Latent Variable Variances
W5Opennesss_Dad  ~~ 1*W5Opennesss_Dad
W7Opennesss_Dad  ~~ 1*W7Opennesss_Dad
W11Opennesss_Dad ~~ 1*W11Opennesss_Dad
W12Opennesss_Dad ~~ 1*W12Opennesss_Dad
W13Opennesss_Dad ~~ 1*W13Opennesss_Dad

#Parcel Intercepts

d05_O1 ~ dintercept1*1
d05_O2 ~ 1
d05_O3 ~ dintercept3*1

d07_O1 ~ dintercept1*1
d07_O2 ~ 1
d07_O3 ~ dintercept3*1

d11_O1 ~ 1
d11_O2 ~ dintercept2*1
d11_O3 ~ 1

d12_O1 ~ 1
d12_O2 ~ 1
d12_O3 ~ 1

d13_O1 ~ 1
d13_O2 ~ 1
d13_O3 ~ 1

# Parcel variances
d05_O1 ~~ d05_O1
d05_O2 ~~ d05_O2
d05_O3 ~~ d05_O3

d07_O1 ~~ d07_O1
d07_O2 ~~ d07_O2
d07_O3 ~~ d07_O3

d11_O1 ~~ d11_O1
d11_O2 ~~ d11_O2
d11_O3 ~~ d11_O3

d12_O1 ~~ d12_O1
d12_O2 ~~ d12_O2
d12_O3 ~~ d12_O3

d13_O1 ~~ d13_O1
d13_O2 ~~ d13_O2
d13_O3 ~~ d13_O3

# Parcel residual covariances
d05_O1 ~~ d07_O1 + d11_O1 + d12_O1 + d13_O1
d05_O2 ~~ d07_O2 + d11_O2 + d12_O2 + d13_O2
d05_O3 ~~ d07_O3 + d11_O3 + d12_O3 + d13_O3

d07_O1 ~~ d11_O1 + d12_O1 + d13_O1
d07_O2 ~~ d11_O2 + d12_O2 + d13_O2
d07_O3 ~~ d11_O3 + d12_O3 + d13_O3

d11_O1 ~~ d12_O1 + d13_O1
d11_O2 ~~ d12_O2 + d13_O2
d11_O3 ~~ d12_O3 + d13_O3

d12_O1 ~~ d13_O1
d12_O2 ~~ d13_O2
d12_O3 ~~ d13_O3


##Univariate Growth Curve Stuff:
DadOpennesssIntercept =~ 1*W5Opennesss_Dad+1*W7Opennesss_Dad+1*W11Opennesss_Dad+1*W12Opennesss_Dad+1*W13Opennesss_Dad

DadOpennesssSlope =~ -0.569*W5Opennesss_Dad+-0.364*W7Opennesss_Dad+0.13*W11Opennesss_Dad+0.274*W12Opennesss_Dad+0.569*W13Opennesss_Dad


DadOpennesssIntercept ~ 0
DadOpennesssSlope ~ 1

DadOpennesssIntercept ~~ DadOpennesssIntercept
DadOpennesssSlope ~~ DadOpennesssSlope
DadOpennesssIntercept ~~ DadOpennesssSlope
"
```

# 2. Combining Models into a Single Table

```{r}
# Univariate Models
# Full Models
ExtraUnivariateFull <- list(Child_Univariate_Extraversion, Mom_Univariate_Extraversion_Full, Dad_Extraversion_Univariate_Full)
AgreeUnivariateFull <- list(Child_Univariate_Agreeableness, Mom_Univariate_Agreeableness_Full, Dad_Agreeableness_Univariate_Full)
ConsciUnivariateFull <- list(Child_Univariate_Conscientiousness, Mom_Univariate_Conscientiousness_Full, Dad_Conscientiousness_Univariate_Full)
NeuroUnivariateFull <- list(Child_Univariate_Neuroticism, Mom_Univariate_Neuroticism_Full, Dad_Neuroticism_Univariate_Full)
OpenUnivariateFull <- list(Child_Univariate_Opennesss, Mom_Univariate_Opennesss_Full, Dad_Opennesss_Univariate_Full)


## Truncated parental trajectories for the overlap models
ExtraUnivariateOverlap <- list(Mom_Univariate_Extraversion_Overlap, Dad_Univariate_Extraversion_Overlap)
AgreeUnivariateOverlap <- list(Mom_Univariate_Agreeableness_Overlap, Dad_Univariate_Agreeableness_Overlap)
ConsciUnivariateOverlap <- list(Mom_Univariate_Conscientiousness_Overlap, Dad_Univariate_Conscientiousness_Overlap)
NeuroUnivariateOverlap <- list(Mom_Univariate_Neuroticism_Overlap, Dad_Univariate_Neuroticism_Overlap)
OpenUnivariateOverlap <- list(Mom_Univariate_Opennesss_Overlap, Dad_Univariate_Opennesss_Overlap)

#
AllUnivariateModelsFull <- list(
  ExtraUnivariateFull,
  AgreeUnivariateFull,
  ConsciUnivariateFull,
  NeuroUnivariateFull,
  OpenUnivariateFull
)

AllUnivariateModelsOverlap <- list(
  ExtraUnivariateOverlap,
  AgreeUnivariateOverlap,
  ConsciUnivariateOverlap,
  NeuroUnivariateOverlap,
  OpenUnivariateOverlap
)


ALLUniMODELS <- list(AllUnivariateModelsFull, AllUnivariateModelsOverlap)

B5Domains <- list(
  "Extraversion",
  "Agreeableness",
  "Conscientiousness",
  "Neuroticism",
  "Opennesss"
)

MonadListFULL <- list("Child", "Mom", "Dad")
MonadListOVERLAP <- list("Mom", "Dad")
Modeltypes <- list("Full", "Overlap")


UnivariateRows <- list()
for (ModelTypeIndex in seq_along(Modeltypes)) {
  for (DomainIndex in seq_along(B5Domains)) {
    if (ModelTypeIndex == 1) {
      ProperMonadList <- MonadListFULL
    } else {
      ProperMonadList <- MonadListOVERLAP
    }

    for (MonadIndex in seq_along(ProperMonadList)) {
      Domain <- B5Domains[[DomainIndex]]
      Monad <- ProperMonadList[[MonadIndex]]
      Dyad1 <- Monad
      Dyad2 <- Monad
      LGCType <- "Univariate"
      TrajectoryType <- Modeltypes[[ModelTypeIndex]]

      LHSDomain <- Domain
      RHS <- Domain

      ModelString <- ALLUniMODELS[[ModelTypeIndex]][[DomainIndex]][[MonadIndex]]
      row_df <- data.frame(Dyad1, Dyad2, LGCType, TrajectoryType, LHSDomain, RHS, ModelString)
      UnivariateRows <- append(UnivariateRows, list(row_df))
    }
  }
}

UnivariateModels <- bind_rows(UnivariateRows)
```

```{r}
nrow(UnivariateModels)
UnivariateModels
```

```{r}
save(UnivariateModels, file = "AllUnivariateModelsTable_LatentSlopeFactor_INCREMENTAL_7_16_2024.RData")
```

# 3. Fitting All Univariate Models

This code allows us to get the the Slope-Intercept Correlations for all UniVar models:

```{r}
UnivariateModelFitObjects <- future_apply(UnivariateModels,
  MARGIN = 1,
  FUN = function(x) {
    lavaan(
      model = x[["ModelString"]], # lavaan and not growth()
      data = ZSCORED,
      missing = "fiml",
      parallel = "multicore",
      estimator = "MLR",
      control = list(
        iter.max = 300,
        em.h1.iter.max = 500
      )
    ) # default
  },
  future.seed = TRUE
)


save(UnivariateModelFitObjects, file = "FittedUnivariateModelsObjects_INCREMENTAL_7_16_2024.RData")


AllUnivariateStandardizedSolutions <- future_lapply(UnivariateModelFitObjects, FUN = {
  function(x) standardizedsolution(x)
}, future.seed = TRUE)
length(AllUnivariateStandardizedSolutions)



UnivariateModels$StandardizedSolution <- AllUnivariateStandardizedSolutions

save(UnivariateModels, file = "AllUnivariateModelsWithStandardizedSolutions_INCREMENTAL_7_16_2024.RData")
```

## a. Extracting Univariate Parameters

```{r}
UnivariateModels
```

```{r}
UnivariateModels$StandardizedSolution[[2]]
```

```{r}
UnivariateModels$StandardizedSolution[[16]]
```

```{r}
GetSlopeInterceptCorrelation <- function(row) {
  # First, we record some values from the row in question
  solution <- row$StandardizedSolution
  person <- row$Dyad1
  domain <- row$LHSDomain
  TrajType <- row$TrajectoryType

  # use the values above to get text that matches the LHS and RHS output

  LatentInterceptText <- paste0(person, domain, "Intercept")
  LatentSlopeText <- paste0(person, domain, "Slope")

  # get the row
  filtered_row <- solution |>
    filter(
      op == "~~",
      lhs == LatentInterceptText,
      rhs == LatentSlopeText
    ) |>
    select(lhs, op, rhs, est.std, pvalue, ci.lower, ci.upper)

  print(filtered_row)

  # add the relevant data back in: we aren't saving this to the original table; we are creating a new one.
  NewRow <- filtered_row |>
    mutate(
      FamilyRole = person,
      Domain = domain,
      TrajectoryType = TrajType
    )

  return(NewRow)
}

UnivariateSlopeInterceptEstimateRows <- future_apply(UnivariateModels,
  MARGIN = 1,
  FUN = function(row) {
    GetSlopeInterceptCorrelation(row)
  }
)
UnivariateSlopeInterceptCorrelations <- do.call(rbind, UnivariateSlopeInterceptEstimateRows)
UnivariateSlopeInterceptCorrelations
write.csv(UnivariateSlopeInterceptCorrelations, "AllUnivariateInterceptSlopeCorrelations__FinalTable_7_16_2024.csv")
# all univariate tables won't change by renaming the constraints
```

## b. Finalizing the Univariate Intercept-Slope Correlations (into a table)

```{r}
UnivariateSI_Table <- UnivariateSlopeInterceptCorrelations |>
  select(TrajectoryType, FamilyRole, Domain, est.std, pvalue, ci.lower, ci.upper) |>
  rename(
    `Model Type` = TrajectoryType,
    `Family Role` = FamilyRole,
    `Correlation Coefficent` = est.std,
    `p value` = pvalue,
    `Lower CI` = ci.lower,
    `Upper CI` = ci.upper
  ) |>
  mutate_if(is.numeric, round, digits = 2) |>
  kable(
    escape = F,
    format = "html"
  ) %>%
  kable_classic(
    full_width = F,
    html_font = "Times New Roman"
  )

UnivariateSI_rows_to_bold <- which(UnivariateSlopeInterceptCorrelations$pvalue < 0.05)

# Apply row formatting
for (row in UnivariateSI_rows_to_bold) {
  UnivariateSI_Table <- UnivariateSI_Table %>% row_spec(row, bold = TRUE)
}

# Print the table
UnivariateSI_Table
```

```{r}
UnivariateModels
```

# ----- Section 2: Bivariate Models ----- ----- ----- ----- ----- -----

# 1. Braiding UNIVARIATE Models into BIVARIATE Models

```{r}
B5Domains <- list(
  "Extraversion",
  "Agreeableness",
  "Conscientiousness",
  "Neuroticism",
  "Opennesss"
)

MonadListFULL <- list("Child", "Mom", "Dad")
MonadListOVERLAP <- list("Mom", "Dad")
Modeltypes <- list("Full", "Overlap")

DyadsFull <- list(
  list("Child", "Mom"),
  list("Child", "Dad"),
  list("Mom", "Dad")
)

DyadsOverlap <- list(
  list("Child", "Mom"),
  list("Child", "Dad")
)

BivariateRows <- list()

for (ModelTypeIndex in seq_along(Modeltypes)) {
  for (DomainIndex in seq_along(B5Domains)) {
    for (DomainIndex2 in seq_along(B5Domains)) {
      if (ModelTypeIndex == 1) {
        ProperDyadList <- DyadsFull
      } else {
        ProperDyadList <- DyadsOverlap
      }

      for (DyadIndex in seq_along(ProperDyadList)) {
        LHSDomain <- B5Domains[[DomainIndex]]
        RHSDomain <- B5Domains[[DomainIndex2]]
        Dyad <- ProperDyadList[[DyadIndex]]
        Dyad1 <- Dyad[[1]]
        Dyad2 <- Dyad[[2]]
        LGCType <- "Bivariate"
        TrajectoryType <- Modeltypes[[ModelTypeIndex]]

        if (ModelTypeIndex == 1) {
          LHS_STRING <- UnivariateModels |>
            filter(
              Dyad1 == Dyad[[1]],
              TrajectoryType == Modeltypes[[ModelTypeIndex]],
              LHSDomain == B5Domains[[DomainIndex]]
            ) |>
            select(ModelString) |>
            pull(ModelString)
        } # Extract the value as a string

        else { ## when modelType ==2, we need the 'Full' Child trajectory and the Overlapped Parental Trajectory
          LHS_STRING <- UnivariateModels |>
            filter(
              Dyad1 == Dyad[[1]],
              TrajectoryType == Modeltypes[[1]],
              LHSDomain == B5Domains[[DomainIndex]]
            ) |>
            select(ModelString) |>
            pull(ModelString)
        }

        RHS_STRING <- UnivariateModels |>
          filter(
            Dyad1 == Dyad[[2]],
            TrajectoryType == Modeltypes[[ModelTypeIndex]],
            LHSDomain == B5Domains[[DomainIndex2]]
          ) |>
          select(ModelString) |>
          pull(ModelString) # Extract the value as a string

        if (ModelTypeIndex == 2 && DomainIndex == 1 && DomainIndex2 == 1) {
          print(Dyad[[1]])
          print(Dyad[[2]])
          print(Modeltypes[[ModelTypeIndex]])
          print(B5Domains[[DomainIndex]])
          print(B5Domains[[DomainIndex2]])
          cat(LHS_STRING)
          cat(RHS_STRING)
        }


        CombinedModelString <- paste(LHS_STRING, RHS_STRING, sep = "\n")

        ### now need to add the bivariate bits
        Line1 <- "###Bivariate Bits:"
        Line2 <- paste(paste0(Dyad1, LHSDomain, "Intercept"), "~~", paste0(Dyad2, RHSDomain, "Intercept"), sep = " ")
        Line3 <- paste(paste0(Dyad1, LHSDomain, "Slope"), "~~", paste0(Dyad2, RHSDomain, "Slope"), sep = " ")
        Line4 <- paste(paste0(Dyad1, LHSDomain, "Intercept"), "~~", paste0(Dyad2, RHSDomain, "Slope"), sep = " ")
        Line5 <- paste(paste0(Dyad2, RHSDomain, "Intercept"), "~~", paste0(Dyad1, LHSDomain, "Slope"), sep = " ")



        BivariateLines <- paste(Line1, Line2, Line3, Line4, Line5, sep = "\n")
        # cat(BivariateLines)
        # cat('\n')

        WholeModel <- paste(CombinedModelString, BivariateLines, sep = "\n")

        row_df <- data.frame(Dyad1, Dyad2, LGCType, TrajectoryType, LHSDomain, RHSDomain, WholeModel)
        BivariateRows <- append(BivariateRows, list(row_df))
      }
    }
  }
}

BivariateModels <- do.call(rbind, BivariateRows)
save(BivariateModels, file = "AllBivariateModelsTable_LatentSlopeFactor_INCREMENTAL_7_16_2024.RData")
BivariateModels
getwd()
```

### a. Bivariate Syntax Checking

```{r}
# Lavvanifyed = future_apply(BivariateModels,
#                               MARGIN = 1,
#                              FUN = function (x) {lavaanify(x)})
# Lavvanifyed[[125]]

cat(BivariateModels$WholeModel[[76]])
## Check that this has Child and MOther
## Check that constraints are not shared // collided in the model namespace (clambda and mlambda instead of lambda)
## Check that the weights are symmetrical and that no wave is 0
# Check passed
```

### b. Fitting the Bivariate Models

```{r}
BivariateModelFitObjects <- future_apply(BivariateModels,
  MARGIN = 1,
  FUN = function(x) {
    lavaan(
      model = x[["WholeModel"]], # using Lavaan and not growth
      data = ZSCORED,
      missing = "fiml", # using fiml and not two.stage
      parallel = "multicore",
      estimator = "MLR",
      start = "default", # https://groups.google.com/g/lavaan/c/mEFEs2lt6kA/m/9vjHGyNlAgAJ
      control = list(
        iter.max = 400,
        em.h1.iter.max = 10000
      )
    )
  },
  future.seed = TRUE
)


save(BivariateModelFitObjects, file = "FittedBivariateModelsObjects_INCREMENTAL_7_17_2024.RData")


AllBivariateStandardizedSolutions <- future_lapply(BivariateModelFitObjects, FUN = {
  function(x) standardizedsolution(x)
}, future.seed = TRUE)

BivariateModels$StandardizedSolution <- AllBivariateStandardizedSolutions

save(BivariateModels, file = "AllBivariateModelsWithStandardizedSolutions_INCREMENTAL_6_17_2024.RData")



BivariateModels
```

### c. Extracting Parameters from Standardized Solution

```{r}
## Gets all the params.
BivariateParameterExtraction <- function(solution, lhs_domain, rhs_domain, lhs_dyad, rhs_dyad, lgctype, trajtype) {
  pairs <- data.frame( # defines the pairs of lhs-rhs bits
    lhs = c(
      paste0(lhs_dyad, lhs_domain, "Intercept"),
      paste0(lhs_dyad, lhs_domain, "Slope"),
      paste0(lhs_dyad, lhs_domain, "Intercept"),
      paste0(lhs_dyad, lhs_domain, "Slope")
    ),
    rhs = c(
      paste0(rhs_dyad, rhs_domain, "Intercept"),
      paste0(rhs_dyad, rhs_domain, "Slope"),
      paste0(rhs_dyad, rhs_domain, "Slope"),
      paste0(rhs_dyad, rhs_domain, "Intercept")
    ),
    stringsAsFactors = FALSE
  )

  # Initialize an empty data frame to store the results
  concatenated_rows <- data.frame()
  # Loop through each pair and extract relevant rows
  for (i in 1:nrow(pairs)) {
    pair <- pairs[i, ]
    filtered_rows <- solution %>%
      filter(op == "~~", lhs == pair$lhs, rhs == pair$rhs) %>%
      select(lhs, op, rhs, est.std, pvalue, ci.lower, ci.upper)

    # Add the dyad and domain information to the filtered rows
    if (nrow(filtered_rows) > 0) {
      filtered_rows <- cbind(
        filtered_rows,
        lhs_dyad = lhs_dyad,
        rhs_dyad = rhs_dyad,
        lhs_domain = lhs_domain,
        rhs_domain = rhs_domain,
        lgctype = lgctype,
        trajectorytype = trajtype
      )
    }

    concatenated_rows <- rbind(concatenated_rows, filtered_rows)
  }

  return(concatenated_rows)
}
```

```{r}
ParamEstimates <- future_apply(BivariateModels,
  MARGIN = 1,
  FUN = function(row) {
    solution <- row[["StandardizedSolution"]]
    BivariateParameterExtraction(solution, row["LHSDomain"], row["RHSDomain"], row["Dyad1"], row["Dyad2"], row["LGCType"], row["TrajectoryType"])
  }
)
# ParameterEstimates
ParameterEstimates <- bind_rows(ParamEstimates)
AllParameterEstimates <- ParameterEstimates
AllParameterEstimates
```

## d. Saving / Loading All Parameter Estimates

```{r}
save(AllParameterEstimates,
  file = "AllInterceptSlopeParameterEstimates_AllBivariateModels_6_8_2024.RData"
)

load("AllInterceptSlopeParameterEstimates_AllBivariateModels_6_8_2024.RData",verbose=T)
  AllParameterEstimates
```

# 2. Making Main Results Tables

```{r}
SlopeSlope_InterceptInterceptParams <- AllParameterEstimates |>
  mutate(ParamType = case_when(
    grepl("Slope", lhs) & grepl("Slope", rhs) ~ "Slope-Slope",
    grepl("Intercept", lhs) & grepl("Intercept", rhs) ~ "Intercept-Intercept",
    grepl("Slope", lhs) & grepl("Intercept", rhs) ~ "Slope-Intercept",
    grepl("Intercept", lhs) & grepl("Slope", rhs) ~ "Intercept-Slope"
  )) |>
  arrange(match(ParamType, c("Slope-Slope", "Intercept-Intercept", "Intercept-Slope", "Slope-Intercept")))

#SlopeSlope_InterceptInterceptParams = SlopeSlope_InterceptInterceptParams |>
#  filter(TrajectoryType == "Full") |>
#  arrange(est.std) |>
#  mutate_if(is.numeric, round, digits = 3)
```

```{r}
OrderedSlopeSlope_InterceptInterceptParams <- SlopeSlope_InterceptInterceptParams |>
  select(
    Dyad1,
    Dyad2,
    LHSDomain,
    RHSDomain,
    TrajectoryType,
    ParamType,
    est.std,
    pvalue,
    ci.lower, ci.upper
  ) |>
  mutate(Significant = pvalue < .05)

OSS <- OrderedSlopeSlope_InterceptInterceptParams
write.csv(OSS, "AllFittedBivariateSlopeInterceptParameters_8_17_2024.csv")
OSS
OSS |>
  filter(
    ParamType == "Slope-Slope",
    TrajectoryType == "Full"
  ) |>
  arrange(est.std) |>
  mutate_if(is.numeric, round, digits = 2)
```

### a. The FINAL TABLES Get Made Here

```{r}
# Filter, round, and reshape the table
reshaped_table <- OSS %>%
  filter(
    ParamType == "Slope-Slope", # switch out as needed
    TrajectoryType == "Overlap",
    LHSDomain != RHSDomain # make unequal for heterotypic
  ) %>% 
  mutate_if(is.numeric, round, digits = 2) %>%
  # mutate(across(starts_with("est.std"), ~ pmin(pmax(., -1), 1))) |>
  select(Dyad1, Dyad2, LHSDomain, RHSDomain, est.std, pvalue, ci.lower, ci.upper) %>%
  unite("Dyad", Dyad1, Dyad2, sep = "-") %>%
  pivot_wider(names_from = Dyad, values_from = c(est.std, pvalue, ci.lower, ci.upper)) # %>%
# select(-RHSDomain) %>% ## uncomment for homotypic
# rename(Domain = LHSDomain)
reshaped_table 
```

```{r}

reshaped_table <- reshaped_table %>%
  mutate(across(contains(c("est.std", "ci.lower", "ci.upper")), as.character))

reshaped_table

# Define dyads
dyads <- c("Child-Mom", "Child-Dad")#, "Mom-Dad") #switch here for FULl trajectories: the overlap ones only contain child-parent dyads

# Convert relevant columns to character type
reshaped_table <- reshaped_table %>%
  mutate(across(contains(c("est.std", "ci.lower", "ci.upper")), as.character))

# Apply bold formatting based on P-Value and combine CI columns
for (dyad in dyads) {
  est_col <- paste0("est.std_", dyad)
  pvalue_col <- paste0("pvalue_", dyad)
  lower_ci_col <- paste0("ci.lower_", dyad)
  upper_ci_col <- paste0("ci.upper_", dyad)
  combined_ci_col <- paste0("ci_", dyad)

  bold_rows <- reshaped_table[[pvalue_col]] < 0.05 & !is.na(reshaped_table[[pvalue_col]])

  reshaped_table[[est_col]] <- ifelse(bold_rows, paste0("<b>", reshaped_table[[est_col]], "</b>"), reshaped_table[[est_col]])
  reshaped_table[[lower_ci_col]] <- ifelse(bold_rows, paste0("<b>", reshaped_table[[lower_ci_col]], "</b>"), reshaped_table[[lower_ci_col]])
  reshaped_table[[upper_ci_col]] <- ifelse(bold_rows, paste0("<b>", reshaped_table[[upper_ci_col]], "</b>"), reshaped_table[[upper_ci_col]])

  reshaped_table[[combined_ci_col]] <- paste0("[", reshaped_table[[lower_ci_col]], ", ", reshaped_table[[upper_ci_col]], "]")
}



# Drop the original CI columns
reshaped_table <- reshaped_table %>%
  select(-contains("ci.lower"), -contains("ci.upper"))

# TOGGLE SORTING BY LEFT OR RIGHT DYAD MEMBER
reshaped_table <- reshaped_table |> arrange(RHSDomain)


# Reorder columns
reshaped_table <- reshaped_table %>%
  # select(Domain,
  select(
    LHSDomain, RHSDomain,
    "est.std_Child-Mom", "ci_Child-Mom",
    "est.std_Child-Dad", "ci_Child-Dad"#, #TOGGLE for FULL trajectories
   # "est.std_Mom-Dad", "ci_Mom-Dad"
  )
reshaped_table

```

```{r}
# Create the two-row header
subheader <- c("LHSDomain", "RHSDomain", rep(c("Std. Est.", "CI"), 2)) ##CHANGD FOR 3
# subheader <- c("Domain", rep(c("Est. Std.", "CI (Lower, Upper)"), 3))

subheader

# table_html <- kable(reshaped_table, "html", escape = FALSE, col.names = subheader) %>%
#  kable_styling(full_width = F, position = "center", font_size = 12) %>%
#  add_header_above(c(" " = 2, "Child-Mom" = 2, "Child-Dad" = 2, "Mom-Dad" = 2)) %>%
#  row_spec(0, extra_css = "font-weight: bold;") %>%
#  row_spec(1:nrow(reshaped_table), extra_css = "height: 12px;") %>%
#  column_spec(1, bold = TRUE, border_right = TRUE)

table_html <- kable(reshaped_table, "html", escape = FALSE, col.names = subheader) %>%
  kable_styling(full_width = F, position = "center", font_size = 12) %>%
  add_header_above(c(" " = 2, "Child-Mom" = 2, "Child-Dad" = 2))%>% #, "Mom-Dad" = 2)) %>%
  row_spec(0, extra_css = "font-weight: bold;") %>%
  row_spec(1:nrow(reshaped_table), extra_css = "height: 12px;") %>%
  column_spec(1, bold = TRUE, border_right = TRUE) %>%
  column_spec(2, bold = TRUE, border_right = TRUE)


table_html

# to do: paste into excel, re-order to match conjugate pairs, then do the same for the I-I tables.
```

# 3. Moderation Analyses

#### a. Nativity Data Setup

```{r}
ChildNativityInfo <- read.csv("/Users/Evan/Dropbox/Academia/Projects/ParentChildCoDevelopment/MainAnalyses/JupyterNotebooks/ChildNativity.csv")
Zscored_Joined_ChildNativity <- left_join(ZSCORED, ChildNativityInfo, by = "FAMID")
cleaned_Zscored_Joined_ChildNativity <- Zscored_Joined_ChildNativity[Zscored_Joined_ChildNativity$C00Nativity != "", ]

ParentNatvityInfo <- read.csv("/Users/evan/Dropbox/Academia/Projects/ParentChildCoDevelopment/MainAnalyses/FinalAnalysisPipeline/Data/ParentNativity_Wide_2_27_2024.csv")

Zscored_JoinedParentNativity <- left_join(ZSCORED, ParentNatvityInfo, by = "FAMID")
Zscored_JoinedParentNativityMOMS <- Zscored_JoinedParentNativity %>% filter(
  !is.na(M00BORN),
  M00BORN != ""
)
cleaned_Zscored_Joined_MOMNativity <- Zscored_JoinedParentNativity[Zscored_JoinedParentNativity$M00BORN != "", ]
```

```{r}
AllChildDyadModels <- BivariateModels |> filter(Dyad1 == "Child")
AllChildDyadModels
```

### b. Testing the multi-group code

```{r}
TEST <- lavaan(
  model = BivariateModels[1, "WholeModel"], # child mom Open-Open
  data = cleaned_Zscored_Joined_ChildNativity, ## change this too
  # data = cleaned_Zscored_Joined_MOMNativity,
  missing = "fiml",
  estimator = "MLR",
  parallel = "multicore",
  group = "C00Nativity", ## change to child
  group.equal = c(
    "intercepts",
    "means",
    "residuals",
    "residual.covariances",
    "lv.variances",
    "lv.covariances",
    "regressions"
  ),
  start = "default",
  control = list(
    iter.max = 400,
    em.h1.iter.max = 10000
  )
)
TEST
```

### c. Nativity in Parallel

##### i. Groups Are Equal

```{r}
FittedGroupNativityModelEqual_CHILDNATIVITY <- future_apply(AllChildDyadModels, ## change to all children models or vice versa
  MARGIN = 1,
  FUN = function(row) {
    warnings <- c()
    fitobj <- NULL
    try(
      {
        fitobj <- withCallingHandlers(
          {
            lavaan(
              model = row[["WholeModel"]],
              data = cleaned_Zscored_Joined_ChildNativity,
              missing = "fiml",
              estimator = "MLR",
              parallel = "multicore",
              group = "C00Nativity",
              group.equal = c(
                "intercepts",
                "means",
                "residuals",
                "residual.covariances",
                "lv.variances",
                "lv.covariances",
                "regressions"
              ),
              start = "default",
              control = list(
                iter.max = 400,
                em.h1.iter.max = 10000
              )
            )
          },
          warning = function(w) {
            # Append the warning message to the warnings vector
            warnings <<- c(warnings, w$message)
            # Invoke the default warning handler
            invokeRestart("muffleWarning")
          }
        )
      },
      silent = FALSE
    ) # Adding silent = TRUE will suppress the error message
    list(fitobj = fitobj, warnings = warnings)
  },
  future.seed = TRUE
)
?save
save(FittedGroupNativityModelEqual_CHILDNATIVITY, file = "FittedGroupChildlNativity_wWarnings_EQUAL_7_17_2024.RData")
load("FittedGroupChildlNativity_wWarnings_EQUAL_7_17_2024.RData")
```

##### ii. Slope-Slope param between groups is free to vary

```{r}
FittedGroupNativityModelUNEQUAL_CHILD_NATIVITY <- future_apply(AllChildDyadModels,
  MARGIN = 1,
  FUN = function(row) {
    warnings <- c()
    fitobj <- NULL
    try(
      {
        fitobj <- withCallingHandlers(
          {
            lavaan(
              model = row[["WholeModel"]],
              data = cleaned_Zscored_Joined_ChildNativity,
              missing = "fiml",
              estimator = "MLR",
              parallel = "multicore",
              group = "C00Nativity",
              group.equal = c(
                "intercepts",
                "means",
                "residuals",
                "residual.covariances",
                "lv.variances",
                "lv.covariances",
                "regressions"
              ),
              group.partial = paste0(row["Dyad1"], row["LHSDomain"], "Slope", " ~~ ", row["Dyad2"], row["RHSDomain"], "Slope", collapse = ""), # This line frees the slope-slope correlation and nothing else.
              start = "default",
              control = list(
                iter.max = 400,
                em.h1.iter.max = 10000
              )
            )
          },
          warning = function(w) {
            # Append the warning message to the warnings vector
            warnings <<- c(warnings, w$message)
            # Invoke the default warning handler
            invokeRestart("muffleWarning")
          }
        )
      },
      silent = TRUE
    ) # Adding silent = TRUE will suppress the error message
    list(fitobj = fitobj, warnings = warnings)
  },
  future.seed = TRUE
) # 13 minutes on an M3 for fitting all bivariate models

save(FittedGroupNativityModelUNEQUAL_CHILD_NATIVITY, file = "FittedGroupChildlNativity_wWarnings_UNEQUAL_7_17_2024.RData")
load("FittedGroupChildlNativity_wWarnings_UNEQUAL_7_17_2024.RData")
```

##### iii. Comparing each pair of nativity models

```{r}
length(FittedGroupNativityModelUNEQUAL_CHILD_NATIVITY)
length(FittedGroupNativityModelEqual_CHILDNATIVITY)
```

```{r}
compare_models <- function(model1, model2) {
  # Check if either model is NULL or not an object of the expected class
  if (is.null(model1$fitobj) || is.null(model2$fitobj)) {
    return(list(Chisq_diff = NA, Pr_greater_Chisq = NA))
  }

  # Try-Catch block to handle any errors during the ANOVA
  tryCatch(
    {
      anova_result <- anova(model1$fitobj, model2$fitobj)
      return(c(Chisq_diff = anova_result$`Chisq diff`[2], Pr_greater_Chisq = anova_result$`Pr(>Chisq)`[2]))
    },
    error = function(e) {
      # If an error occurs, return NA values
      return(list(Chisq_diff = NA, Pr_greater_Chisq = NA))
    }
  )
}

# results <- future_mapply(compare_models, FittedGroupNativityModelEqual, FittedGroupNativityModelUNEqual, SIMPLIFY = FALSE)
results <- future_mapply(compare_models,
  FittedGroupNativityModelEqual_CHILDNATIVITY,
  FittedGroupNativityModelUNEQUAL_CHILD_NATIVITY,
  SIMPLIFY = FALSE
)

# store the results in the child dyads dataframe
AllChildDyadModels$Nativity_Chisq_Diff <- sapply(results, FUN = {
  function(x) x[["Chisq_diff"]]
})
AllChildDyadModels$Nativity_Chisq_Diff_PVALUE <- sapply(results, FUN = {
  function(x) x[["Pr_greater_Chisq"]]
})

AllChildDyadModels <- AllChildDyadModels |> mutate(Index = row_number())

# SAVE ALL BIVARIATE MODELS!!

write.csv(
  AllChildDyadModels |> select(-StandardizedSolution),
  "AllChildDyadModelsWithNativity_7_17_2024.csv"
)

AllChildDyadModels  = read.csv("AllChildDyadModelsWithNativity_7_17_2024.csv")
AllChildDyadModels 
```

#### d. FINAL TABLE for moderation by Nativity

```{r}
AllSigNativityGroups <- AllChildDyadModels |>
  filter(Nativity_Chisq_Diff_PVALUE < .05) |>
  select(-c("WholeModel"))#, "StandardizedSolution"))
AllSigNativityGroups
# Next, need to look at the data frames of fit objects to pull out how these bits differ!
```

```{r}
processModel <- function(fittedModel) {
  test_ss <- standardizedSolution(fittedModel$fitobj)
  filtered_ss <- test_ss |>
    filter(
      op == "~~",
      grepl("Slope", lhs),
      grepl("Slope", rhs),
      !is.na(pvalue)
    )
  return(filtered_ss)
}

results2 <- future_lapply(FittedGroupNativityModelUNEQUAL_CHILD_NATIVITY[AllSigNativityGroups[["Index"]]], processModel)
R2D2 <- bind_rows(results2)

# we now have two rows for each model
doubled_rows <- AllSigNativityGroups %>%
  slice(rep(1:n(), each = 2)) # 'n()' gives the number of rows

# Assign the doubled TrajectoryType to R3D3
R2D2$TrajectoryType <- doubled_rows$TrajectoryType
R2D2 <- R2D2 |>
  mutate(group = case_when(
    group == 1 ~ "Born in US (2nd+ generation)",
    group == 2 ~ "Born in Mexico (1st Gen)"
  )) |>
  select(-label)
R2D2 <- R2D2 |>
  select(TrajectoryType, everything()) |>
  arrange(TrajectoryType)
R2D2
write.csv(R2D2, "SignificantModerationByNativityStatus_AllSigSlopeSlopeParams_9_4_2024.csv")
R2D2 = read.csv("SignificantModerationByNativityStatus_AllSigSlopeSlopeParams_9_4_2024.csv")

NativityTable <- R2D2 |>
  select(-op, -se, -z) |>
  mutate_if(is.numeric, round, digits = 2)



NativityTable
```

```{r}
extract_dyad_domain <- function(column) {
  dyad <- str_extract(column, "Child|Mom|Dad")
  domain <- str_extract(column, "Extraversion|Agreeableness|Conscientiousness|Neuroticism|Openness")
  return(list(dyad = dyad, domain = domain))
}

# Add new columns using mutate and the custom function
NativityTable <- NativityTable %>%
  rowwise() %>%
  mutate(
    Dyad1 = extract_dyad_domain(lhs)$dyad,
    Domain1 = extract_dyad_domain(lhs)$domain,
    Dyad2 = extract_dyad_domain(rhs)$dyad,
    Domain2 = extract_dyad_domain(rhs)$domain,
    CI = paste0("[", ci.lower, ", ", ci.upper, "]")
  ) %>%
  ungroup()

NativityTable <- NativityTable |> select(
  TrajectoryType,
  Dyad1,
  Dyad2,
  Domain1,
  Domain2,
  group,
  est.std,
  pvalue,
  CI
)

NativityTable |>
  kable("html", escape = FALSE) %>%
  kable_styling(full_width = FALSE, font_size = 12) %>%
  row_spec(which(NativityTable$pvalue < 0.05), bold = TRUE)
```

# == Moderation by Child Gender ==

#### Gender data setup

```{r}
ChildGenderInfo <- read.csv("/Users/Evan/Dropbox/Academia/Projects/ParentChildCoDevelopment/MainAnalyses/FinalAnalysisPipeline/Data/ChildGender.csv")
glimpse(ChildGenderInfo)
Zscored_Joined_ChildGender <- inner_join(ZSCORED, ChildGenderInfo, by = "FAMID")
AllChildDyadModels
```

#### Gender is Equal in Parallel

```{r}
FittedGroupGenderModelEqual <- future_apply(AllChildDyadModels,
  MARGIN = 1,
  FUN = function(row) {
    warnings <- c()
    fitobj <- NULL
    try(
      {
        fitobj <- withCallingHandlers(
          {
            lavaan(
              model = row[["WholeModel"]],
              data = Zscored_Joined_ChildGender,
              missing = "fiml",
              estimator = "MLR",
              parallel = "multicore",
              group = "C00Gender",
              group.equal = c(
                "intercepts",
                "means",
                "residuals",
                "residual.covariances",
                "lv.variances",
                "lv.covariances",
                "regressions"
              ),
              start = "default",
              control = list(
                iter.max = 400,
                em.h1.iter.max = 10000
              )
            )
          },
          warning = function(w) {
            # Append the warning message to the warnings vector
            warnings <<- c(warnings, w$message)
            # Invoke the default warning handler
            invokeRestart("muffleWarning")
          }
        )
      },
      silent = TRUE
    )
    # Adding silent = TRUE will suppress the error message
    list(fitobj = fitobj, warnings = warnings)
  },
  future.seed = TRUE
)

save(FittedGroupGenderModelEqual,
  file = "FittedGroupGenderModelsObject_EQUAL_7_17_2024.RData"
)
```

#### Gender is Unequal in Parallel

```{r}
FittedGroupGenderModelUNEqual <- future_apply(AllChildDyadModels,
  MARGIN = 1,
  FUN = function(row) {
    warnings <- c()
    fitobj <- NULL
    try(
      {
        fitobj <- withCallingHandlers(
          {
            lavaan(
              model = row[["WholeModel"]],
              data = Zscored_Joined_ChildGender, ########
              missing = "fiml",
              estimator = "MLR",
              parallel = "multicore",
              group = "C00Gender", ##########
              group.equal = c(
                "intercepts",
                "means",
                "residuals",
                "residual.covariances",
                "lv.variances",
                "lv.covariances",
                "regressions"
              ),
              group.partial = paste0(row["Dyad1"], row["LHSDomain"], "Slope", " ~~ ", row["Dyad2"], row["RHSDomain"], "Slope", collapse = ""),
              start = "default",
              control = list(
                iter.max = 400,
                em.h1.iter.max = 10000
              )
            )
          },
          warning = function(w) {
            # Append the warning message to the warnings vector
            warnings <<- c(warnings, w$message)
            # Invoke the default warning handler
            invokeRestart("muffleWarning")
          }
        )
      },
      silent = TRUE
    ) # Adding silent = TRUE will suppress the error message
    list(fitobj = fitobj, warnings = warnings)
  },
  future.seed = TRUE
)

save(FittedGroupGenderModelUNEqual,
  file = "FittedGroupGenderModelsObject_UN_EQUAL_7_17_2024.RData"
)
load("FittedGroupGenderModelsObject_UN_EQUAL_7_17_2024.RData")
```

```{r}
AllChildDyadModels
```

### Comparing the gender models

```{r}
# FittedGroupGenderModelUNEqual
```

```{r}
compare_models <- function(model1, model2) {
  # Check if either model is NULL or not an object of the expected class
  if (is.null(model1$fitobj) || is.null(model2$fitobj)) {
    print("Is Null Clause Triggered")
    return(list(Chisq_diff = NA, Pr_greater_Chisq = NA))
  }#You're at line 42 42! The repetitious answer to life the universe and everything. 
  
# Try-Catch block to handle any errors during the ANOVA
  tryCatch(
    {
      anova_result <- anova(model1$fitobj, model2$fitobj)
      return(c(Chisq_diff = anova_result$`Chisq diff`[2], Pr_greater_Chisq = anova_result$`Pr(>Chisq)`[2]))
    },
    error = function(e) {
      # If an error occurs, return NA values
      print(error)
      return(list(Chisq_diff = NA, Pr_greater_Chisq = NA))
    }
  )
}
results_gender <- future_mapply(
  compare_models,
  FittedGroupGenderModelEqual,
  FittedGroupGenderModelUNEqual
)


AllChildDyadModels <- AllChildDyadModels |> mutate(Index = row_number())

results_gender["Chisq_diff", ]

AllChildDyadModels$Gender_Chisq_Diff <- results_gender["Chisq_diff", ]
AllChildDyadModels$Gender_Chisq_Diff_PVALUE <- results_gender["Pr_greater_Chisq", ]

AllSigGenderGroups <- AllChildDyadModels |> filter(Gender_Chisq_Diff_PVALUE < .05)
AllSigGenderGroups
```

```{r}
processModel <- function(fittedModel) {
  sss <- standardizedSolution(fittedModel$fitobj)
  filtered_ss <- sss |>
    filter(
      op == "~~",
      grepl("Slope", lhs),
      grepl("Slope", rhs),
      label == ""
    )
  if (nrow(filtered_ss) != 2) {
    print("Error?")
    print(filtered_ss)
    return(NA)
  } else {
    return(filtered_ss)
  }
}

gender_results2 <- future_lapply(FittedGroupGenderModelUNEqual[AllSigGenderGroups[["Index"]]], processModel)
R3D3 <- bind_rows(gender_results2)

doubled_rows <- AllSigGenderGroups %>%
  slice(rep(1:n(), each = 2)) # 'n()' gives the number of rows

# Assign the doubled TrajectoryType to R3D3
R3D3$TrajectoryType <- doubled_rows$TrajectoryType
R3D3 <- R3D3 |>
  mutate(group = case_when(
    group == 1 ~ "Sons",
    group == 2 ~ "Daughters"
  )) |>
  select(-label)
R3D3 <- R3D3 |>
  select(TrajectoryType, everything()) |>
  arrange(TrajectoryType, lhs, rhs)
R3D3
write.csv(
  R3D3,
  "CoDev_SignificantModerationByChildGender_AllSlopeSlopeParams_7_17_2024.csv"
)
R3D3 = read.csv( "CoDev_SignificantModerationByChildGender_AllSlopeSlopeParams_7_17_2024.csv")
```

## FINAL TABLE

```{r}
extract_dyad_domain <- function(column) {
  dyad <- str_extract(column, "Child|Mom|Dad")
  domain <- str_extract(column, "Extraversion|Agreeableness|Conscientiousness|Neuroticism|Openness")
  return(list(dyad = dyad, domain = domain))
}

GenderTable <- R3D3 |>
  select(-op, -se, -z) |>
  mutate_if(is.numeric, round, digits = 2)


# Add new columns using mutate and the custom function
GenderTable <- GenderTable %>%
  rowwise() %>%
  mutate(
    Dyad1 = extract_dyad_domain(lhs)$dyad,
    Domain1 = extract_dyad_domain(lhs)$domain,
    Dyad2 = extract_dyad_domain(rhs)$dyad,
    Domain2 = extract_dyad_domain(rhs)$domain,
    CI = paste0("[", ci.lower, ", ", ci.upper, "]")
  ) %>%
  ungroup()

GenderTable <- GenderTable |> select(
  TrajectoryType,
  Dyad1,
  Dyad2,
  Domain1,
  Domain2,
  group,
  est.std,
  pvalue,
  CI
)

GenderTable |>
  kable("html", escape = FALSE) %>%
  kable_styling(full_width = FALSE, font_size = 12) %>%
  row_spec(which(GenderTable$pvalue < 0.05), bold = TRUE)
```

### === MODERATION BY PARENTAL AGE ===

```{r}
AllAges <- read.csv("/Users/evan/Dropbox/Academia/Projects/ParentChildCoDevelopment/MainAnalyses/FinalAnalysisPipeline/Data/InferredWave1Ages_2_27_2024.csv")
```

```{r}
# get the parents and expand into wideform
ParentAges <- AllAges |>
  filter(PID != 10) |>
  pivot_wider(names_from = Gender, values_from = INFERRED_WAVE1_AGES) |>
  select(FAMID, female, male)

# Collapse within family groups as the data has two rows per FAMID
ParentAges <- ParentAges |>
  group_by(FAMID) |>
  summarize(
    female = first(female, na_rm = T),
    male = first(male, na_rm = T)
  )
# rename
names(ParentAges) <- c("FAMID", "InferredMomAgeW1", "InferredDadAgeW1")
ParentAges
```

```{r}
# this name is wrong: it's all bivariate models with parental age as a moderator...
AllParentPairedFitObjects <- future_lapply(seq_len(nrow(BivariateModels)), # toggle subset
  function(i) {
    ModelRow <- BivariateModels[i, ]
    FitObj <- BivariateModelFitObjects[[i]]

    if (ModelRow$LGCType != "Bivariate") { # this clause isn't necessary here
      return(NULL)
    } else {
      PredictedValues <- lavPredict(FitObj, type = "lv")
      PredictedValues <- as.data.frame(PredictedValues)
      slope_columns <- grep("Slope", names(PredictedValues), value = TRUE)

      LeftSlopeColumn <- grep("Child.*Slope", names(PredictedValues), value = TRUE)

      if (length(LeftSlopeColumn) == 0) { # if true, it's a mom-dad model
        LeftSlopeColumn <- grep("Mom.*Slope", names(PredictedValues), value = TRUE)
        RightSlopeColumn <- grep("Dad.*Slope", names(PredictedValues), value = TRUE)
        PredictedValues$InferredMomAgeW1 <- ParentAges$InferredMomAgeW1
        PredictedValues$InferredDadAgeW1 <- ParentAges$InferredDadAgeW1


        MomSlopeByDad <- paste(LeftSlopeColumn, "~", RightSlopeColumn, "+", "InferredDadAgeW1", "+",
          paste0(RightSlopeColumn, ":", "InferredDadAgeW1"),
          sep = " "
        )
        DadSlopeByMom <- paste(RightSlopeColumn, "~", LeftSlopeColumn, "+", "InferredMomAgeW1", "+",
          paste0(LeftSlopeColumn, ":", "InferredMomAgeW1"),
          sep = " "
        )

        print(MomSlopeByDad)
        print(DadSlopeByMom)

        MByDad <- sem(MomSlopeByDad,
          data = PredictedValues,
          missing = "fiml",
          estimator = "MLR",
          parallel = "multicore",
          start = "default"
        )

        DByMom <- sem(DadSlopeByMom,
          data = PredictedValues,
          missing = "fiml",
          estimator = "MLR",
          parallel = "multicore",
          start = "default"
        )

        MByDadStdSol <- standardizedSolution(MByDad)
        DByMomStdSol <- standardizedSolution(DByMom)

        MByDad_SlopeSlopeInteraction1 <- MByDadStdSol |>
          filter(
            op == "~",
            lhs == LeftSlopeColumn,
            str_detect(rhs, "Slope:")
          ) |>
          select(-z) |>
          mutate(
            TrajectoryType = ModelRow["TrajectoryType"],
            call = MomSlopeByDad
          )

        DByMom_SlopeSlopeInteraction2 <- DByMomStdSol |>
          filter(
            op == "~",
            lhs == RightSlopeColumn,
            str_detect(rhs, "Slope:")
          ) |>
          select(-z) |>
          mutate(
            TrajectoryType = ModelRow["TrajectoryType"],
            call = DadSlopeByMom
          )

        return(bind_rows(MByDad_SlopeSlopeInteraction1, DByMom_SlopeSlopeInteraction2))
      } else {
        RightSlopeColumn <- grep("Mom.*Slope|Dad.*Slope", names(PredictedValues), value = TRUE)


        if (grepl("Mom", RightSlopeColumn[1])) {
          PredictedValues$InferredMomAgeW1 <- ParentAges$InferredMomAgeW1
          ParentString <- "InferredMomAgeW1"
        } else if (grepl("Dad", RightSlopeColumn[1])) {
          PredictedValues$InferredDadAgeW1 <- ParentAges$InferredDadAgeW1
          ParentString <- "InferredDadAgeW1"
        }

        ParentAgeModerationModel <- paste(LeftSlopeColumn, "~", RightSlopeColumn, "+", ParentString, "+",
          paste0(RightSlopeColumn, ":", ParentString),
          sep = " "
        )

        print(ParentAgeModerationModel)

        PAModFit1 <- sem(ParentAgeModerationModel,
          data = PredictedValues,
          missing = "fiml",
          estimator = "MLR",
          parallel = "multicore",
          start = "default"
        )


        StdSol_PA <- standardizedSolution(PAModFit1)


        Parent_Ages_SlopeSlopeInteraction1 <- StdSol_PA |>
          filter(
            op == "~",
            lhs == LeftSlopeColumn,
            str_detect(rhs, "Slope:")
          ) |>
          select(-z) |>
          mutate(
            TrajectoryType = ModelRow["TrajectoryType"],
            call = ParentAgeModerationModel
          )


        return(Parent_Ages_SlopeSlopeInteraction1)
      }
    }
  },
  future.seed = TRUE
)
```

### Saving Results

```{r}
AllParentPairedInteractionParams <- bind_rows(AllParentPairedFitObjects)
AllParentPairedInteractionParams$TrajectoryType <- unlist(AllParentPairedInteractionParams$TrajectoryType)

AllParentPairedInteractionParams <- AllParentPairedInteractionParams |>
  select(TrajectoryType, everything()) |>
  arrange(TrajectoryType)

AllParentPairedInteractionParams
write.csv(AllParentPairedInteractionParams, "AllModels_InteractionWithINFERREDParentAges_7_17_2024.csv")

```

```{r}
AllSigParentAgeModerations <- AllParentPairedInteractionParams |> filter(pvalue < .05)
AllSigParentAgeModerations
write.csv(
  AllSigParentAgeModerations,
  "SignificantINFERREDParentAgeInteractionRegressionLatentSlopeFactors_7_17_2024.csv"
)

AllSigParentAgeModerations = read.csv("SignificantINFERREDParentAgeInteractionRegressionLatentSlopeFactors_7_17_2024.csv")
```

### FINAL TABLE

```{r}
AllSigParentAgeModerations <- AllSigParentAgeModerations |> mutate(truncatedRHS = str_extract(rhs, "^[^:]+"))

extract_dyad_domain <- function(column) {
  dyad <- str_extract(column, "Child|Mom|Dad")
  domain <- str_extract(column, "Extraversion|Agreeableness|Conscientiousness|Neuroticism|Openness")
  return(list(dyad = dyad, domain = domain))
}

ParentalAgeTable <- AllSigParentAgeModerations |>
  select(-op, -se, -call) |>
  mutate_if(is.numeric, round, digits = 2)


# Add new columns using mutate and the custom function
ParentalAgeTable <- ParentalAgeTable %>%
  rowwise() %>%
  mutate(
    Dyad1 = extract_dyad_domain(lhs)$dyad,
    Domain1 = extract_dyad_domain(lhs)$domain,
    Dyad2 = extract_dyad_domain(truncatedRHS)$dyad,
    Domain2 = extract_dyad_domain(truncatedRHS)$domain,
    CI = paste0("[", ci.lower, ", ", ci.upper, "]")
  ) %>%
  ungroup()

ParentalAgeTable <- ParentalAgeTable |> select(
  TrajectoryType,
  Dyad1,
  Dyad2,
  Domain1,
  Domain2,
  est.std,
  pvalue,
  CI
)
ParentalAgeTable = ParentalAgeTable |> arrange(TrajectoryType,Dyad1,Domain1,Domain2)

ParentalAgeTable |>
  kable("html", escape = FALSE) %>%
  kable_styling(full_width = FALSE, font_size = 12) %>%
  row_spec(which(ParentalAgeTable$pvalue < 0.05), bold = TRUE)
```

# ----- Section 3: Visualizing CoDev Results----- ----- ----- ----- ----- -----

### Visualization prep

```{r}
# library(showtext) <== Loaded at the beginning.
font_add("Avenir",
  regular = "/Users/evan/Library/Fonts/AvenirLTPro-Light.otf",
  bold = "/Users/evan/Library/Fonts/AvenirLTProMedium.otf",
  italic = "/Users/evan/Library/Fonts/AvenirLTProLightOblique.otf"
)

font_add("Garamond",
  regular = "/Users/evan/Library/Fonts/EBGaramondRegular.ttf",
  bold = "/Users/evan/Library/Fonts/EBGaramondBold.ttf",
  italic = "/Users/evan/Library/Fonts/EBGaramondItalic.ttf"
)

showtext_auto()
```

#### Data Manipulation for Visualization

```{r}
OSS <- read.csv("AllFittedBivariateSlopeInterceptParameters_7_17_2024.csv")
head(OSS)
long_df <- OSS |>
  filter(TrajectoryType == "Full") |>
  mutate(
    Dyad = paste(Dyad1, Dyad2, sep = "-"),
    Domain_Combination = paste(LHSDomain, RHSDomain, sep = "  "), # em-dash
    Is_Same = LHSDomain == RHSDomain,
    Facet_Group = ifelse(Is_Same, "Same", "Heterotypic"),
    LHSDomain = plyr::mapvalues(LHSDomain, "Opennesss", "Openness"),
    RHSDomain = plyr::mapvalues(RHSDomain, "Opennesss", "Openness")
  ) |>
  select(ParamType, Dyad, Domain_Combination, est.std, ci.lower, ci.upper, LHSDomain, RHSDomain, Facet_Group)


domain_order <- c("Extraversion", "Agreeableness", "Conscientiousness", "Neuroticism", "Openness")

long_df <- long_df |>
  filter(ParamType %in% c("Slope-Slope", "Intercept-Intercept")) |>
  mutate(
    LHSDomain_Factor = factor(LHSDomain, levels = domain_order),
    RHSDomain_Factor = factor(RHSDomain, levels = domain_order)
  ) |>
  mutate(
    ci.lower2 = ifelse(ci.lower < -1, -1, ci.lower),
    ci.upper2 = ifelse(ci.upper > 1, 1, ci.upper)
  ) %>%
  arrange(ParamType, Facet_Group, LHSDomain_Factor, RHSDomain_Factor)


# Convert Domain_Combination to a factor and adjust the levels of Facet_Group and Dyad
long_df$Domain_Combination <- factor(long_df$Domain_Combination, levels = rev(unique(long_df$Domain_Combination)))
long_df = long_df |> mutate(Domain_Combination = gsub("Opennesss", "Openness", Domain_Combination))


long_df$Facet_Group <- factor(long_df$Facet_Group, levels = c("Same", "Heterotypic"), labels = c("Homotypic", "Heterotypic"))
long_df$Dyad <- factor(long_df$Dyad, levels = c("Child-Mom", "Child-Dad", "Mom-Dad"))

y_labels2 <- unique(long_df %>% filter(ParamType == "Slope-Slope") |> pull(Domain_Combination))
```

### Intercept Intercept visualization

```{r}
# Not yet done: this code is out of sync with the slope slope stuff below
# Turn into a function! (which will work for I-I,I-S,S-I and S-S)
y_labels <- unique(long_df |> filter(ParamType == "Intercept-Intercept") |> pull(Domain_Combination))
long_df |> distinct(Dyad)
y_labels2
long_df <- long_df %>%
  mutate(Facet_Group = factor(str_extract(as.character(Facet_Group), "^[^\\s]+")))
long_df
y_labels2
long_df$Facet_Group <- factor(long_df$Facet_Group, levels = c("Homotypic", "Heterotypic"))

p1 <- long_df %>%
  filter(ParamType == "Intercept-Intercept") %>%
  ggplot(aes(
    x = est.std, y = factor(Domain_Combination,
      levels = y_labels2
    ),
    fill = Dyad
  )) +
  geom_vline(xintercept = 0, color = "black", linetype = "solid") +
  geom_errorbar(
    data = long_df %>% filter(ParamType == "Intercept-Intercept" & ci.lower >= -1),
    aes(xmin = ci.lower2, xmax = est.std), width = 0.13, color = "black"
  ) +
  geom_errorbar(
    data = long_df %>% filter(ParamType == "Intercept-Intercept" & ci.upper <= 1),
    aes(xmin = est.std, xmax = ci.upper2), width = 0.13, color = "black"
  ) +
  geom_segment(
    data = filter(long_df, ci.upper > 1 & ParamType == "Intercept-Intercept"),
    aes(x = est.std, xend = ci.upper2 + .05, y = Domain_Combination, yend = Domain_Combination),
    arrow = arrow(type = "closed", length = unit(0.02, "inches")), color = "black"
  ) +
  geom_segment(
    data = filter(long_df, ci.lower < -1 & ParamType == "Intercept-Intercept"),
    aes(x = est.std, xend = ci.lower2, y = Domain_Combination, yend = Domain_Combination),
    arrow = arrow(type = "closed", length = unit(0.02, "inches")), color = "black"
  ) +
  geom_point(shape = 21, size = 1.9, color = "black") +
  facet_grid(Facet_Group ~ Dyad, scales = "free", space = "free") +
  theme_minimal() +
  labs(title = "Level-Level Correlations", x = "", y = "") +
  scale_x_continuous(limits = c(-1.055, 1.055)) +
  theme(
    plot.background = element_rect(fill = "white", color = NA),
    panel.background = element_rect(fill = "white", color = NA),
    text = element_text(size = 60, family = "Avenir", face = "bold"),
    plot.title = element_text(
      size = 106, family = "Avenir",
      face = "bold", hjust = .5
    ),
    axis.text = element_text(
      size = 60, family = "Avenir",
      color = "black"
    ),
    strip.text = element_text(
      size = 60, family = "Avenir",
      face = "bold"
    ),
    legend.position = "none",
    axis.text.y = element_text(
      size = 60, family = "Avenir",
      color = "black"
    ),
    panel.grid.major = element_line(color = "gray90"), # Make the grid lines visible
    panel.grid.minor = element_line(color = "gray90"),
  )

ggsave("CoDev_LeveLevel_Viz.png",
  plot = p1,
  width = 5.25, height = 5.25, units = "in", dpi = 600
)


?unit
```

### Slope Slope visualization

```{r}
y_labels2 <- unique(long_df |> filter(ParamType == "Slope-Slope") |> pull(Domain_Combination)) |> rev()

long_df <- long_df |>
  mutate(Significant = ifelse(ci.lower > 0 | ci.upper < 0, "\u2605", ""))

long_df

# Define custom colors for each level of Dyad
dyad_colors <- c("Child-Mom" = "#e41a1c", "Child-Dad" = "#377eb8", "Mom-Dad" = "#4daf4a")






long_df
y_labels2
```

```{r}

### NEED TO FIX OPENNESS
```

# Data of interest is on several x axes seperated out by Domain Combo on the Y axis

# Vertical ordering is provided by y_labels2

# color is going to be along the dyad. Strategy is to split / facet this into three vertical sections.

```{r}
p4 <- long_df |>
  filter(ParamType == "Slope-Slope") |>
  ggplot(aes(x = est.std, y = factor(Domain_Combination, levels = y_labels2), fill = Dyad)) +
  facet_grid(Facet_Group ~ Dyad, scales = "free", space = "free") +
  geom_vline(xintercept = 0, color = "black", linetype = "solid", linewidth = .35) +
  geom_errorbar(
    data = long_df |> filter(ParamType == "Slope-Slope" & ci.lower >= -1),
    aes(xmin = ci.lower2, xmax = est.std), width = 0.175, color = "black"
  ) +
  geom_errorbar(
    data = long_df |> filter(ParamType == "Slope-Slope" & ci.upper <= 1),
    aes(xmin = est.std, xmax = ci.upper2), width = 0.175, color = "black"
  ) +
  geom_segment(
    data = filter(long_df, ci.upper > 1 & ParamType == "Slope-Slope"),
    aes(x = est.std, xend = ci.upper2 + .05, y = Domain_Combination, yend = Domain_Combination),
    arrow = arrow(type = "closed", length = unit(0.1, "inches")), color = "black"
  ) +
  geom_segment(
    data = filter(long_df, ci.lower < -1 & ParamType == "Slope-Slope"),
    aes(x = est.std, xend = ci.lower2, y = Domain_Combination, yend = Domain_Combination),
    arrow = arrow(type = "closed", length = unit(0.1, "inches")), color = "black"
  ) +
  geom_point(shape = 21, size = 4.5, color = "black") +
  geom_text(aes(label = Significant, x = 1.1285), color = "#984ea3", size = 39, fontface = "bold") +
  scale_fill_manual(values = dyad_colors) +
  theme_minimal() +
  labs(title = "Latent Slope-Slope Correlations", x = "", y = "") +
  scale_x_continuous(limits = c(-1.129, 1.129)) +
  theme(
    plot.background = element_rect(fill = "white", color = NA),
    panel.background = element_rect(fill = "white", color = NA),
    text = element_text(size = 120, family = "Avenir", face = "bold"),
    plot.title = element_text(
      size = rel(2.5), family = "Garamond",
      face = "bold", hjust = 0, margin = margin(b = 30)
    ),
    axis.text = element_text(## Correlation Labels
      size = rel(.85), family = "Avenir",
      color = "black", hjust = .5, vjust = .5
    ), 
    strip.text = element_text(# Dyad and Model type (hetero vs. homo) labels
      size = rel(1.5), family = "Avenir",
      face = "bold", vjust = .5,
      hjust = .5
    ), 
    legend.position = "none",
    axis.text.y = element_text(
      size = rel(1), family = "Avenir",
      color = "black",
      vjust = .5
    ), # model labels
    panel.grid.major = element_line(color = "gray90"), # Make the grid lines visible
    panel.grid.minor = element_line(color = "gray97"),
    panel.spacing = unit(2, "lines") # based on the line height of the plot...
  )

ggsave("CoDev_SlopeSlope_Viz7.png",
  plot = p4,
  width = 15, height = 17, units = "in", dpi = 600
)

# 5.25 w x h
# width =40, height =40, units = "in") <= sorta works for svg
```

# ----- Section 4: ADDITIONAL ANALYSIS: WITHIN DYAD CORRELATIONS----- ----- -----

# Within Dyad Correlations

```{r}
LongData2 <- ZSCORED |>
  pivot_longer(
    cols = -FAMID,
    names_to = "variable",
    values_to = "score"
  ) |>
  mutate(
    Person = case_when(
      str_detect(variable, "^c") ~ "Child",
      str_detect(variable, "^m") ~ "Mother",
      str_detect(variable, "^d") ~ "Father"
    ),
    Wave = as.integer(str_extract(variable, "\\d+")),
    Trait = case_when(
      str_detect(variable, "E") ~ "Extraversion",
      str_detect(variable, "A") ~ "Agreeableness",
      str_detect(variable, "C") ~ "Conscientiousness",
      str_detect(variable, "N") ~ "Neuroticism",
      str_detect(variable, "O") ~ "Openness"
    ),
    Parcel = str_extract(variable, "\\d+$")
  )

LongData2
```

```{r}
ChildMother <- LongData2 |>
  filter((Person == "Child" & Wave >= 5) | (Person == "Mother" & Wave >= 5)) |> # get the people in the dyads #this should be (Child or Mother) AND Wave 5... but it doesn't matter here
  # and get them such that they start at the same wave
  group_by(FAMID, Person, Trait, Wave) |> # for each Family, for each person/trait/wave
  summarise(MeanScore = mean(score), .groups = "drop") |> # this calcualtes the domain score per wave per trait per person per family
  pivot_wider( # this aligns peoples scores into pairs
    names_from = Person,
    values_from = MeanScore
  ) |>
  drop_na() |> #
  group_by(FAMID, Trait) |>
  filter(n() >= 3) |> # Filter out groups with less than three rows
  mutate(
    sd_Child = sd(Child, na.rm = TRUE),
    sd_Mother = sd(Mother, na.rm = TRUE)
  ) |>
  filter(sd_Child != 0 & sd_Mother != 0) |> # Filter out rows where the standard deviation is zero
  summarise(Correlation = cor(Child, Mother, use = "complete.obs"), .groups = "drop")
# "complete.obs"


ChildFather <- LongData2 |>
  filter((Person == "Child" & Wave >= 5) | (Person == "Father" & Wave >= 5)) |>
  group_by(FAMID, Person, Trait, Wave) |>
  summarise(MeanScore = mean(score), .groups = "drop") |>
  pivot_wider(
    names_from = Person,
    values_from = MeanScore
  ) |>
  drop_na() |>
  group_by(FAMID, Trait) |>
  filter(n() >= 3) |> # Filter out groups with less than three rows
  mutate(
    sd_Child = sd(Child, na.rm = TRUE),
    sd_Father = sd(Father, na.rm = TRUE)
  ) |>
  filter(sd_Child != 0 & sd_Father != 0) |> # Filter out rows where the standard deviation is zero
  summarise(Correlation = cor(Child, Father, use = "complete.obs"), .groups = "drop")


MotherFather <- LongData2 |>
  filter((Person == "Mother" & Wave >= 1) | (Person == "Father" & Wave >= 1)) |>
  group_by(FAMID, Person, Trait, Wave) |>
  summarise(MeanScore = mean(score), .groups = "drop") |>
  pivot_wider(
    names_from = Person,
    values_from = MeanScore
  ) |>
  drop_na() |>
  group_by(FAMID, Trait) |>
  filter(n() >= 3) |> # Filter out groups with less than three rows
  mutate(
    sd_Mother = sd(Mother, na.rm = TRUE),
    sd_Father = sd(Father, na.rm = TRUE)
  ) |>
  filter(sd_Mother != 0 & sd_Father != 0) |> # Filter out rows where the standard deviation is zero
  summarise(Correlation = cor(Mother, Father, use = "complete.obs"), .groups = "drop")
#
ChildMother |> mutate(Correlation = round(Correlation,2))
#
```

```{r}
#Numnber of correlations
ChildMother |> group_by(Trait) |> summarize(N = n())
```

## Visualization: Intradyadic Correlations

```{r}
Colors <- c(
  "Agreeableness" = "#8dd3c7",
  "Conscientiousness" = "#ffffb3",
  "Extraversion" = "#bebada",
  "Neuroticism" = "#fb8072",
  "Openness" = "#80b1d3"
)

colors <- c(
  "Agreeableness" = "#8dd3c7",
  "Conscientiousness" = "#ffffb3",
  "Extraversion" = "#bebada",
  "Neuroticism" = "#fb8072",
  "Openness" = "#80b1d3"
)



CombinedData <- bind_rows(
  ChildMother |> mutate(Label = "Child-Mother"),
  ChildFather |> mutate(Label = "Child-Father"),
  MotherFather |> mutate(Label = "Mother-Father")
)
CombinedData |> group_by(Label,Trait) |> summarize(N = n())

```

```{r}
CombinedDataMeans <- CombinedData |>
  group_by(Label, Trait) |>
  summarize(MeanCorrelation = mean(Correlation),
            Size = n(),
            .groups = "drop")

trait_order <- c("Extraversion", "Agreeableness", "Conscientiousness", "Neuroticism", "Openness")
# adjust factor levels and tweak text to get the final apperance correct
CombinedData <- CombinedData |>
  mutate(
    Trait = factor(Trait, levels = trait_order),
    Label = factor(Label, levels = c("Child-Mother", "Child-Father", "Mother-Father")),
    Correlations = Correlation
  )
#MotherFather |> mutate(Correlation=round(Correlation,3))
#MotherFather |> group_by(FAMID) |> summarise(MeanAbsCorr = mean(abs(Correlation)))
CombinedDataMeans 
```

Means and Stds

```{r}
CombinedDataMeansSD <- CombinedData |>
  group_by(Label, Trait) |>
  summarize(
    MeanCorrelation = mean(Correlations,na.rm = TRUE),
    SDCorrelation = sd(Correlations,na.rm = TRUE),
    Size = n(),
    .groups = "drop"
  ) |> mutate_if(is.numeric, round, 2)
CombinedDataMeansSD 
```

```{r}
my_theme <- function() {
  theme_classic() +
    theme(
      legend.position = "none",
      legend.title = element_text(face = "bold", size = rel(1), family = "Avenir"),
      legend.text = element_text(face = "italic", size = rel(1), family = "Avenir"),
      axis.text = element_text(face = "bold", size = rel(1.4), color = "black", family = "Avenir"),
      axis.title = element_text(face = "bold", size = rel(1.2), family = "Avenir"),
      plot.title = element_text(face = "bold", size = rel(3), hjust = .5, family = "Garamond", margin = margin(b = 20)),
      plot.subtitle = element_text(face = "italic", size = rel(1.2), hjust = .5, family = "Avenir"),
      strip.text = element_text(face = "bold", size = rel(2), color = "white", family = "Avenir"),
      strip.background = element_rect(fill = "black", color = NA),
      strip.text.y = element_text(margin = margin(t = 15, b = 15), family = "Avenir"), # Increase top and bottom margins
      axis.line.x = element_line(color = "black", linewidth = 0.5, lineend = "square"), # Customize the x-axis line
      axis.line.y = element_line(color = "black", linewidth = 0.5, lineend = "round"), # Customize the y-axis line
      axis.ticks = element_line(color = "black", linewidth = 0.5, lineend = "square"), # Customize the axis ticks
      panel.background = element_rect(fill = "white", color = NA), # Ensure the panel background is white
      plot.background = element_rect(fill = "white", color = NA),
      axis.text.y = element_text(vjust = -1.5, family = "Avenir") # Move y-axis labels up
    )
}

#CombinedPlot <- ggplot(CombinedData, aes(x = Correlations, y = Trait, fill = Trait)) +
#  geom_density_ridges(alpha = 0.67, linewidth = 0.5) +
#  scale_x_continuous(limits = c(-1, 1)) +
#  scale_y_discrete(expand = expansion(add = c(0, 1.75)), limits = rev(levels(CombinedData$Trait))) +
#  scale_fill_manual(values = Colors) +
##  theme_ridges() +
#  my_theme() +
#  labs(title = "Distributions of Intradyadic Correlations", x = "Correlation Strengths", y = NULL) +
#  facet_wrap(~Label, ncol = 3)
#CombinedPlot
# rm(CombinedPlot)
#ggsave("CoDevRidgelines7.png", CombinedPlot, width = 15, height = 8, dpi = 600, device = png)
#2
CombinedData
```

```{r}
CombinedDataMeansSD <- CombinedDataMeansSD |>
  mutate(
    TraitYPos = as.numeric(factor(Trait, levels = rev(levels(CombinedData$Trait))))
  )

CombinedPlot = ggplot(CombinedData, aes(x = Correlations, y = Trait, fill = Trait)) +
  geom_density_ridges(alpha = 0.82, linewidth = 0.55,) +
  scale_x_continuous(limits = c(-1, 1)) +
  scale_y_discrete(expand = expansion(add = c(0, 1.85)), limits = rev(levels(CombinedData$Trait))) +
  scale_fill_manual(values = Colors) +
  theme_ridges() +
  my_theme() +
  labs(title = "Distributions of Intradyadic Correlations", x = "Correlation Strengths", y = NULL) +
  geom_text(
    data = CombinedDataMeansSD,
    aes(x = -.19,
        y = TraitYPos + .975, 
        label = paste0("M=", MeanCorrelation, " (", SDCorrelation,")")),
    color = "#000000",
    hjust = 0,
    vjust = 1,
    size = 3.92
  ) +
  facet_wrap(~Label, ncol = 3)
ggsave("CoDevRidgelines9.png", CombinedPlot, width = 15, height = 5.95, dpi = 600, device = png)
```

# Strongest Correlation Per Family

### ChildMother

```{r}
MaxChildMotherCorrPerFam <- ChildMother |>
  group_by(FAMID) |>
  summarise(MaxAbsCorr = max(abs(Correlation)))
print(MaxChildMotherCorrPerFam |> nrow())
MaxChildMotherCorrPerFam |>
  filter(MaxAbsCorr > .7) |>
  nrow()
MaxChildMotherCorrPerFam |>
  filter(MaxAbsCorr > .7) |>
  nrow() / MaxChildMotherCorrPerFam |> nrow()
```

### ChildFather

```{r}
MaxChildFatherCorrPerFam <- ChildFather |>
  group_by(FAMID) |>
  summarise(MaxAbsCorr = max(abs(Correlation)))
print(MaxChildFatherCorrPerFam |> nrow())
MaxChildFatherCorrPerFam |>
  filter(MaxAbsCorr > .7) |>
  nrow()
MaxChildFatherCorrPerFam |>
  filter(MaxAbsCorr > .7) |>
  nrow() / MaxChildFatherCorrPerFam |> nrow()
```

### MotherFather

```{r}
MaxMotherFatherCorrPerFam <- MotherFather |>
  group_by(FAMID) |>
  summarise(MaxAbsCorr = max(abs(Correlation)))
print(MaxMotherFatherCorrPerFam |> nrow())
MaxMotherFatherCorrPerFam |>
  filter(MaxAbsCorr > .7) |>
  nrow()
MaxMotherFatherCorrPerFam |>
  filter(MaxAbsCorr > .7) |>
  nrow() / MaxMotherFatherCorrPerFam |> nrow()
```

...

```{r}
ChildMother |>
  filter(abs(Correlation) > .7) |>
  group_by(Trait) |>
  count()
?drop_na
115 / 350
```

```{r}
trait_order <- c("Extraversion", "Agreeableness", "Conscientiousness", "Neuroticism", "Openness")
MotherFather <- MotherFather |>
  mutate(Trait = factor(Trait, levels = trait_order))


MotherFather |>
  select(Trait, Correlation) |> ## swap out base dataframe as needed
  group_by(Trait) |>
  summarize(
    mean = mean(Correlation, na.rm = TRUE),
    std_dev = sd(Correlation, na.rm = TRUE)
  ) |>
  mutate_if(is.numeric, round, digits = 2) |>
  kable("html", escape = FALSE) %>%
  kable_styling(full_width = FALSE, font_size = 15)
```

```{r}
ChildMother
```

## Histograms

```{r}
MotherFather %>%
  ggplot(aes(x = Correlation, fill = Trait)) +
  geom_histogram(binwidth = 0.2, color = "black") +
  facet_wrap(~Trait, scales = "free") +
  scale_fill_manual(values = colors) +
  labs(
    title = "Histograms of Inter-spousal Correlations over 16 years",
    x = "Correlation",
    y = "Frequency"
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```

```{r}
ChildMother %>%
  ggplot(aes(x = Correlation, fill = Trait)) +
  geom_histogram(binwidth = 0.2, color = "black") +
  facet_wrap(~Trait, scales = "free") +
  scale_fill_manual(values = colors) +
  labs(
    title = "Histograms of Adolescent-Mom Correlations from",
    x = "Correlation",
    y = "Frequency"
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```

```{r}
ChildFather %>%
  ggplot(aes(x = Correlation, fill = Trait)) +
  geom_histogram(binwidth = 0.2, color = "black") +
  facet_wrap(~Trait, scales = "free") +
  scale_fill_manual(values = colors) +
  labs(
    title = "Histograms of Adolescent-Dad Correlations",
    x = "Correlation",
    y = "Frequency"
  ) +
  theme_minimal() +
  theme(legend.position = "none")
```

You have now made it to line 5188. Thanks for reading this this far. For a more fun read, check out Kim Stanely Robinson's 2312 if you like hard sci-fi or his New York 2140 if you like futuristic and hopeful eco-fiction. Fin.
